### 2024-09-04 paper/main.tex
update

% !TEX program = xelatex
\documentclass[twocolumn,superscriptaddress,english,showpacs,longbibliography]{revtex4-2}
\usepackage[colorlinks=true,urlcolor=blue,citecolor=blue,linkcolor=blue]{hyperref}

\usepackage{svg}
\usepackage{amsmath}
\usepackage{graphicx}% Include figure files
\usepackage{textcomp}
\usepackage{bm}% bold math
\usepackage{color}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{graphicx}
\usepackage{color}
\usepackage{mathrsfs}
\usepackage{float}
\usepackage{indentfirst}
\usepackage{txfonts}
\usepackage{algorithm}  
\usepackage{algpseudocode}  
\usepackage{balance}
\usepackage{flushend}
\usepackage{cleveref}
\usepackage{kbordermatrix}
\usepackage{blkarray}
\usepackage{tikz}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}  % Use Input in the format of Algorithm  
\renewcommand{\algorithmicensure}{\textbf{Output:}} % Use Output in the format of Algorithm  
\newtheorem{hyp}{Hypothesis}

\newcommand{\jinguo}[1]{[{\color{blue}{JGL: #1}}]}
\newcommand{\ym}[1]{[{\color{red}{YM: #1}}]}
\newcommand{\s}{\mathbf {s}}
\newcommand{\net}[1]{{\textsc{#1}}}
\newcommand{\argmin}{\mathop{\mathrm{argmin}}\limits}
\newcommand{\Eq}[1]{Eq.~(\ref{#1})}
\newcommand{\Fig}[1]{Fig.~\ref{#1}}

\begin{document}

\title{Surface programmable materials}

\author{Authors}
\email{xxx@xxx.com}
\affiliation{
    XXX
}

\begin{abstract}
\end{abstract}

\maketitle

\section{Introduction}

\jinguo{Please cover the following topics:
\begin{enumerate}
    \item The method to thermalize, inspired from crystalization and heat zone.
\end{enumerate}
}
\ym{Need to add a brief summary about the state-of-the-art TCs. Following is some basic summaries of references
\begin{enumerate}
    \item The material was orderly grown by slowly moving the temperature gradient in-plane~\cite{Zhang2014}. Tested thermal gradient force for grain boundary migration~\cite{Bai2015}.
    \item Discussed the architecture of future thermodynamic computer and brought up an idea about the understanding of using TC to solve problems~\cite{hylton2021vision}.
    \item TODO: search for gadgets for array multiplier.
\end{enumerate}
}

Improving the energy efficiency of computation is a major challenge in the development of future computing systems.
The thermodynamic computer (TC)~\cite{conte2019thermodynamic} is a new type of computer that uses thermodynamics to perform computation.
Instead of performing the computation deterministically, TCs are stochastic and are driven by thermodynamics.
Physical implementations of TCs include DNA machines~\cite{tanaka2005design}, memristors~\cite{yang2013memristive, wang2017memristors, kumar2017chaotic, wang2018fully}, and Ising machines~\cite{gu2012encoding, lucas2014ising, mohseni2022ising, fabre2014optical}.

The computational process of TCs utilizes the tendency of a physical system to evolve towards the state with the lowest free energy.
By manipulating the minimum free energy state of the system, the computation can be performed.
The change of free energy minimum state can be achieved by changing the distribution of the particles in the system, such as in the case of DNA machines~\cite{Feynman2018} or lowering the temperature of the system, such as in the case of Ising machines~\cite{boixo2013experimental}.
The former is known as the Brownian machine, which evolves the system toward the direction of the entropy increase, while the latter are energy based, which evolves the system toward the direction of the energy decrease.
\jinguo{What category are the memristors?}

Energy based models are probability one of the most powerful models for computation.
The Ising model is not only capable of universal computation~\cite{gu2012encoding}, and it can be used to formulate many NP problems~\cite{lucas2014ising,mohseni2022ising}.

However, they are notoriously hard to thermalize, even with the help of quantum entanglement~\cite{boixo2013experimental, boixo2014evidence, Pichler2018, Ebadi2022, Nguyen2023}.
There is no evidence yet that they can significantly outperform existing algorithms run on classical computers~\cite{}.
Even when the encoded problem is an easy one, it is not guaranteed that the system can thermalize in polynomial time as we will show in the main text.

Intrigued by the question of how to thermalize and lower the energy of an Ising machine, we propose a new type of TC that has a crystalline structure.
The crystalline structure is based on a universal elementary cellular automata, and is translational invariant in all spacial dimensions.
The translational invariance not only makes the crystal easier to be constructed in nature, but also enables the study of the scaling behavior the thermalization process.
In the rest of this paper, we first show that the crystalline structure can be programmed on its surfaces to perform universal computation \Cref{sec:Overview-of-main-results}.
Then we use numerical results in \Cref{sec:numerical-result} to show that if we thermalize the crystal from the so-called ``deterministic direction'', the crystal can thermalize in time almost linear to the size of the crystal, i.e. efficient computation can be performed.

% The way to lower the free energy is inspired by the process of crystalization.
% The material is orderly grown by slowly moving the temperature gradient in-plane~\cite{Zhang2014}.
% Growing a perfect crystal itself is a computation process of copying the information from one surface to another.
%In the DNA based TC, the DNA enzyme is driven by thermodynamics, and the computation is performed by the enzyme as it moves along the DNA strand. It is a Brownian type computational model~\cite{Feynman2018} that driven by the change of entropy.

% TCs are distinguished by their ability to employ the underlying physics of the computing substrate to accomplish a task.
% For example, TCs may employ naturally occurring device-level fluctuations to explore a state space and to stabilize on low-energy representations, which may then be employed in an engineered task.
% TCs are directly connected to real-world potentials, which drive the evolution of their internal organization.
% A user might program constraints that describe an optimization objective over the external potentials and that capture the TC’s natural tendency to maximize entropy production in the environment while minimizing entropy production internally.
% TCs have the potential to be more energy efficient than conventional computers, and they may be able to solve problems that are difficult for conventional computers to solve.
% TCs are still in the early stages of development, but they have the potential to revolutionize computing in the future.

% A thermodynamic computer is a complex system, driven by thermodynamics when exposed to external potentials. Like quantum computers, TCs are distinguished by their ability
% to employ the underlying physics of computing substrate to
% accomplish a task. For example, TCs may employ naturally
% occurring device-level fluctuations to explore a state space
% and to stabilize on low-energy representations, which may
% then be employed in an engineered task~\cite{conte2019thermodynamic}.

% Comparing with all conventional computers fully controlled by humans, the TC, on the other hand, are directly connected to real-world potentials, which drive the
% evolution of its internal organization. As an example of using a TC, a user might program
% constraints that describe an optimization objective
% over the external potentials and that capture the TC’s
% natural tendency to maximize entropy production in the
% environment while minimizing entropy production internally~\cite{conte2019thermodynamic}.

%Quantum annealing outperform classical annealing~\cite{boixo2013experimental, boixo2014evidence}.
%Firstly introduced Rydberg atoms to solve MIS problem with quantum property~\cite{Pichler2018}. Utilized quantum annealing on Rydberg arrays to efficiently solve the combinatorial optimization problem~\cite{Nguyen2023}

%Provided basic knowledge about computational model like DNA Enzyme driven by thermodynamics, raised concepts of reversible computing and gradient power~\cite{Feynman2018}.

%Proved Ising model is capable of universal computation~\cite{gu2012encoding}. Provided Ising formulations of many NP problems~\cite{lucas2014ising}.
%Reviewed various type of Ising machines as hardware analog solvers of combinatorial optimization problems~\cite{mohseni2022ising}.
%A special optical form Ising machine~\cite{fabre2014optical}.
%Other type of TCs like memristors~\cite{yang2013memristive, wang2017memristors, kumar2017chaotic,wang2018fully}, DNA machine~\cite{tanaka2005design}.

\section{Overview of the computation model}\label{sec:Overview-of-main-results}
In this article, We develop a new type of TC shown in \Cref{Surface-programmable-thermodynamic computer}(a), which features a crystalline structure based on a universal elementary cellular automata, makes it easier to be constructed in real life.

\tikzset{every picture/.style={line width=0.75pt}} %set default line width to 0.75pt        
\tikzset {_ue4dovf1e/.code = {\pgfsetadditionalshadetransform{ \pgftransformshift{\pgfpoint{0 bp } { -37.5 bp }  }  \pgftransformrotate{0 }  \pgftransformscale{2 }  }}}
\pgfdeclarehorizontalshading{_qxg3a7xt1}{150bp}{rgb(0bp)=(1,0.33,0);
rgb(37.5bp)=(1,0.33,0);
rgb(49.856583731515066bp)=(1,0.19,0);
rgb(62.5bp)=(1,0.33,0);
rgb(100bp)=(1,0.33,0)}
\tikzset{_licxtq9bp/.code = {\pgfsetadditionalshadetransform{\pgftransformshift{\pgfpoint{0 bp } { -37.5 bp }  }  \pgftransformrotate{0 }  \pgftransformscale{2 } }}}
\pgfdeclarehorizontalshading{_h9amsdqzx} {150bp} {color(0bp)=(transparent!80);
color(37.5bp)=(transparent!80);
color(49.856583731515066bp)=(transparent!30);
color(62.5bp)=(transparent!80);
color(100bp)=(transparent!80) } 
\pgfdeclarefading{_htcz8osfa}{\tikz \fill[shading=_h9amsdqzx,_licxtq9bp] (0,0) rectangle (50bp,50bp); } 
\tikzset{every picture/.style={line width=0.75pt}} %set default line width to 0.75pt

\begin{figure}[h]
    \centering

    \begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1, >=stealth]
    %uncomment if require: \path (0,408); %set diagram left start at 0, and has height of 408

    %Shape: Axis 2D [id:dp47589449610201395] 
    % \draw  (252,306) -- (464.6,306)(252,45.4) -- (252,306) -- cycle (457.6,301) -- (464.6,306) -- (457.6,311) (247,52.4) -- (252,45.4) -- (257,52.4)  ;
    \draw[->][line width=1.5pt] (257,315) -- (464.6,315) node[anchor=north west] {};
    % 绘制 Y 轴
    \draw[->][line width=1.5pt] (257,315) -- (257,45.4) node[anchor=south east] {};
    % \node at (358.3, 306) [anchor=north] {$Time$};
    \draw (358.3,320) node [anchor=north][inner sep=0.75pt]   [align=left] {${Time}$};
    % \node at (252, 175.7) [anchor=east] {$Space$};
    \draw (215,175.7) node [anchor=west][inner sep=0.75pt]   [align=left] {${Space}$};
    %Rounded Rect [id:dp5816101232993451] 
    \path  [shading=_qxg3a7xt1,_ue4dovf1e,path fading= _htcz8osfa ,fading transform={xshift=2}] (281.6,76.28) .. controls (281.6,66.96) and (289.16,59.4) .. (298.48,59.4) -- (349.12,59.4) .. controls (358.44,59.4) and (366,66.96) .. (366,76.28) -- (366,274.52) .. controls (366,283.84) and (358.44,291.4) .. (349.12,291.4) -- (298.48,291.4) .. controls (289.16,291.4) and (281.6,283.84) .. (281.6,274.52) -- cycle ; % for fading 
     % \draw   (281.6,76.28) .. controls (281.6,66.96) and (289.16,59.4) .. (298.48,59.4) -- (349.12,59.4) .. controls (358.44,59.4) and (366,66.96) .. (366,76.28) -- (366,274.52) .. controls (366,283.84) and (358.44,291.4) .. (349.12,291.4) -- (298.48,291.4) .. controls (289.16,291.4) and (281.6,283.84) .. (281.6,274.52) -- cycle ; % for border

    %Straight Lines [id:da12591274303854672] 
    \draw    (286,113.8) -- (296,113.8) ;
    %Straight Lines [id:da6889475605006761] 
    \draw    (306,113.8) -- (326,113.8) ;
    %Straight Lines [id:da6840209064516296] 
    \draw    (346,113.8) -- (366,113.8) ;
    %Straight Lines [id:da5182517300873626] 
    \draw    (286,143.8) -- (296,143.8) ;
    %Straight Lines [id:da6622021804539293] 
    \draw    (306,143.8) -- (326,143.8) ;
    %Straight Lines [id:da10986080077044069] 
    \draw    (346,143.8) -- (366,143.8) ;
    %Straight Lines [id:da06891079444490966] 
    \draw    (286,173.8) -- (296,173.8) ;
    %Straight Lines [id:da7088700201192246] 
    \draw    (306,173.8) -- (326,173.8) ;
    %Straight Lines [id:da8985551907012945] 
    \draw    (346,173.8) -- (366,173.8) ;
    %Straight Lines [id:da48183061562007] 
    \draw    (346,143.8) -- (366,143.8) ;
    %Straight Lines [id:da29259596379627184] 
    \draw    (346,173.8) -- (366,173.8) ;
    %Straight Lines [id:da10525896181304528] 
    \draw    (286,243.8) -- (296,243.8) ;
    %Straight Lines [id:da302504314759217] 
    \draw    (306,243.8) -- (326,243.8) ;
    %Straight Lines [id:da8403039577473146] 
    \draw    (346,243.8) -- (366,243.8) ;
    %Straight Lines [id:da5032229548045282] 
    \draw    (439,243.8) -- (449,243.8) ;
    %Straight Lines [id:da6606636042343228] 
    \draw    (439,173.8) -- (449,173.8) ;
    %Straight Lines [id:da648800320875722] 
    \draw    (439,143.8) -- (449,143.8) ;
    %Straight Lines [id:da3048783844469498] 
    \draw    (439,113.8) -- (449,113.8) ;
    %Shape: Circle [id:dp6177125527635312] 
    \draw  [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ] (309,173.8) .. controls (309,172.14) and (310.34,170.8) .. (312,170.8) .. controls (313.66,170.8) and (315,172.14) .. (315,173.8) .. controls (315,175.46) and (313.66,176.8) .. (312,176.8) .. controls (310.34,176.8) and (309,175.46) .. (309,173.8) -- cycle ;
    %Shape: Circle [id:dp9641797724088836] 
    \draw  [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ] (444,173.8) .. controls (444,172.14) and (445.34,170.8) .. (447,170.8) .. controls (448.66,170.8) and (450,172.14) .. (450,173.8) .. controls (450,175.46) and (448.66,176.8) .. (447,176.8) .. controls (445.34,176.8) and (444,175.46) .. (444,173.8) -- cycle ;
    %Shape: Circle [id:dp5216399345009763] 
    \draw  [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ] (444,243.8) .. controls (444,242.14) and (445.34,240.8) .. (447,240.8) .. controls (448.66,240.8) and (450,242.14) .. (450,243.8) .. controls (450,245.46) and (448.66,246.8) .. (447,246.8) .. controls (445.34,246.8) and (444,245.46) .. (444,243.8) -- cycle ;
    %Shape: Circle [id:dp8730561346145524] 
    \draw  [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ] (444,143.8) .. controls (444,142.14) and (445.34,140.8) .. (447,140.8) .. controls (448.66,140.8) and (450,142.14) .. (450,143.8) .. controls (450,145.46) and (448.66,146.8) .. (447,146.8) .. controls (445.34,146.8) and (444,145.46) .. (444,143.8) -- cycle ;
    %Shape: Circle [id:dp20793574265872938] 
    \draw  [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ] (444,113.8) .. controls (444,112.14) and (445.34,110.8) .. (447,110.8) .. controls (448.66,110.8) and (450,112.14) .. (450,113.8) .. controls (450,115.46) and (448.66,116.8) .. (447,116.8) .. controls (445.34,116.8) and (444,115.46) .. (444,113.8) -- cycle ;
    %Straight Lines [id:da07747816733572055] 
    \draw    (271,113.8) -- (286,113.8) ;
    %Straight Lines [id:da46458200365321267] 
    \draw    (271,143.8) -- (286,143.8) ;
    %Straight Lines [id:da6911160749578646] 
    \draw    (271,173.8) -- (286,173.8) ;
    %Straight Lines [id:da977764753764023] 
    \draw    (271,243.8) -- (286,243.8) ;
    %Shape: Circle [id:dp2077543137374267] 
    \draw  [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ] (268,113.8) .. controls (268,112.14) and (269.34,110.8) .. (271,110.8) .. controls (272.66,110.8) and (274,112.14) .. (274,113.8) .. controls (274,115.46) and (272.66,116.8) .. (271,116.8) .. controls (269.34,116.8) and (268,115.46) .. (268,113.8) -- cycle ;
    %Shape: Circle [id:dp21380722237130656] 
    \draw  [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ] (268,143.8) .. controls (268,142.14) and (269.34,140.8) .. (271,140.8) .. controls (272.66,140.8) and (274,142.14) .. (274,143.8) .. controls (274,145.46) and (272.66,146.8) .. (271,146.8) .. controls (269.34,146.8) and (268,145.46) .. (268,143.8) -- cycle ;
    %Shape: Circle [id:dp1680590103325741] 
    \draw   (268,173.8) .. controls (268,172.14) and (269.34,170.8) .. (271,170.8) .. controls (272.66,170.8) and (274,172.14) .. (274,173.8) .. controls (274,175.46) and (272.66,176.8) .. (271,176.8) .. controls (269.34,176.8) and (268,175.46) .. (268,173.8) -- cycle ;
    %Shape: Circle [id:dp7473613782402011] 
    \draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ] (266.5,173.8) .. controls (266.5,171.31) and (268.51,169.3) .. (271,169.3) .. controls (273.49,169.3) and (275.5,171.31) .. (275.5,173.8) .. controls (275.5,176.29) and (273.49,178.3) .. (271,178.3) .. controls (268.51,178.3) and (266.5,176.29) .. (266.5,173.8) -- cycle ;
    %Curve Lines [id:da44907258759639634] 
    \draw    (278,173.8) .. controls (287.76,173.88) and (282.25,149.83) .. (296,149.8) ;
    %Curve Lines [id:da9408681678935567] 
    \draw    (274,273.8) .. controls (287,273.45) and (282.25,249.83) .. (296,249.8) ;
    %Curve Lines [id:da6386811890007127] 
    \draw    (296,197.8) .. controls (281.95,197.88) and (288.96,174.12) .. (278,173.8) ;
    %Curve Lines [id:da8138750209583685] 
    \draw    (296,107.8) .. controls (281.95,107.88) and (288,83.95) .. (274,83.8) ;
    %Straight Lines [id:da3653413273236392] 
    \draw    (325.5,113.8) -- (335.5,113.8) ;
    %Straight Lines [id:da16432948773608946] 
    \draw    (325.5,143.8) -- (335.5,143.8) ;
    %Straight Lines [id:da6739770002305319] 
    \draw    (325.5,173.8) -- (335.5,173.8) ;
    %Straight Lines [id:da2884180319037881] 
    \draw    (325.5,243.8) -- (335.5,243.8) ;
    %Straight Lines [id:da7251828149781272] 
    \draw    (315,113.8) -- (325.5,113.8) ;
    %Straight Lines [id:da09058450500132387] 
    \draw    (315,143.8) -- (325.5,143.8) ;
    %Straight Lines [id:da3921065083493407] 
    \draw    (315,173.8) -- (325.5,173.8) ;
    %Straight Lines [id:da007877760257336996] 
    \draw    (315,243.8) -- (325.5,243.8) ;
    %Straight Lines [id:da8374371156226426] 
    \draw    (366,113.8) -- (376,113.8) ;
    %Straight Lines [id:da9678309129770906] 
    \draw    (366,143.8) -- (376,143.8) ;
    %Straight Lines [id:da7361499806097593] 
    \draw    (366,173.8) -- (376,173.8) ;
    %Straight Lines [id:da6319078106662868] 
    \draw    (366,243.8) -- (376,243.8) ;
    %Straight Lines [id:da4405211719951492] 
    \draw    (355,113.8) -- (366,113.8) ;
    %Straight Lines [id:da4252229620947994] 
    \draw    (355,143.8) -- (366,143.8) ;
    %Straight Lines [id:da890591025300383] 
    \draw    (355,173.8) -- (366,173.8) ;
    %Straight Lines [id:da9131249668505879] 
    \draw    (355,243.8) -- (366,243.8) ;
    %Straight Lines [id:da7592375019488422] 
    \draw    (399.6,113.76) -- (419.6,113.76) ;
    %Straight Lines [id:da24129797069017322] 
    \draw    (399.6,143.76) -- (419.6,143.76) ;
    %Straight Lines [id:da9245052427082239] 
    \draw    (399.6,173.76) -- (419.6,173.76) ;
    %Straight Lines [id:da7011628293134007] 
    \draw    (399.6,243.76) -- (419.6,243.76) ;
    %Straight Lines [id:da8499202784094941] 
    \draw    (419.1,113.76) -- (429.1,113.76) ;
    %Straight Lines [id:da6204904262909317] 
    \draw    (419.1,143.76) -- (429.1,143.76) ;
    %Straight Lines [id:da03663650815216268] 
    \draw    (419.1,173.76) -- (429.1,173.76) ;
    %Straight Lines [id:da5227514591137388] 
    \draw    (419.1,243.76) -- (429.1,243.76) ;
    %Straight Lines [id:da38681589798229576] 
    \draw    (407.6,113.76) -- (419.1,113.76) ;
    %Straight Lines [id:da54264693532568] 
    \draw    (407.6,143.76) -- (419.1,143.76) ;
    %Straight Lines [id:da32474848386202826] 
    \draw    (407.6,173.76) -- (419.1,173.76) ;
    %Straight Lines [id:da8658223172801294] 
    \draw    (407.6,243.76) -- (419.1,243.76) ;
    %Shape: Circle [id:dp9427971243264817] 
    \draw  [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ] (402,113.8) .. controls (402,112.14) and (403.34,110.8) .. (405,110.8) .. controls (406.66,110.8) and (408,112.14) .. (408,113.8) .. controls (408,115.46) and (406.66,116.8) .. (405,116.8) .. controls (403.34,116.8) and (402,115.46) .. (402,113.8) -- cycle ;
    %Shape: Circle [id:dp46086243960357365] 
    \draw  [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ] (402,143.76) .. controls (402,142.1) and (403.34,140.76) .. (405,140.76) .. controls (406.66,140.76) and (408,142.1) .. (408,143.76) .. controls (408,145.42) and (406.66,146.76) .. (405,146.76) .. controls (403.34,146.76) and (402,145.42) .. (402,143.76) -- cycle ;
    %Shape: Circle [id:dp6620083068720557] 
    \draw  [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ] (402,173.8) .. controls (402,172.14) and (403.34,170.8) .. (405,170.8) .. controls (406.66,170.8) and (408,172.14) .. (408,173.8) .. controls (408,175.46) and (406.66,176.8) .. (405,176.8) .. controls (403.34,176.8) and (402,175.46) .. (402,173.8) -- cycle ;
    %Shape: Circle [id:dp9202066916344684] 
    \draw  [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ] (402,243.8) .. controls (402,242.14) and (403.34,240.8) .. (405,240.8) .. controls (406.66,240.8) and (408,242.14) .. (408,243.8) .. controls (408,245.46) and (406.66,246.8) .. (405,246.8) .. controls (403.34,246.8) and (402,245.46) .. (402,243.8) -- cycle ;
    %Curve Lines [id:da32334900655572585] 
    \draw    (314,273.8) .. controls (327,273.45) and (322.25,249.83) .. (336,249.8) ;
    %Curve Lines [id:da11724765940385651] 
    \draw    (354,273.8) .. controls (367,273.45) and (362.25,249.83) .. (376,249.8) ;
    %Curve Lines [id:da7982105615434423] 
    \draw    (407.1,273.76) .. controls (420.1,273.41) and (415.35,249.79) .. (429.1,249.76) ;
    %Curve Lines [id:da004908421581965694] 
    \draw    (336,107.8) .. controls (321.95,107.88) and (328,83.95) .. (314,83.8) ;
    %Curve Lines [id:da9511690430401551] 
    \draw    (376,107.8) .. controls (361.95,107.88) and (368,83.95) .. (354,83.8) ;
    %Curve Lines [id:da9914997890244512] 
    \draw    (429.1,107.76) .. controls (415.05,107.84) and (421.1,83.91) .. (407.1,83.76) ;
    %Rounded Rect [id:dp42702965624068967] 
    \draw  [fill={rgb, 255:red, 235; green, 83; blue, 112 }  ,fill opacity=1 ] (293.67,104.2) .. controls (293.67,102.87) and (294.74,101.8) .. (296.07,101.8) -- (303.27,101.8) .. controls (304.59,101.8) and (305.67,102.87) .. (305.67,104.2) -- (305.67,123.4) .. controls (305.67,124.73) and (304.59,125.8) .. (303.27,125.8) -- (296.07,125.8) .. controls (294.74,125.8) and (293.67,124.73) .. (293.67,123.4) -- cycle ;
    %Curve Lines [id:da06858342935056427] 
    \draw    (278,143.8) .. controls (287.76,143.88) and (280.18,119.86) .. (293.93,119.83) ;
    %Curve Lines [id:da723298045787133] 
    \draw    (317.5,143.8) .. controls (327.26,143.88) and (321.75,119.83) .. (335.5,119.8) ;
    %Curve Lines [id:da2512187850282652] 
    \draw    (358,143.8) .. controls (367.76,143.88) and (362.25,119.83) .. (376,119.8) ;
    %Curve Lines [id:da9053084993063347] 
    \draw    (411.1,143.76) .. controls (420.86,143.84) and (415.35,119.79) .. (429.1,119.76) ;
    %Curve Lines [id:da92353097157552] 
    \draw    (317.5,173.8) .. controls (327.26,173.88) and (321.75,149.83) .. (335.5,149.8) ;
    %Curve Lines [id:da24776318146114673] 
    \draw    (358,173.8) .. controls (367.76,173.88) and (362.25,149.83) .. (376,149.8) ;
    %Curve Lines [id:da07442995908116457] 
    \draw    (411.1,173.76) .. controls (420.86,173.84) and (415.35,149.79) .. (429.1,149.76) ;
    %Curve Lines [id:da956818800686466] 
    \draw    (278,203.8) .. controls (287.76,203.88) and (282.25,179.83) .. (296,179.8) ;
    %Curve Lines [id:da06594681326228691] 
    \draw    (317.5,203.8) .. controls (327.26,203.88) and (321.75,179.83) .. (335.5,179.8) ;
    %Curve Lines [id:da5916140616891901] 
    \draw    (411.1,203.76) .. controls (420.86,203.84) and (415.35,179.79) .. (429.1,179.76) ;
    %Curve Lines [id:da06825346822128453] 
    \draw    (296,137.8) .. controls (281.95,137.88) and (288.96,114.12) .. (278,113.8) ;
    %Curve Lines [id:da5729440546733633] 
    \draw    (296,167.8) .. controls (281.95,167.88) and (288.96,144.12) .. (278,143.8) ;
    %Curve Lines [id:da2689295741977933] 
    \draw    (335.5,137.8) .. controls (321.45,137.88) and (328.46,114.12) .. (317.5,113.8) ;
    %Curve Lines [id:da8736063287654374] 
    \draw    (335.5,167.8) .. controls (321.45,167.88) and (328.46,144.12) .. (317.5,143.8) ;
    %Curve Lines [id:da315584754437392] 
    \draw    (335.5,197.8) .. controls (321.45,197.88) and (328.46,174.12) .. (317.5,173.8) ;
    %Curve Lines [id:da46919548113502985] 
    \draw    (376,197.8) .. controls (361.95,197.88) and (368.96,174.12) .. (358,173.8) ;
    %Curve Lines [id:da5791093989238294] 
    \draw    (376,167.8) .. controls (361.95,167.88) and (368.96,144.12) .. (358,143.8) ;
    %Curve Lines [id:da2995343957801271] 
    \draw    (376,137.8) .. controls (361.95,137.88) and (368.96,114.12) .. (358,113.8) ;
    %Curve Lines [id:da6279904209902487] 
    \draw    (429.1,137.76) .. controls (415.05,137.84) and (422.06,114.08) .. (411.1,113.76) ;
    %Curve Lines [id:da7566681121693786] 
    \draw    (429.1,167.76) .. controls (415.05,167.84) and (422.06,144.08) .. (411.1,143.76) ;
    %Curve Lines [id:da7687108096378197] 
    \draw    (429.1,197.76) .. controls (415.05,197.84) and (422.06,174.08) .. (411.1,173.76) ;
    %Curve Lines [id:da9906758036883361] 
    \draw    (278,243.8) .. controls (287.76,243.88) and (282.25,219.83) .. (296,219.8) ;
    %Curve Lines [id:da6426692743902085] 
    \draw    (317.5,243.8) .. controls (327.26,243.88) and (321.75,219.83) .. (335.5,219.8) ;
    %Curve Lines [id:da7324254375871793] 
    \draw    (358,243.8) .. controls (367.76,243.88) and (362.25,219.83) .. (376,219.8) ;
    %Curve Lines [id:da03023041445865271] 
    \draw    (411.1,243.76) .. controls (420.86,243.84) and (415.35,219.79) .. (429.1,219.76) ;
    %Curve Lines [id:da6837151140111912] 
    \draw    (296,237.8) .. controls (281.95,237.88) and (288.96,214.12) .. (278,213.8) ;
    %Curve Lines [id:da7387383084996648] 
    \draw    (335.5,237.8) .. controls (321.45,237.88) and (328.46,214.12) .. (317.5,213.8) ;
    %Curve Lines [id:da9210010738401084] 
    \draw    (429.1,237.76) .. controls (415.05,237.84) and (422.06,214.08) .. (411.1,213.76) ;
    %Shape: Circle [id:dp20146326966731642] 
    \draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ] (308.5,173.8) .. controls (308.5,171.31) and (310.51,169.3) .. (313,169.3) .. controls (315.49,169.3) and (317.5,171.31) .. (317.5,173.8) .. controls (317.5,176.29) and (315.49,178.3) .. (313,178.3) .. controls (310.51,178.3) and (308.5,176.29) .. (308.5,173.8) -- cycle ;
    %Shape: Circle [id:dp4487595160974982] 
    \draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ] (266.5,143.8) .. controls (266.5,141.31) and (268.51,139.3) .. (271,139.3) .. controls (273.49,139.3) and (275.5,141.31) .. (275.5,143.8) .. controls (275.5,146.29) and (273.49,148.3) .. (271,148.3) .. controls (268.51,148.3) and (266.5,146.29) .. (266.5,143.8) -- cycle ;
    %Shape: Circle [id:dp9195781546216495] 
    \draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ] (266.5,113.8) .. controls (266.5,111.31) and (268.51,109.3) .. (271,109.3) .. controls (273.49,109.3) and (275.5,111.31) .. (275.5,113.8) .. controls (275.5,116.29) and (273.49,118.3) .. (271,118.3) .. controls (268.51,118.3) and (266.5,116.29) .. (266.5,113.8) -- cycle ;
    %Shape: Circle [id:dp6116837286965402] 
    \draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ] (269.5,83.8) .. controls (269.5,81.31) and (271.51,79.3) .. (274,79.3) .. controls (276.49,79.3) and (278.5,81.31) .. (278.5,83.8) .. controls (278.5,86.29) and (276.49,88.3) .. (274,88.3) .. controls (271.51,88.3) and (269.5,86.29) .. (269.5,83.8) -- cycle ;
    %Shape: Circle [id:dp3625678025113275] 
    \draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ] (308.5,143.8) .. controls (308.5,141.31) and (310.51,139.3) .. (313,139.3) .. controls (315.49,139.3) and (317.5,141.31) .. (317.5,143.8) .. controls (317.5,146.29) and (315.49,148.3) .. (313,148.3) .. controls (310.51,148.3) and (308.5,146.29) .. (308.5,143.8) -- cycle ;
    %Shape: Circle [id:dp03312322880961438] 
    \draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ] (308.5,113.8) .. controls (308.5,111.31) and (310.51,109.3) .. (313,109.3) .. controls (315.49,109.3) and (317.5,111.31) .. (317.5,113.8) .. controls (317.5,116.29) and (315.49,118.3) .. (313,118.3) .. controls (310.51,118.3) and (308.5,116.29) .. (308.5,113.8) -- cycle ;
    %Shape: Circle [id:dp043865844405652554] 
    \draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ] (309.5,83.8) .. controls (309.5,81.31) and (311.51,79.3) .. (314,79.3) .. controls (316.49,79.3) and (318.5,81.31) .. (318.5,83.8) .. controls (318.5,86.29) and (316.49,88.3) .. (314,88.3) .. controls (311.51,88.3) and (309.5,86.29) .. (309.5,83.8) -- cycle ;
    %Shape: Circle [id:dp21578576624907608] 
    \draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ] (349.5,83.8) .. controls (349.5,81.31) and (351.51,79.3) .. (354,79.3) .. controls (356.49,79.3) and (358.5,81.31) .. (358.5,83.8) .. controls (358.5,86.29) and (356.49,88.3) .. (354,88.3) .. controls (351.51,88.3) and (349.5,86.29) .. (349.5,83.8) -- cycle ;
    %Shape: Circle [id:dp28073888823911486] 
    \draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ] (349,113.8) .. controls (349,111.31) and (351.01,109.3) .. (353.5,109.3) .. controls (355.99,109.3) and (358,111.31) .. (358,113.8) .. controls (358,116.29) and (355.99,118.3) .. (353.5,118.3) .. controls (351.01,118.3) and (349,116.29) .. (349,113.8) -- cycle ;
    %Shape: Circle [id:dp5081744133289241] 
    \draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ] (349,143.8) .. controls (349,141.31) and (351.01,139.3) .. (353.5,139.3) .. controls (355.99,139.3) and (358,141.31) .. (358,143.8) .. controls (358,146.29) and (355.99,148.3) .. (353.5,148.3) .. controls (351.01,148.3) and (349,146.29) .. (349,143.8) -- cycle ;
    %Shape: Circle [id:dp01748356301794951] 
    \draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ] (349,173.8) .. controls (349,171.31) and (351.01,169.3) .. (353.5,169.3) .. controls (355.99,169.3) and (358,171.31) .. (358,173.8) .. controls (358,176.29) and (355.99,178.3) .. (353.5,178.3) .. controls (351.01,178.3) and (349,176.29) .. (349,173.8) -- cycle ;
    %Shape: Circle [id:dp2526359291560343] 
    \draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ] (266.5,243.8) .. controls (266.5,241.31) and (268.51,239.3) .. (271,239.3) .. controls (273.49,239.3) and (275.5,241.31) .. (275.5,243.8) .. controls (275.5,246.29) and (273.49,248.3) .. (271,248.3) .. controls (268.51,248.3) and (266.5,246.29) .. (266.5,243.8) -- cycle ;
    %Shape: Circle [id:dp30795312394062346] 
    \draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ] (269.5,273.8) .. controls (269.5,271.31) and (271.51,269.3) .. (274,269.3) .. controls (276.49,269.3) and (278.5,271.31) .. (278.5,273.8) .. controls (278.5,276.29) and (276.49,278.3) .. (274,278.3) .. controls (271.51,278.3) and (269.5,276.29) .. (269.5,273.8) -- cycle ;
    %Shape: Circle [id:dp6531679226550287] 
    \draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ] (309.5,273.8) .. controls (309.5,271.31) and (311.51,269.3) .. (314,269.3) .. controls (316.49,269.3) and (318.5,271.31) .. (318.5,273.8) .. controls (318.5,276.29) and (316.49,278.3) .. (314,278.3) .. controls (311.51,278.3) and (309.5,276.29) .. (309.5,273.8) -- cycle ;
    %Shape: Circle [id:dp23741910846556058] 
    \draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ] (349.5,273.8) .. controls (349.5,271.31) and (351.51,269.3) .. (354,269.3) .. controls (356.49,269.3) and (358.5,271.31) .. (358.5,273.8) .. controls (358.5,276.29) and (356.49,278.3) .. (354,278.3) .. controls (351.51,278.3) and (349.5,276.29) .. (349.5,273.8) -- cycle ;
    %Shape: Circle [id:dp8799962376767778] 
    \draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ] (308.5,243.8) .. controls (308.5,241.31) and (310.51,239.3) .. (313,239.3) .. controls (315.49,239.3) and (317.5,241.31) .. (317.5,243.8) .. controls (317.5,246.29) and (315.49,248.3) .. (313,248.3) .. controls (310.51,248.3) and (308.5,246.29) .. (308.5,243.8) -- cycle ;
    %Shape: Circle [id:dp5436648552880832] 
    \draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ] (349,243.8) .. controls (349,241.31) and (351.01,239.3) .. (353.5,239.3) .. controls (355.99,239.3) and (358,241.31) .. (358,243.8) .. controls (358,246.29) and (355.99,248.3) .. (353.5,248.3) .. controls (351.01,248.3) and (349,246.29) .. (349,243.8) -- cycle ;
    %Shape: Circle [id:dp4508122471949372] 
    \draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ] (402.6,83.76) .. controls (402.6,81.27) and (404.61,79.26) .. (407.1,79.26) .. controls (409.59,79.26) and (411.6,81.27) .. (411.6,83.76) .. controls (411.6,86.25) and (409.59,88.26) .. (407.1,88.26) .. controls (404.61,88.26) and (402.6,86.25) .. (402.6,83.76) -- cycle ;
    %Shape: Circle [id:dp7623420038386579] 
    \draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ] (402,113.8) .. controls (402,111.31) and (404.01,109.3) .. (406.5,109.3) .. controls (408.99,109.3) and (411,111.31) .. (411,113.8) .. controls (411,116.29) and (408.99,118.3) .. (406.5,118.3) .. controls (404.01,118.3) and (402,116.29) .. (402,113.8) -- cycle ;
    %Shape: Circle [id:dp6338949287421527] 
    \draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ] (402.1,143.76) .. controls (402.1,141.27) and (404.11,139.26) .. (406.6,139.26) .. controls (409.09,139.26) and (411.1,141.27) .. (411.1,143.76) .. controls (411.1,146.25) and (409.09,148.26) .. (406.6,148.26) .. controls (404.11,148.26) and (402.1,146.25) .. (402.1,143.76) -- cycle ;
    %Shape: Circle [id:dp9494208779127] 
    \draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ] (402,173.8) .. controls (402,171.31) and (404.01,169.3) .. (406.5,169.3) .. controls (408.99,169.3) and (411,171.31) .. (411,173.8) .. controls (411,176.29) and (408.99,178.3) .. (406.5,178.3) .. controls (404.01,178.3) and (402,176.29) .. (402,173.8) -- cycle ;
    %Shape: Circle [id:dp7362804325370593] 
    \draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ] (402,243.8) .. controls (402,241.31) and (404.01,239.3) .. (406.5,239.3) .. controls (408.99,239.3) and (411,241.31) .. (411,243.8) .. controls (411,246.29) and (408.99,248.3) .. (406.5,248.3) .. controls (404.01,248.3) and (402,246.29) .. (402,243.8) -- cycle ;
    %Shape: Circle [id:dp9761672870224487] 
    \draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ] (402.6,273.76) .. controls (402.6,271.27) and (404.61,269.26) .. (407.1,269.26) .. controls (409.59,269.26) and (411.6,271.27) .. (411.6,273.76) .. controls (411.6,276.25) and (409.59,278.26) .. (407.1,278.26) .. controls (404.61,278.26) and (402.6,276.25) .. (402.6,273.76) -- cycle ;
    %Shape: Circle [id:dp3587618015248244] 
    \draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ] (444,113.8) .. controls (444,111.31) and (446.01,109.3) .. (448.5,109.3) .. controls (450.99,109.3) and (453,111.31) .. (453,113.8) .. controls (453,116.29) and (450.99,118.3) .. (448.5,118.3) .. controls (446.01,118.3) and (444,116.29) .. (444,113.8) -- cycle ;
    %Shape: Circle [id:dp257482515582123] 
    \draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ] (444,143.8) .. controls (444,141.31) and (446.01,139.3) .. (448.5,139.3) .. controls (450.99,139.3) and (453,141.31) .. (453,143.8) .. controls (453,146.29) and (450.99,148.3) .. (448.5,148.3) .. controls (446.01,148.3) and (444,146.29) .. (444,143.8) -- cycle ;
    %Shape: Circle [id:dp8680615145799881] 
    \draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ] (444,173.8) .. controls (444,171.31) and (446.01,169.3) .. (448.5,169.3) .. controls (450.99,169.3) and (453,171.31) .. (453,173.8) .. controls (453,176.29) and (450.99,178.3) .. (448.5,178.3) .. controls (446.01,178.3) and (444,176.29) .. (444,173.8) -- cycle ;
    %Shape: Circle [id:dp4306579762720619] 
    \draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ] (444,243.8) .. controls (444,241.31) and (446.01,239.3) .. (448.5,239.3) .. controls (450.99,239.3) and (453,241.31) .. (453,243.8) .. controls (453,246.29) and (450.99,248.3) .. (448.5,248.3) .. controls (446.01,248.3) and (444,246.29) .. (444,243.8) -- cycle ;
    %Rounded Rect [id:dp9521886425866692] 
    \draw  [fill={rgb, 255:red, 235; green, 83; blue, 112 }  ,fill opacity=1 ] (293.67,134.2) .. controls (293.67,132.87) and (294.74,131.8) .. (296.07,131.8) -- (303.27,131.8) .. controls (304.59,131.8) and (305.67,132.87) .. (305.67,134.2) -- (305.67,153.4) .. controls (305.67,154.73) and (304.59,155.8) .. (303.27,155.8) -- (296.07,155.8) .. controls (294.74,155.8) and (293.67,154.73) .. (293.67,153.4) -- cycle ;
    %Rounded Rect [id:dp9007360317843287] 
    \draw  [fill={rgb, 255:red, 235; green, 83; blue, 112 }  ,fill opacity=1 ] (293.7,164.2) .. controls (293.7,162.87) and (294.77,161.8) .. (296.1,161.8) -- (303.3,161.8) .. controls (304.63,161.8) and (305.7,162.87) .. (305.7,164.2) -- (305.7,183.4) .. controls (305.7,184.73) and (304.63,185.8) .. (303.3,185.8) -- (296.1,185.8) .. controls (294.77,185.8) and (293.7,184.73) .. (293.7,183.4) -- cycle ;
    %Rounded Rect [id:dp7755940946979027] 
    \draw  [fill={rgb, 255:red, 235; green, 83; blue, 112 }  ,fill opacity=1 ] (293.7,233.87) .. controls (293.7,232.54) and (294.77,231.47) .. (296.1,231.47) -- (303.3,231.47) .. controls (304.63,231.47) and (305.7,232.54) .. (305.7,233.87) -- (305.7,253.07) .. controls (305.7,254.39) and (304.63,255.47) .. (303.3,255.47) -- (296.1,255.47) .. controls (294.77,255.47) and (293.7,254.39) .. (293.7,253.07) -- cycle ;
    %Rounded Rect [id:dp3770236077825324] 
    \draw  [fill={rgb, 255:red, 235; green, 83; blue, 112 }  ,fill opacity=1 ] (333.67,104.2) .. controls (333.67,102.87) and (334.74,101.8) .. (336.07,101.8) -- (343.27,101.8) .. controls (344.59,101.8) and (345.67,102.87) .. (345.67,104.2) -- (345.67,123.4) .. controls (345.67,124.73) and (344.59,125.8) .. (343.27,125.8) -- (336.07,125.8) .. controls (334.74,125.8) and (333.67,124.73) .. (333.67,123.4) -- cycle ;
    %Rounded Rect [id:dp2955229197086444] 
    \draw  [fill={rgb, 255:red, 235; green, 83; blue, 112 }  ,fill opacity=1 ] (333.67,134.2) .. controls (333.67,132.87) and (334.74,131.8) .. (336.07,131.8) -- (343.27,131.8) .. controls (344.59,131.8) and (345.67,132.87) .. (345.67,134.2) -- (345.67,153.4) .. controls (345.67,154.73) and (344.59,155.8) .. (343.27,155.8) -- (336.07,155.8) .. controls (334.74,155.8) and (333.67,154.73) .. (333.67,153.4) -- cycle ;
    %Rounded Rect [id:dp3257551753328596] 
    \draw  [fill={rgb, 255:red, 235; green, 83; blue, 112 }  ,fill opacity=1 ] (333.7,164.2) .. controls (333.7,162.87) and (334.77,161.8) .. (336.1,161.8) -- (343.3,161.8) .. controls (344.63,161.8) and (345.7,162.87) .. (345.7,164.2) -- (345.7,183.4) .. controls (345.7,184.73) and (344.63,185.8) .. (343.3,185.8) -- (336.1,185.8) .. controls (334.77,185.8) and (333.7,184.73) .. (333.7,183.4) -- cycle ;
    %Rounded Rect [id:dp5015753026325627] 
    \draw  [fill={rgb, 255:red, 235; green, 83; blue, 112 }  ,fill opacity=1 ] (333.7,233.57) .. controls (333.7,232.24) and (334.77,231.17) .. (336.1,231.17) -- (343.3,231.17) .. controls (344.63,231.17) and (345.7,232.24) .. (345.7,233.57) -- (345.7,252.77) .. controls (345.7,254.09) and (344.63,255.17) .. (343.3,255.17) -- (336.1,255.17) .. controls (334.77,255.17) and (333.7,254.09) .. (333.7,252.77) -- cycle ;
    %Rounded Rect [id:dp0888424840477875] 
    \draw  [fill={rgb, 255:red, 235; green, 83; blue, 112 }  ,fill opacity=1 ] (427.7,103.87) .. controls (427.7,102.54) and (428.77,101.47) .. (430.1,101.47) -- (437.3,101.47) .. controls (438.63,101.47) and (439.7,102.54) .. (439.7,103.87) -- (439.7,123.07) .. controls (439.7,124.39) and (438.63,125.47) .. (437.3,125.47) -- (430.1,125.47) .. controls (428.77,125.47) and (427.7,124.39) .. (427.7,123.07) -- cycle ;
    %Rounded Rect [id:dp7785611532578929] 
    \draw  [fill={rgb, 255:red, 235; green, 83; blue, 112 }  ,fill opacity=1 ] (427.7,134.2) .. controls (427.7,132.87) and (428.77,131.8) .. (430.1,131.8) -- (437.3,131.8) .. controls (438.63,131.8) and (439.7,132.87) .. (439.7,134.2) -- (439.7,153.4) .. controls (439.7,154.73) and (438.63,155.8) .. (437.3,155.8) -- (430.1,155.8) .. controls (428.77,155.8) and (427.7,154.73) .. (427.7,153.4) -- cycle ;
    %Rounded Rect [id:dp7907921203888848] 
    \draw  [fill={rgb, 255:red, 235; green, 83; blue, 112 }  ,fill opacity=1 ] (427.73,164.2) .. controls (427.73,162.87) and (428.81,161.8) .. (430.13,161.8) -- (437.33,161.8) .. controls (438.66,161.8) and (439.73,162.87) .. (439.73,164.2) -- (439.73,183.4) .. controls (439.73,184.73) and (438.66,185.8) .. (437.33,185.8) -- (430.13,185.8) .. controls (428.81,185.8) and (427.73,184.73) .. (427.73,183.4) -- cycle ;
    %Rounded Rect [id:dp8701852355059259] 
    \draw  [fill={rgb, 255:red, 235; green, 83; blue, 112 }  ,fill opacity=1 ] (427.73,233.9) .. controls (427.73,232.57) and (428.81,231.5) .. (430.13,231.5) -- (437.33,231.5) .. controls (438.66,231.5) and (439.73,232.57) .. (439.73,233.9) -- (439.73,253.1) .. controls (439.73,254.43) and (438.66,255.5) .. (437.33,255.5) -- (430.13,255.5) .. controls (428.81,255.5) and (427.73,254.43) .. (427.73,253.1) -- cycle ;

%Straight Lines [id:da7675709313550161] 
\draw [dashed]   (424.25,128.9) -- (424.25,158.9) ;
%Straight Lines [id:da5513222139736342] 
\draw [dashed]   (424.25,128.9) -- (443.15,128.9) ;
%Straight Lines [id:da5724218915400858] 
% \draw [dashed]   (448.31,132.74) -- (472.65,132.7) ;
\draw[->][line width=1.0pt] (468,170.7) -- (446,154.7) ;
%Straight Lines [id:da98028289030947] 
\draw  [dashed]  (424.25,158.9) -- (443.15,158.85) ;
%Straight Lines [id:da3690262092301855] 
\draw  [dashed]  (443.15,128.9) -- (443.15,158.85) ;

%Shape: Circle [id:dp3980815479811872] 
\draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ] (491,154.1) .. controls (491,151.61) and (493.01,149.6) .. (495.5,149.6) .. controls (497.99,149.6) and (500,151.61) .. (500,154.1) .. controls (500,156.59) and (497.99,158.6) .. (495.5,158.6) .. controls (493.01,158.6) and (491,156.59) .. (491,154.1) -- cycle ;
%Shape: Circle [id:dp8208493476316323] 
\draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ] (491,191.1) .. controls (491,188.61) and (493.01,186.6) .. (495.5,186.6) .. controls (497.99,186.6) and (500,188.61) .. (500,191.1) .. controls (500,193.59) and (497.99,195.6) .. (495.5,195.6) .. controls (493.01,195.6) and (491,193.59) .. (491,191.1) -- cycle ;
%Shape: Circle [id:dp3173494411067954] 
\draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ] (478.67,172.6) .. controls (478.67,170.11) and (480.68,168.1) .. (483.17,168.1) .. controls (485.65,168.1) and (487.67,170.11) .. (487.67,172.6) .. controls (487.67,175.09) and (485.65,177.1) .. (483.17,177.1) .. controls (480.68,177.1) and (478.67,175.09) .. (478.67,172.6) -- cycle ;
%Shape: Circle [id:dp967421569400009] 
\draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ] (503.4,172.6) .. controls (503.4,170.11) and (505.41,168.1) .. (507.9,168.1) .. controls (510.39,168.1) and (512.4,170.11) .. (512.4,172.6) .. controls (512.4,175.09) and (510.39,177.1) .. (507.9,177.1) .. controls (505.41,177.1) and (503.4,175.09) .. (503.4,172.6) -- cycle ;
%Shape: Circle [id:dp938870324276512] 
\draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ] (524.7,172.5) .. controls (524.7,170.01) and (526.71,168) .. (529.2,168) .. controls (531.69,168) and (533.7,170.01) .. (533.7,172.5) .. controls (533.7,174.99) and (531.69,177) .. (529.2,177) .. controls (526.71,177) and (524.7,174.99) .. (524.7,172.5) -- cycle ;
%Rounded Rect [id:dp40904235215635065] 
\draw  [fill={rgb, 255:red, 235; green, 83; blue, 112 }  ,fill opacity=1 ] (475.6,155.04) .. controls (475.6,148.59) and (480.83,143.36) .. (487.28,143.36) -- (525.12,143.36) .. controls (531.57,143.36) and (536.8,148.59) .. (536.8,155.04) -- (536.8,190.08) .. controls (536.8,196.53) and (531.57,201.76) .. (525.12,201.76) -- (487.28,201.76) .. controls (480.83,201.76) and (475.6,196.53) .. (475.6,190.08) -- cycle ;
%Straight Lines [id:da6938220604961829] 
\draw    (491,154.1) -- (469.8,154.1) ;
%Straight Lines [id:da05667244881651223] 
\draw    (478.67,172.47) -- (469.8,172.5) ;
%Straight Lines [id:da7336130308225484] 
\draw    (491,191.1) -- (469.8,191.1) ;
%Straight Lines [id:da9632416883191204] 
\draw    (483.17,172.6) -- (495.5,154.1) ;
%Straight Lines [id:da8062551247029028] 
\draw    (483.17,172.6) -- (495.5,191.1) ;
%Straight Lines [id:da6815111207533529] 
\draw    (495.5,154.1) -- (507.9,172.6) ;
%Straight Lines [id:da2583696463055196] 
\draw    (495.5,191.1) -- (507.9,172.6) ;
%Straight Lines [id:da5112788448231447] 
\draw    (483.17,172.6) -- (507.9,172.6) ;
%Straight Lines [id:da21092112099851623] 
\draw    (495.5,191.1) -- (495.5,154.1) ;
%Curve Lines [id:da6381556136782309] 
\draw    (495.5,191.1) .. controls (509.12,191.04) and (521.92,189.04) .. (529.2,172.5) ;
%Curve Lines [id:da40382455887046964] 
\draw    (495.5,154.1) .. controls (511.92,153.84) and (524.32,158.24) .. (529.2,172.5) ;
%Curve Lines [id:da518536427411914] 
\draw    (529.2,172.5) .. controls (514.32,159.44) and (495.92,161.04) .. (483.17,172.6) ;
%Curve Lines [id:da5213323072929468] 
\draw    (529.2,172.5) .. controls (523.52,180.64) and (511.92,179.84) .. (507.9,172.6) ;
%Straight Lines [id:da26081701800713075] 
\draw    (533.7,172.5) -- (541.8,172.5) ;
%Shape: Circle [id:dp28592847133985866] 
\draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ] (478.67,172.6) .. controls (478.67,170.11) and (480.68,168.1) .. (483.17,168.1) .. controls (485.65,168.1) and (487.67,170.11) .. (487.67,172.6) .. controls (487.67,175.09) and (485.65,177.1) .. (483.17,177.1) .. controls (480.68,177.1) and (478.67,175.09) .. (478.67,172.6) -- cycle ;
%Shape: Circle [id:dp7005363351052425] 
\draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ] (491,154.1) .. controls (491,151.61) and (493.01,149.6) .. (495.5,149.6) .. controls (497.99,149.6) and (500,151.61) .. (500,154.1) .. controls (500,156.59) and (497.99,158.6) .. (495.5,158.6) .. controls (493.01,158.6) and (491,156.59) .. (491,154.1) -- cycle ;
%Shape: Circle [id:dp5131516311175763] 
\draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ] (491,191.1) .. controls (491,188.61) and (493.01,186.6) .. (495.5,186.6) .. controls (497.99,186.6) and (500,188.61) .. (500,191.1) .. controls (500,193.59) and (497.99,195.6) .. (495.5,195.6) .. controls (493.01,195.6) and (491,193.59) .. (491,191.1) -- cycle ;
%Shape: Circle [id:dp38829310474408074] 
\draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ] (503.4,172.6) .. controls (503.4,170.11) and (505.41,168.1) .. (507.9,168.1) .. controls (510.39,168.1) and (512.4,170.11) .. (512.4,172.6) .. controls (512.4,175.09) and (510.39,177.1) .. (507.9,177.1) .. controls (505.41,177.1) and (503.4,175.09) .. (503.4,172.6) -- cycle ;
%Shape: Circle [id:dp6003377245628321] 
\draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ] (524.7,172.5) .. controls (524.7,170.01) and (526.71,168) .. (529.2,168) .. controls (531.69,168) and (533.7,170.01) .. (533.7,172.5) .. controls (533.7,174.99) and (531.69,177) .. (529.2,177) .. controls (526.71,177) and (524.7,174.99) .. (524.7,172.5) -- cycle ;

    % Text Node
    \draw (379,111.8) node [anchor=north west][inner sep=0.75pt]   [align=left] {$\displaystyle \cdots $};
    % Text Node
    \draw (379,141.8) node [anchor=north west][inner sep=0.75pt]   [align=left] {$\displaystyle \cdots $};
    % Text Node
    \draw (379,172.09) node [anchor=north west][inner sep=0.75pt]   [align=left] {$\displaystyle \cdots $};
    % Text Node
    \draw (379,241.8) node [anchor=north west][inner sep=0.75pt]   [align=left] {$\displaystyle \cdots $};
    % Text Node
    \draw (283,193.97) node [anchor=north west][inner sep=0.75pt]   [align=left] {$\displaystyle \vdots $};
    % Text Node
    \draw (322.5,193.97) node [anchor=north west][inner sep=0.75pt]   [align=left] {$\displaystyle \vdots $};
    % Text Node
    \draw (363,193.97) node [anchor=north west][inner sep=0.75pt]   [align=left] {$\displaystyle \vdots $};
    % Text Node
    \draw (420.1,194) node [anchor=north west][inner sep=0.75pt]   [align=left] {$\displaystyle \vdots $};
    % Text Node
    \draw (382.4,194.52) node [anchor=north west][inner sep=0.75pt]   [align=left] {$\displaystyle \ddots $};
    % Text Node
    \draw (292,45) node [anchor=north west][inner sep=0.75pt]   [align=left] {${Heat\ Zone}$};
    % Text Node
    \draw (220.87,45.67) node [anchor=north west][inner sep=3pt]   [align=left] {\large {$\displaystyle \mathtt{(a)}$}};
    % Text Node
    \draw (490.67,121.47) node [anchor=north west][inner sep=3pt]   [align=left] {\large {$\displaystyle \mathtt{(b)}$}};
    % Text Node
    \draw (492.43,150.41) node [anchor=north west][inner sep=0.75pt]   [align=left] {{\tiny {\fontfamily{ptm}\selectfont p}}};
    % Text Node
    \draw (479.75,168.95) node [anchor=north west][inner sep=0.75pt]   [align=left] {{\fontfamily{ptm}\selectfont {\tiny q}}};
    % Text Node
    \draw (492.83,188.12) node [anchor=north west][inner sep=0.75pt]   [align=left] {{\tiny {\fontfamily{ptm}\selectfont r}}};
    % Text Node
    \draw (525.34,167.95) node [anchor=north west][inner sep=0.75pt]   [align=left] {{\tiny {\fontfamily{ptm}\selectfont q'}}};
    % Text Node
    \draw (504.00,168.45) node [anchor=north west][inner sep=0.75pt]   [align=left] {{\tiny {\fontfamily{ptm}\selectfont A}}};

    \draw [<->] [line width=1.0] (283.2, 295.4) -- (365.2, 295.4) ;
    \draw [->] [line width=1.0] (310, 73) -- (337, 73);
    % \draw   (283.2,286.4) .. controls (283.2,291.07) and (285.53,293.4) .. (290.2,293.4) -- (314.2,293.4) .. controls (320.87,293.4) and (324.2,295.73) .. (324.2,300.4) .. controls (324.2,295.73) and (327.53,293.4) .. (334.2,293.4)(331.2,293.4) -- (358.2,293.4) .. controls (362.87,293.4) and (365.2,291.07) .. (365.2,286.4) ;    \draw   [->] (312.63,73.33) -- (336.63,73.33) ;
    % Text Node
    \draw (319.33,63.67) node [anchor=north west][inner sep=0.75pt]   [align=left] {$\displaystyle v$};
    % Text Node
    \draw (306.20,298.47) node [anchor=north west][inner sep=0.75pt]   [align=left] {$\displaystyle Width$};

    \end{tikzpicture}
    \caption{Surface programmable thermodynamic computer (TC) and rule110 automata gadget. $\mathtt{(a)}$ Example of a surface programmable TC with a moving heat bath slowly doing ``calculation''. White circles are spins and black lines represent interaction between spins, while red rectangles represent cellular automata gadget. $\mathtt{(b)}$ Example of a rule110 gadget. Here spins $p$, $q$, and $r$ represent the left, middle, and right states in the cellular automata, respectively, while $q^\prime$ represents the result computed by the cellular automata, and $A$ is an auxiliary spin. We define a spin pointing up as representing logical 1 and pointing down as representing logical 0. \jinguo{why capital A? q' not clear.}}
    \label{Surface-programmable-thermodynamic computer}
\end{figure}

The physical implementation of the TC is based on spins, with computational information encoded in the orientation of the spins, represented by white circles, while the red box represents a logic circuit, composed of several spins. The horizontal axis represents the number of computational layers, with spins belonging to the same computational layer sharing the same horizontal coordinate, and vertical axis represents the number of spins in each layer.

The input layer consists of the leftmost spin, while the output layer consists of the rightmost spin. The entire computing process can be described by gradually moving the external heat bath, which creates a temperature gradient and, consequently, a heat zone, from the input layer to the output layer. By utilizing thermal fluctuations from the heat bath, the spins in different layers sequentially settle into low-energy states within the state space, effectively completing the iterative computation of the cellular automata.

Users can design the computing algorithm and obtain the desired output by setting the input configuration and then making slight movements to the external heat bath, requiring only approximately linear time (up to a $\log^2$ factor) with respect to the number of layers.

\section{Model and Method}\label{sec:model-method}

\subsection{Elementary cellular automata}\label{elementary-cellular-automata}
In cellular automata (CA), `space' is a regular lattice of `cells', each of which contains one of a small allowed set of integers.
Only cells that are close together interact in one `time-step'-the time evolution is given by a rule that looks at the contents of a few neighbouring cells, and decides what should change. At each step, this local rule is applied everywhere simultaneously~\cite{}.
Depending on different rules, some CAs can be more complex than others.
The most interesting category is those proved to be universal~\cite{Berlekamp2004}, meaning that they can simulate any computer program. The best-known examples in two-dimensional include Conway's~\cite{Games1970} ``Game of Life'', Margolus's reversible cellular automata~\cite{Margolus1984} and its quantum version~\cite{Arrighi2012}.
The simplest universal CA is a 1-dimensional cellular automata, namely, the rule 110 CA~\cite{Cook2009}.
This CA is an elementary CA that defined on a one dimensional grid, each cell has two possible states (labeled by 0 and 1). The rule of an elementary CA to determine the state of the cell in next generation depends only on the current state of the cell and its two immediate neighbors. The number of possible elementary CA rules is the same as the number of 3-input Boolean functions, which is $2^{2^3} = 256$. The Boolean function for rule 110 is shown in the following table:

\begin{tabular}{|c|c|c|c|c|c|c|c|c|}
\hline
Current Pattern & 111 & 110 & 101 & 100 & 011 & 010 & 001 & 000 \\
\hline
New Center Cell & 0 & 1 & 1 & 0 & 1 & 1 & 1 & 0 \\
\hline
\end{tabular}

The name of the rule comes from the binary representation of the rule number, which is 110 in decimal.
Let us denote the states of the three cells as $p$, $q$, and $r$, from left to right, respectively. The rule 110 can be expressed as the following Boolean function:
\begin{equation}\label{eq:110rule}
    q^\prime = r \land \neg (q \land \neg p)
\end{equation}
where $q^\prime$ is the state of the center cell in the next generation.

\subsection{Mapping CA to Ising model}

An $n$-vertex fully connected spin-glass Hamiltonian is described as follows.

\begin{equation}
H = \sum_{i < j} J_{ij}s_us_v + \sum_{i=1}^{n}h_i s_i
\end{equation}

where $h_i$ is onsite energy, $J_{ij}$ is interaction energy and
$s_i \in \{-1, 1\}$ is local spin. $s_i=1$ means spin-up and $s_i=-1$ means spin-down.

Previous studies have shown that the Ising model is universal for computation~\cite{Aadit2022, onizawa2020design, camsari2017stochastic}, meaning that any logic circuit can be encoded into the Ising model and solved by finding the ground state of the Ising model. A universal set logic gate gadgets are designed, by concatenating which any logic circuit can be constructed.
For example the logic expression $z = \neg (x \land y)$ can be encoded into the Ising model by the following Hamiltonian:
\begin{equation}
    \begin{split}
        H_{c = a \land b} &= s_a s_b -2 s_a s_c -2 s_bs_c + s_a + s_b -2 s_c\\
        H_{z = \neg c} &= s_c s_z\\
        H_{z = \neg (a \land b)} &= H_{z = \neg c} + H_{c = a \land b}
    \end{split}
\end{equation}
where, the variable $c$ is an ancilla spin.
A cellular automata can be viewed as a translational invariant logic circuit, and thus can be encoded into the Ising model. The ground states of the Ising model encode the correspondence between the inputs and the outputs of the cellular automata.
Directly synthesizing the logic circuit for the universal $110$ rule (\Cref{eq:110rule}) requires at least 3 ancilla spins, which is far from optimal. By converting the gadget finding problem to a linear programming problem~\cite{}, we propose a provable optimal method to encode any cellular automata rule into the Ising model, which is described in \Cref{sec:gadget-design}.
The proposed gadget for the $110$ rule is shown in \Cref{Surface-programmable-thermodynamic computer}(b), which only requires 1 ancilla spin.
The interaction energy and onsite energy of the rule 110 gadget are given below, where $p, q, r$ and inputs and $q'$ is the output in \Cref{Surface-programmable-thermodynamic computer}(b), respectively, while spin $A$ is the auxiliary spin.
\begin{equation}
J = \begin{blockarray}{cccccc}
& p & q & r & q^\prime & A\\
\begin{block}{c(ccccc)}
p & ~\cdot~ & ~1~ & ~1~ & ~2~ & ~3~\\
q & \cdot & \cdot & 2 & 2 & 5\\
r & \cdot & \cdot & \cdot & 2 & 5\\
q^\prime & \cdot & \cdot & \cdot & \cdot & 6\\
A & \cdot & \cdot & \cdot & \cdot & \cdot\\
\end{block}
\end{blockarray}
~~, ~~h = \begin{blockarray}{cc}
& \phantom{x} \\
\begin{block}{c(c)}
p & ~1~\\
q & 2\\
r & 2\\
q^\prime & 2\\
A & 5\\
\end{block}
\end{blockarray}
\end{equation}
Since a copy gate\jinguo{do we really use copy gates?} can be simply described as two spins with an interaction $J_{u, v}=1$, and by applying the method of connecting logic gates~\cite{Aadit2022}, we can concatenate the rule 110 gadget with some copy gates, ultimately forming the TC shown in [Fig. \ref{Surface-programmable-thermodynamic computer}(a)]. The gadget we constructed based on the Rule 110 cellular automata
naturally possesses Turing completeness. Therefore, this 2-dimensional TC is capable of universal computing.

\subsection{Cooling computation with a moving heat bath}\label{cooling-computation-with-moving-heat-bath}

The computational process of the cellular automata is divided into three steps: determining the state of each input cell, iteratively applying the transition rules to generate the next generation of cells, and identifying a certain generation of cells as the output. In fact, the width of the time axis in the Ising TC corresponds to the number of iterations. Hence, the smallest layer of spins on the time axis should be the input layer, and the largest layer of spins should be the output layer.

Given that each ground state of the TC corresponds to a valid computational process of the cellular automata for a given input, the computational process of the TC is essentially reduced to finding the ground state of the TC with the spin configuration in the input layers fixed.

We focus here on the thermodynamics-driven approach to finding ground states, specifically the heating-annealing method. This involves gradually increasing and then decreasing the temperature of the heat bath with which the TC interacts. The TC may employ heat fluctuations to explore a state space in the first stage and stabilize on ground state during the second stage as long as the annealing stage is long enough. However, it is convinced that this stage can last for exponential time for some hard spin-glass problems.

Due to the structure of the TC, we can allow only a portion of the system, rather than the entire system, to interact with the heat bath, while ignoring the interaction energy between the boundary spins and the exterior. After completing the heating-annealing procedure on one part of the system, we move the heat bath to another part and repeat the same process. This approach effectively finds a local ground state for each part of the system, which is reasonable when the global ground state can be divided into multiple local components.

More specifically, the computation, progressing from the input layer to the output layer, involves the following steps: (1) Initialize the input layer configuration by adjusting the onsite energy for each spin. (2) Determine the number of layers $W$ that will interact with the external heat bath in each heating-annealing process. Group the layers in sets of $W$ from input to output, labeling them as groups $1, 2, \cdots, \frac{T}{W}$. The number of heating-annealing repetitions will then be $\frac{T}{W}$, where T is the total number of layers. (3) Perform the heating-annealing process on each group sequentially.

However, solving the ground state from the non-deterministic direction is at least as hard as solving the circuit satisfiability problem, which is NP-complete~\cite{Moore2011}.

% \subsection{Cooling computation with direction}\label{sec:direction}

% Definitions: * \emph{in-surface/out-suface}: The surface of a surface
% programmable material that associated with the input/output of the logic
% circuit.

% The process of heating and annealing the entire material does not have computational capability, as the system lacks logical directionality.

% Logical directionality needs to be introduced through an orderly annealing method. 
% Similar to the localized heating-annealing approach that catalyzes the growth of ordered crystals, we introduced a temperature gradient annealing scheme.

% More specifically, the computation, with computing direction from in-surface to out-surface, contains the following steps: (1). Initialize the in-surface configuration. By removing
% some atoms on the in-surface. (2). Connect the in-surface/out-surface to
% external heat sources at temperature $T_1 < T_2$, respectively. We
% also require that the energy gap between the ground state and the first
% excited state of the Hamiltonian to be $\Delta E< T_1$. (3). Lower the
% temperature of the heat sources ``slowly'' to cool the system to the
% ground state of the Hamiltonian. The temperature of the heat sources at
% time $t$ is $T_{1/2}(t) = T_{1/2}(0)\lambda^{-c t}$, where
% $T_{1/2}(0)$ is the initial temperature of the heat sources, and
% $\alpha$ is a constant.

% The computing direction could be reversed by swaping the temperature of the heat sources connected in-surface and out-surface.
% However, solving the ground state from the non-deterministic direction is at least as hard as solving the circuit satisfiability problem, which is NP-complete~\cite{Moore2011}.

\subsection{Computing by cooling}\label{local-cooling}

We test the hypothesis: Cooling is easy if the process is from the
deterministic direction, hard if the process is from the
non-deterministic direction.

\begin{hyp}
Let $\mathcal{P}$ be a circuit SAT problem, and $\mathcal{E}$ be an energy modeling encoding of $\mathcal{P}$ (locally). There exists a subset of $\mathcal{E}$ that exhibits the overlap gap property~\cite{Gamarnik2021}.
\end{hyp}
The overlap gap property is a property for describing the algorithmic intractability in random structures, which is based on the topological disconnectivity property of the set of pair-wise distances of near optimal solutions.
If the energy landscape of a optimization problem exhibits the overlap gap property, then it can not be solved by any local algorithms in polynomial time, including the simulated annealing method used in this work.
The intuition comes from the energy model encoding of the identity circuit.
Given a circuit with $n$ bits, the ground state degeneracy of the corresponding energy model is at least $2^n$.
The energy model can be vertically stacked $n$ copy gadgets.
Let the circuit depth be $d \sim 2^{\gamma \sqrt{n}}$ for some constant $\gamma > 0$.
The Hamming distance between two degenerate ground states for different input signals is at least $d$, which is exponential to $n$. Let us define the size of the problem as $d\times n$, then this distance is clearly linear to the problem size. We left the rigorous proof of this hypothesis to mathematicians.

In our gadget, cooling from deterministic direction is from input to
output, non-deterministic direction is from output to input. The latter
one must be non-deterministic because this gadget is Turing-Complete.

The goal is to drive the the \textbf{state} to the one with lowest energy as fast as possible, while some bits set to be 1 or 0 in the \textbf{state}.

\subsubsection{Estimation of the computing time along computation direction}\label{estimation-of-the-computing-time}

\ym{This part should be rewrote in future..My words are so poor.}

Let us initially treat the heat bath as ideal, assuming that the temperature within the interacting region of the system is uniform and that the temperature outside this region is zero. We refer to the interacting region as the ``Heat Zone''.

Assume there is an annealing procedure that may prevent the layers in the Heat Zone from stabilizing in the local ground state, or equivalently, that an error occurs in the computation process with a probability $\epsilon$. Repeating this procedure $\frac{T}{W}$ times would result in a probability of $(1-\epsilon)^{\frac{T}{W}}$ to successfully find the proper global ground state. To maintain a constant success probability as $T \rightarrow +\infty$, the error probability $\epsilon$ should scale as $\frac{W}{T}$.

Now we turn to determining the annealing time $t_{th}$ required to achieve an error probability $\epsilon$ in each Heat Zone. Let $\lambda_1$ and $\lambda_2$ be the largest and second largest eigenvalues of the Markov transition matrix, respectively. The relationship between $\frac{\lambda_2}{\lambda_1}$ and $W$ can be expressed as $1 - \frac{\lambda_2}{\lambda_1} \sim e^{-W}$. Consequently, a relationship exists between $t_{th}$ and $\epsilon$, which is given by:

\begin{equation}
    \left( \frac{\lambda_2}{\lambda_1} \right) ^ {t_{th}} = \epsilon \rightarrow t_{th} \sim \ln(\frac{T}{W})e^{W}
\end{equation}

And the total annealing time scale as $\frac{T}{W}\ln(\frac{T}{W})e^W$.

In practice, temperature changes cannot occur instantaneously, and the temperature distribution within the heating zone may not be uniform. Thus, it is necessary to account for the effective width of the Heat Zone when the the heat bath are not ideal.

Suppose the middle of the heat bath is at $middle(t)$, and the temperature at the region with a Time coordinate $x$ can be represent as $Temp(x) \propto \Lambda^{-|x - middle(t)|}$. Then

\begin{equation}
    e^{-\Delta E \Lambda^{cW}} \sim \epsilon \sim \frac{W}{T}
\end{equation}

Where $c$ is the empirical constant for effective width and can be determined during the experiment. The total annealing time should be

\begin{equation}
    t_{total} = \frac{T}{W}(\ln(\frac{T}{W}))^{1+ \frac{1}{c\ln(\Lambda)}}
\end{equation}

\subsubsection{Estimation of the computing time along input memory direction}\label{Estimation-of-the-computing-time-along-input-memory-direction}

We fixed the number of layers and denote $n$ as the width of each layer in this material.

However, we fail to derive an explicitly expression for the time complexity in this direction. 
Numerical result shows that computing complexity is linear to $n$. Thus a total time
for the computation should scale as $nm\log^2(m)e^{(1-\lambda)^{-1}}$

\subsubsection{Testing model through equilibrilium SA}\label{temperature-gradient-and-energy-gradient}

We used simulated annealing to mimic the heating-annealing process.
However, classical simulated annealing can only handle the situation
where the temperature is space-invariant. Thus, a scheme change is needed.

One can simply
make the following modification to the transition probability in the
markov process and return to the situation, called energy-gradient scheme, where the temperature is space-invariant.

\begin{equation}
e^{-\frac{\Delta E_k}{T\lambda^{ct+k}}} = e^{-\frac{\Delta E_k(\frac{1}{\lambda})^k}{T\lambda^{ct}}} = e^{-\frac{\Delta E_k \Lambda^k}{T(t)}}
\end{equation}

Where we denote $\Lambda = \frac{1}{\lambda}$ and the time complexity in $\Lambda$ form is apparently
$T_{total} \sim \frac{m}{W}\log^2(\frac{m}{W})e^{(\Lambda-1)^{-1}}$

\subsection{Algorithm beyond temperature
gradient}\label{algorithm-beyond-temperature-gradient}

Applying a huge energy gradient or temperature gradient to this material
seems not a good idea when the system become larger.

Inspired by the way clothes are ironed, we conceived an idea called wave-packet scheme, that slowly
scanning a wave-shaped temperature curve from one end to the other. This
method is widely used in studying the heating-recrystallization
properties of real materials~\cite{Zhang2014}.

\begin{figure}[h]
\centering
\includegraphics[width=\columnwidth]{../notes/images/zhang2014.png}
\caption{Method to scan the wave packet}
\end{figure}

There are various specific choices for the wave packet, such as
power-law, exponential, and others. In this context, we primarily focus
on a exponential wave packet, which can be directly linked to the
concept of energy gradient.

A expoential wave packet with central position $middle(t)$, amplitude
$A$ and base $\Lambda$, can be express as following.

\[
T(k,t) = A\Lambda^{|k-middle(t)|}
\]

So slowly moving the wave packet means slowly changing $middle(t)$

Let's review the concept \textbf{active zone} defined earlier. When the
temperature of the system is defined as
$T_{tg}(k, t) = T\lambda^{ct-k}$, atoms in the active zone are those
whose layer $k$ belongs to $k<ct - \frac{W}{2}$, where $W$ are
given by
$e^{-\frac{\Delta E_{max}}{\lambda^{\frac{W}{2}}}}\leq \epsilon$. For
those $k<ct - \frac{W}{2}$, the probability that SA would flip an
atom's state is no more than
$e^{-\frac{\Delta E_{max}}{T\lambda^{ct}\lambda^{-ct + \frac{W}{2}}}}=e^{-\frac{\Delta E_{max}}{T\lambda^{\frac{W}{2}}}}\leq \epsilon^{\frac{1}{T}}$,
which means these previous layer would stay ``frozen''. For those layer
much deeper than $k = ct$, SA would just randomly flip them. These
layer won't affect layers in active zone.

Now turn our sight into the wave packet model, we can construct a
similar concept \textbf{heat zone}. Layers in the heat zone are those
$A\lambda^{|k-middle(t)|}\ge \epsilon\rightarrow middle(t) + \frac{\log(\epsilon)}{\log(\Lambda)}< k < middle(t) - \frac{\log(\epsilon)}{\log(\Lambda)}$.

The layers that shallower than
$middle(t) + \frac{\log(\epsilon)}{\log(\Lambda)}$ correspond to
layers shallower than $ct-\frac{W}{2}$ in temperature gradient model,
since they are both stay ``frozen''; layers between
$middle(t) +\frac{\log(\epsilon)}{\log(\Lambda)}$ and $middle(t)$
are effectively cooled down, which correspond to the \textbf{active
zone}; layers deeper than $middle(t)$ are either randomly fliped or
stay ``frozen'', but we don't care their state.

Therefore, the wave packet model are just the same as the temperature
gradient model, and is more likely to be realized physically.

\subsubsection{Some details about non-equilibrium simulated
annealing}\label{some-details-about-non-equilibrium-simulated-annealing}

The classical simulated annealing can only deal with the situation that
the temperature is space-invariant. Although there are many ways to
simulated a real-world system with temperature gradient, such as
Molecular Dynamics \cite{Bai2015, Deng2006}, but
these methods mainly depend on dynamically adjusting the atomic
velocities to achieve a temperature gradient, which can't be directly
used in our model.

There are also Monte Carlo-based methods to simulate a moving
temperature wave packet that facilitates material growth~\cite{Godfrey1995, Tan2017}.
However, these methods fail to establish a direct connection between the simulated temperature and experimental
temperature~\cite{Zollner2014}.
Therefore, based on HeatBath acceptance rule, we made a slight modification to the classical SA model.

When we flip one atom's state, there would be some energy difference
$\Delta E_{i}$ in field $i$ with temperature $T_i$. The
probability to accept this flip would be

\begin{equation}
P = \frac{1}{1 + e^{\sum_i \frac{\Delta E_i}{T_i}}}
\end{equation}

It is easily to observe that when the system returns to
heat-equilibrium, the probability reverts to the classical HeatBath
acceptance probability.
\section{Numerical simulation}\label{sec:numerical-result}

\subsection{Energy model}\label{a-2d-surface-programmable-material}

Given that simulating a cellular automata with a deep computational layer on the Ising model requires a large number of spins, making large-scale numerical simulations impractical, we opted to introduce a similar but simpler energy model to observe the behavior on a larger scale.

Let us define a model Hamiltonian on a 2D lattice of size $S \times T$ as
\begin{equation}\label{eq:toy-hamiltonian}
H = \sum_{t=1}^{T-1}\sum_{i=1}^{S} (n_{i+1, t} \land \neg(n_{i, t} \land \neg n_{i-1, t})) \veebar n_{i,t+1},
\end{equation}
where $n_{i, t} \in \{0, 1\}$ is the state of the cell at row $i$ and column $t$, the boundary is periodic in the space direction, i.e. $n_{0, t} = n_{S, t}$.
Its ground state with energy $0$ encodes a $110$ cellular automata, where the direction of computation is from the left to right.
\subsection{Numerical result}

We conducted numerical experiments both for energy-gradient and wave-packet scheme, under the condition
$\Lambda = 1.3, n = 15$ , and fitted each sweep time against
$m \log^2(m)$. Where $m$ represents the number of the single layers,
$n$ represents the width per single layer.

\begin{figure}[h]
    \centering
    \includegraphics[width=\columnwidth,keepaspectratio]{../notes/images/numercial result.pdf}
    \caption{Time v.s. Depth of the material}
\end{figure}

Another numerical experiment are conducted to determine the time complexity of the computation along the input memory direction.

\begin{figure}[H]
    \centering
    \includegraphics[width=\columnwidth,keepaspectratio]{../notes/images/toymodel_time_vs_width.png}
    \caption{Time v.s. width of the material}
\end{figure}

This indeed informs that the time scale along the memory direction is linear.

\section{Physical implementation on Ising machine}\label{spin-glass}

To examine whether this model could achieve a better performance when
using adiabatic methods, we need to generalize this energy function to
some good hamiltonian. There has already been work on mapping
combinatorial optimization problems to a spin-glass model (known as the
Ising Machine) and leveraging the properties of digital devices that
simulate this Ising Machine to find an appropriate ground state, which
encodes computational information~\cite{Aadit2022,Bybee2023}.

\section{Discussion and Outlook}
Connect real-world thermalization time and the simulated annealing time to explore the connection between time and energy cost per computation.
The emergence of wisdom?

Potential advantages: energy saving, parallelism, no size limits (robust to quantum effects). Disadvantages: slow, error-prone.

\begin{acknowledgments}
    We thank Lei Wang, Madelyn Cain and XXX for helpful discussions on the simulation methods.
\end{acknowledgments}

%\bibliographystyle{apsrev4-1}
\bibliography{refs.bib}

\appendix

\section{Ising machine gadget design}\label{sec:gadget-design}
To map our toy model in \Cref{eq:toy-hamiltonian} to
spin-glass model, we used Linear Programming algorithm.
Linear problems are problems that can be express in standard form as

\begin{equation}
    \begin{split}
        &\min_{x \in \mathbb{R}^n} \sum_{i=1}^n c_ix_i\\
        &\text{s.t. } l_j \leq \sum_{i=1}^n a_{i,j}x_i \leq u_j, \; j=1,\ldots,m\\
        &p_i \leq x_i \leq q_i, \; i=1,\ldots, n
    \end{split}
\end{equation}

Here with a spin-glass consists $N$ atoms, we choose $n$ to be $\frac{N(N-1)}{2} + N$, which means each variable $x_i$ represents a correspond interaction energy $J_{u, v}$ or a correspond onsite energy $h_u$, we assigned aliases to these $x_i$ as $x_{u,v}$ or $x_{u}$.

Let the configuration space of the system be $S = \{\mathbf s_i\mid i=1,\ldots, 2^N\}$, each associated with an energy $H(\mathbf s_i)$. We denote the target states with minimum energy as $S_{\text{min}} \subseteq S$. We can express the linear programming problem as

\begin{equation}
    \begin{split}
        &\min_{J \in \mathbb{R}^{N(N{-}1)/2}, h\in \mathbb{R}^N} 0\\
        &H(\mathbf s_i) < H(\mathbf s_j), \forall \mathbf s_i \in S_{\text{min}}, \mathbf s_j \in S \setminus S_{\text{min}}\\
        &H(\mathbf s_i) = H(\mathbf s_j), \forall \mathbf s_i, \mathbf s_j \in S_{\text{min}}
    \end{split}
\end{equation}

Note that $H$ is a linear function of $J$ and $h$, so the
constraints are linear. The less constraints and equality constraints
can be easily transformed into inequality constraints by adding ancilla
variables.

There is no solution with 4-atoms spin-glass that can satisfy the
constraints. The minimum number of atoms required to satisfy the
constraints is 5. We set the target states to

\begin{table}[H]
    \centering
\begin{tabular}{|c|c|c|c|c|}
\hline
input 1 & input 2 & input 3 & output & ancilla \\
\hline
$\downarrow$ & $\downarrow$ & $\downarrow$ & $\downarrow$ & $?$ \\
$\downarrow$ & $\downarrow$ & $\uparrow$ & $\uparrow$ & $?$ \\
$\downarrow$ & $\uparrow$ & $\downarrow$ & $\uparrow$ & $?$ \\
$\downarrow$ & $\uparrow$ & $\uparrow$ & $\uparrow$ & $?$ \\
$\uparrow$ & $\downarrow$ & $\downarrow$ & $\downarrow$ & $?$ \\
$\uparrow$ & $\downarrow$ & $\uparrow$ & $\uparrow$ & $?$ \\
$\uparrow$ & $\uparrow$ & $\downarrow$ & $\uparrow$ & $?$ \\
$\uparrow$ & $\uparrow$ & $\uparrow$ & $\downarrow$ & $?$ \\
\hline
\end{tabular}
\caption{The eight degenerate ground states of the spin-glass model to implement the $110$ rule.}
\end{table}

where the ancilla bit in each row can be either $\uparrow$ or
$\downarrow$ (256 total possibilities). One of the solutions
satisfying the constraints is

\begin{equation}
J = \begin{pmatrix}
~\cdot~ & ~1~ & ~1~ & ~2~ & ~3~\\
\cdot & \cdot & 2 & 2 & 5\\
\cdot & \cdot & \cdot & 2 & 5\\
\cdot & \cdot & \cdot & \cdot & 6\\
\cdot & \cdot & \cdot & \cdot & \cdot
\end{pmatrix}, h = \begin{pmatrix}
~1~\\
2\\
2\\
2\\
5
\end{pmatrix}
\end{equation}

\section{The implmentation in Rydberg atoms array}\label{physical-model-rydberg-atoms-array}
Let us consider a Rydberg atoms array with a two dimensional embedding. The coordinate of the atom $v$ is denoted as $\mathbf{r}_v$.
The Rydberg Hamiltonian~\cite{Nguyen2023} is defined as

\begin{equation}
    H_{\text{Ryd}} = \sum_v \dfrac{\Omega_v}{2} \sigma^x_v -\sum_v \Delta_v n_v + \sum_{v < w}  V_{\text{Ryd}}(|\overrightarrow{\mathbf{r}_v} -\overrightarrow{\mathbf{r}_w}|)n_v n_w,
\end{equation}
where $\Omega_v$ is the Rabi frequency, $\Delta_v$ is the detuning,
$n_v = \dfrac{1}{2}(1 - \sigma^z_v)$ is the number operator, and
$V_{\text{Ryd}}(|\overrightarrow{\mathbf{r}_v} - \overrightarrow{\mathbf{r}_w}|) = C_6/|\overrightarrow{\mathbf{r}_v} - \overrightarrow{\mathbf{r}_w}|^6$
is the Rydberg interaction potential.

In the following, we will show the classical part of the Rydberg Hamiltonian encodes an independent set problem on a unit disk graph.
In graph theory, an independent set is a set of vertices in a graph, no two of which are adjacent.
Here, we restrict the graph to be a two dimensional unit disk graph $G=(V, E)$, a geometric graph with two dimensional embedding, such that two vertices $u, v \in V$ are connected if and only if they are within the unit radius, i.e. $|\mathbf r_u - \mathbf r_v| < r_B$. This reflects the blockade phenomenon in Rydberg atoms arrays, where two atoms within blockade radius $r_B$ can not excite to the Rydberg state simultaneously due to the strong Rydberg interaction potential. Let us idealize the energy model by treating the blockade interaction between two atoms as infinity if two atoms are within blockade radius, zero otherwise. Then the energy model becomes
\begin{equation}
H_{\text{MWIS}} = -\sum_{v \in V}\Delta_v n_v + \sum_{(u, v) \in E} \infty n_u n_v.
\end{equation}
The ground state of which encodes the maximum weight independent set (MWIS) problem, and $\Delta_v$ is the weight associated with vertex $v \in V$. Whenever we have a atom in the Rydberg state in the ground state of $H_{\text{WMIS}}$, we add the vertex associated with that atom to the maximum independent set.

\subsection{Gadget finding}
Given a target logic gate, the goal is to find a graph $G = (V, E)$ and weights associated with vertices $\{\Delta_v \mid v\in V\}$ such that the WMIS problem of this graph encodes this gate.

Let $\mathcal{M}$ be the set of all maximal independent sets of $G$, where a maximal independent set is an independent set that is not a subset of any other independent set.
Each $\mathbf n \in \mathcal{M}$ is associated with an energy $H_{\text{WMIS}}(\mathbf n) = -\sum_v \Delta_v n_v$. We denote the target states with minimum energy as $\mathcal{M}_{\text{min}} \subseteq \mathcal{M}$. We can express the linear programming problem as

\begin{equation}
    \begin{split}
        &\min_{\boldsymbol{\Delta} \in \mathbb{R}^{|V|}} 0\\
        &\sum_i n_i' \Delta_i < \sum_i n_i \Delta_i, \forall \mathbf n \in \mathcal{M}_{\text{min}}, \mathbf n' \in \mathcal{M} \setminus \mathcal{M}_{\text{min}}\\
        &\sum_i n_i \Delta_i = \sum_i n_i' \Delta_i, \forall \mathbf n, \mathbf n' \in \mathcal{M}_{\text{min}}
    \end{split}
\end{equation}

Note that the constraints are all linear. The less constraints and equality constraints can be easily transformed into inequality constraints by adding ancilla variables.
The possible choice of $S_{\text{min}}$ grows exponentially as the number of ancilla vertices increases, which limits the capability of this method.
\jinguo{We focus on the general graphs first.}

In the following, we restrict the graph to be two dimensional grid graphs, the unit distance can be arbitrary. A graph configuration can be denoted as a boolean mask $M\in \{0, 1\}^{m\times n}$.
\jinguo{Then the unit disk graphs.}

\subsubsection{Energy based universal computation with Rydberg atoms
array}\label{energy-based-universal-computation-with-rydberg-atoms-array}

\textbf{Statement 3}: The classical Rydberg Hamiltonian is universal for classical computation.

The NOR gate can be implemented using the Rydberg Hamiltonian (subfigure
c below). The NOR gate is a universal gate for classical computation.
\includegraphics[width=\columnwidth]{../notes/images/gadgets.png}

The conjunction of gates can be implemented by ``gluing'' the Rydberg
atoms together (subfigure d below). The weights are added together.

For more logic gates, please check the GitHub repository
\href{https://github.com/QuEraComputing/UnitDiskMapping.jl/blob/main/test/logicgates.jl}{UnitDiskMapping.jl}.

\subsubsection{Cooling the Rydberg Hamiltonian}\label{cooling-the-rydberg-hamiltonian}

\textbf{Statement 4}: The Rydberg Hamiltonian, if cooled successfully
with some vertices fixed to certain configuration, can be used to solve
the circuit satisfiability problem, which is NP-complete~\cite{Moore2011}.

$P \neq NP$: Cooling is generally hard, especially when from the
non-deterministic direction.

\subsubsection{The Rule 110 Gadget}\label{the-rule-110-gadget}

We can encode the Rule 110 cellular automata into a Weighted Maximum
Independent Set Problem, with blue vertices assigned a weight of 1 and
red vertices assigned a weight of 2, as follows.

\includegraphics[width=0.6\columnwidth]{../notes/images/image.png}

This graph can be embedded into a grid graph, where two vertices are
connected if and only if their Euclidean distance is no more than $2$.

\includegraphics[width=0.7\columnwidth]{../notes/images/image-1.png}

The correspondence between the Maximum Weighted Independent Set (MWIS)
Solution and Rule 110 is as follows:

The states of vertex \textbf{1}, vertex \textbf{3}, and vertex
\textbf{8} represent the states of the \textbf{middle}, \textbf{left},
and \textbf{right} cells of the automata's \textbf{input},
respectively. If the input value of a cell is 1, then the corresponding
vertex must be in the MWIS solution; otherwise, it is not. Vertex
\textbf{12} corresponds to the automata's \textbf{output}. If the
automata output is 1, then vertex 12 is in the MWIS solution;
otherwise, it is not.

In the automata diagram, the above gadget is equivalent to:

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{../notes/images/rule110.png}
\caption{Alt text}
\end{figure}

There are exactly \textbf{8} different MWIS solutions in this graph (the
weighted size of each MWIS solution is 7), each corresponding to one of
the \textbf{8} possible outputs of the automata. We list them as
follows.
\includegraphics[width=\columnwidth]{../notes/images/gadget110.png}

Utilizing copy gadget and cross gadget~\cite{Nguyen2023}, we construct a \textbf{Surface Programmable Material} with open boundary conditions as follows.

\begin{figure}
\centering
\includesvg[width=\columnwidth]{../notes/images/rule110transvarient.svg}
\caption{Alt text}
\end{figure}

The above gadget depicts a two-layer cellular automata. The vertices in
blue, red, green and black have weights of 1, 2, 3 and 4, respectively.
In the automata diagram, the above gadget is equivalent to:

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{../notes/images/rule110_2-2_automata.png}
\caption{Alt text}
\end{figure}

\subsection{Speed and work}\label{speed-and-work}

The trade-off between the energy consumption and the speed of
computation~\cite{Feynman2018}. To avoid confusion, we emphasize the
``energy consumption'' is defined as the work done in a computational
process, which is the same as the amount of heat dissipated to the
environment. This quantity has a lower bound given by the Landauer
principle, which states that the work done in a computation is at least
$kT\ln 2$ per bit erased\cite{Reeb2014}.

Information erasure in the surface programmable material is proportional
to the volume of the material, which is $O(tS)$, where $t$ is the
time of computation, and $S$ is memory (proportional to the surface
area) of the material.

From the chemical reaction perspective, the speed of computation is
determined by the parameter $\lambda$.

\subsubsection{Quantum adiabatic annealing energy gap}\label{quantum-adiabatic-annealing-energy-gap}

One possible way is to use quantum adiabatic annealing: start from a
simple hamiltonian $H(0)$ and its simple ground state
$|\psi(0)\rangle$, then gradually change the parameters until reaching
the desire hamiltonian $H(t)$.

More specifically, set $\Delta(t=0) <0$ and $\Omega(t=0) =0$
initially, then first turning on $\Omega(t)$ to a non-zero value,
sweeping $\Delta(t)$ to final value, and finally turning off
$\Omega(t)$.

\begin{equation}
H_{QAA}(t) = \sum_{v\in V} (-\Delta(t)w_v \hat n_v + \Omega(t)\sigma_{v}^x) + \sum_{(u,w) \in E} U\hat n_u \hat n_w
\end{equation}

If the time evolution is sufficiently slow, then by the adiabatic
theorem, the system follows the instantaneous ground state, ending up in
the solution to the MWIS problem~\cite{Pichler2018}.
Then we only need to evalute
the minimum energy gap $\Delta_{QAA}$ between the ground and
first-excited states of instantaneous hamiltonian.

We set $\Omega = 1 \times 2\pi$ and sweep the $\Delta$ from $3
\times 2\pi$ to $40 \times 2\pi$ with 1*1 gadget. For deterministic
direction, we simply set the weight of the input vertices to $50$; as
for non-deterministic direction, we set the weight of the output vertice
to $50$.

Result listed as follows. \textbf{However, we didn't see cooling from
deterministic direction would give a smaller energy gap than the other
direction. We think that's because the size of this gadget is too
small.}

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{../notes/images/energy_gap_1_gadget.png}
\caption{Alt text}
\end{figure}

\section{Classical Dynamics}\label{classical-dynamics-1}
We firstly tried classical adiabatic annealing with the classical-spin
mapping method~\cite{Wang2013}
\begin{equation}
\frac{\partial \vec M_i}{\partial t} = \vec M_{i} \times \vec H_{i}(t)
\end{equation}

where

\begin{equation}
\vec H_i(t) = -\frac{\partial H(t)}{\partial \vec M_i} 
\end{equation}

Here the hamiltonian of the system is

\begin{equation}
H(t) = \frac{t}{T}(\sum_{u,v}J_{u,v} M_{u,z}M_{v,z} + \sum_{u} h_u M_{u, z}) + (1-\frac{t}{T})(I\sum_{u}M_{u,x})
\end{equation}

The former term is the generally increasing target hamiltonian, the
latter term is a generally decreasing known Ising-transverse field. We
can explicitly write out the effective magnetic field.

\[
\vec H_{i}(t) = -\frac{t}{T}(\sum_{v}J_{i, v}M_{v,z} + h_i)\hat e_z - (1-\frac{t}{T})I\hat e_x
\]

Integrate the ordinary differential equation then we get the classical
dynamics of this spin-glass model. However, result shows that it is
extremely hard to find the solution when the number of layers exceed
$4$ (input layer is pinned).

The reason maybe that the mapped spin-glass model lies in the hard
region in ~\cite{Wang2013}. Because every interaction energy is positive, which
gives rise to strong frustration. Results in this reference also shows that even in
random spin-glass model, there exist hard instance that can't be solve.

\end{document}

### 2024-09-04 paper/main.tex
update

@@
 
-\title{Surface programmable materials}
+\title{Crystal as a Thermodynamic Computer}
 
@@
 \begin{abstract}
+    Thermodynamic computers are believed to be more energy efficient than conventional computers, however, a practical implementation of a thermodynamic computer is still challenging.
+In this paper, we propose a thermodynamics driven computer that enables use to perform computation by editing its surface.
+    The crystalline structure is based on a universal elementary cellular automata, and is translational invariant in all spacial dimensions.
+The translational invariance not only makes the crystal easier to be constructed in nature, but also enables the study of the scaling behavior the thermalization process.
 \end{abstract}

### 2024-09-04 paper/main.tex
update

@@
 In this paper, we propose a thermodynamics driven computer that enables use to perform computation by editing its surface.
-    The crystalline structure is based on a universal elementary cellular automata, and is translational invariant in all spacial dimensions.
+    The crystalline structure is based on a universal elementary CA, and is translational invariant in all spacial dimensions.
 The translational invariance not only makes the crystal easier to be constructed in nature, but also enables the study of the scaling behavior the thermalization process.
@@
 Intrigued by the question of how to thermalize and lower the energy of an Ising machine, we propose a new type of TC that has a crystalline structure.
-The crystalline structure is based on a universal elementary cellular automata, and is translational invariant in all spacial dimensions.
+The crystalline structure is based on a universal elementary CA, and is translational invariant in all spacial dimensions.
 The translational invariance not only makes the crystal easier to be constructed in nature, but also enables the study of the scaling behavior the thermalization process.
@@
 \section{Overview of the computation model}\label{sec:Overview-of-main-results}
-In this article, We develop a new type of TC shown in \Cref{Surface-programmable-thermodynamic computer}(a), which features a crystalline structure based on a universal elementary cellular automata, makes it easier to be constructed in real life.
+In this article, We develop a new type of TC shown in \Cref{Surface-programmable-thermodynamic computer}(a), which features a crystalline structure based on a universal elementary CA, makes it easier to be constructed in real life.
 
@@
 $\mathtt{(a)}$ Example of a surface programmable TC with a moving heat bath slowly doing ``calculation''.
-White circles are spins and black lines represent interaction between spins, while red rectangles represent cellular automata gadget.
+White circles are spins and black lines represent interaction between spins, while red rectangles represent CA gadget.
 $\mathtt{(b)}$ Example of a rule110 gadget.
@@
 The entire computing process can be described by gradually moving the external heat bath, which creates a temperature gradient and, consequently, a heat zone, from the input layer to the output layer.
-By utilizing thermal fluctuations from the heat bath, the spins in different layers sequentially settle into low-energy states within the state space, effectively completing the iterative computation of the cellular automata.
+By utilizing thermal fluctuations from the heat bath, the spins in different layers sequentially settle into low-energy states within the state space, effectively completing the iterative computation of the CA.
 
@@
 The most interesting category is those proved to be universal~\cite{Berlekamp2004}, meaning that they can simulate any computer program.
-The best-known examples in two-dimensional include Conway's~\cite{Games1970} ``Game of Life'', Margolus's reversible cellular automata~\cite{Margolus1984} and its quantum version~\cite{Arrighi2012}.
-The simplest universal CA is a 1-dimensional cellular automata, namely, the rule 110 CA~\cite{Cook2009}.
+The best-known examples in two-dimensional include Conway's~\cite{Games1970} ``Game of Life'', Margolus's reversible CA~\cite{Margolus1984} and its quantum version~\cite{Arrighi2012}.
+The simplest universal CA is a 1-dimensional CA, namely, the rule 110 CA~\cite{Cook2009}.
 This CA is an elementary CA that defined on a one dimensional grid, each cell has two possible states (labeled by 0 and 1).
@@
 where, the variable $c$ is an ancilla spin.
-A cellular automata can be viewed as a translational invariant logic circuit, and thus can be encoded into the Ising model.
-The ground states of the Ising model encode the correspondence between the inputs and the outputs of the cellular automata.
+A CA can be viewed as a translational invariant logic circuit, and thus can be encoded into the Ising model.
+The ground states of the Ising model encode the correspondence between the inputs and the outputs of the CA.
 Directly synthesizing the logic circuit for the universal $110$ rule (\Cref{eq:110rule}) requires at least 3 ancilla spins, which is far from optimal.
-By converting the gadget finding problem to a linear programming problem~\cite{}, we propose a provable optimal method to encode any cellular automata rule into the Ising model, which is described in \Cref{sec:gadget-design}.
+By converting the gadget finding problem to a linear programming problem~\cite{}, we propose a provable optimal method to encode any CA rule into the Ising model, which is described in \Cref{sec:gadget-design}.
 The proposed gadget for the $110$ rule is shown in \Cref{Surface-programmable-thermodynamic computer}(b), which only requires 1 ancilla spin.
@@
 \ref{Surface-programmable-thermodynamic computer}(a)].
-The gadget we constructed based on the Rule 110 cellular automata
+The gadget we constructed based on the Rule 110 CA
 naturally possesses Turing completeness. Therefore, this 2-dimensional TC is capable of universal computing.
@@
 
-The computational process of the cellular automata is divided into three steps: determining the state of each input cell, iteratively applying the transition rules to generate the next generation of cells, and identifying a certain generation of cells as the output.
+The computational process of the CA is divided into three steps: determining the state of each input cell, iteratively applying the transition rules to generate the next generation of cells, and identifying a certain generation of cells as the output.
 In fact, the width of the time axis in the Ising TC corresponds to the number of iterations.
@@
 
-Given that each ground state of the TC corresponds to a valid computational process of the cellular automata for a given input, the computational process of the TC is essentially reduced to finding the ground state of the TC with the spin configuration in the input layers fixed.
+Given that each ground state of the TC corresponds to a valid computational process of the CA for a given input, the computational process of the TC is essentially reduced to finding the ground state of the TC with the spin configuration in the input layers fixed.
 
@@
 
-Given that simulating a cellular automata with a deep computational layer on the Ising model requires a large number of spins, making large-scale numerical simulations impractical, we opted to introduce a similar but simpler energy model to observe the behavior on a larger scale.
+Given that simulating a CA with a deep computational layer on the Ising model requires a large number of spins, making large-scale numerical simulations impractical, we opted to introduce a similar but simpler energy model to observe the behavior on a larger scale.
 
@@
 where $n_{i, t} \in \{0, 1\}$ is the state of the cell at row $i$ and column $t$, the boundary is periodic in the space direction, i.e. $n_{0, t} = n_{S, t}$.
-Its ground state with energy $0$ encodes a $110$ cellular automata, where the direction of computation is from the left to right.
+Its ground state with energy $0$ encodes a $110$ CA, where the direction of computation is from the left to right.
 \subsection{Numerical result}
@@
 
-We can encode the Rule 110 cellular automata into a Weighted Maximum
+We can encode the Rule 110 CA into a Weighted Maximum
 Independent Set Problem, with blue vertices assigned a weight of 1 and
@@
 
-The above gadget depicts a two-layer cellular automata. The vertices in
+The above gadget depicts a two-layer CA. The vertices in
 blue, red, green and black have weights of 1, 2, 3 and 4, respectively.

### 2024-09-04 paper/main.tex
update

--- 2024-09-04 paper/main.tex
@@
 
-\title{Surface programmable materials}
+\title{Crystal as a thermodynamic computer}
 
@@
 The former is known as the Brownian machine, which evolves the system toward the direction of the entropy increase, while the latter are energy based, which evolves the system toward the direction of the energy decrease.
-\jinguo{What category are the memristors?}
+\jinguo{What category are the memristors?} \ym{Memristors are energy based, which evolves the system toward the direction of the energy decrease.}
 
@@
 Intrigued by the question of how to thermalize and lower the energy of an Ising machine, we propose a new type of TC that has a crystalline structure.
-The crystalline structure is based on a universal elementary cellular automata, and is translational invariant in all spacial dimensions.
+The crystalline structure is based on a universal elementary cellular automaton, and is translational invariant in all spacial dimensions.
 The translational invariance not only makes the crystal easier to be constructed in nature, but also enables the study of the scaling behavior the thermalization process.
@@
 \section{Overview of the computation model}\label{sec:Overview-of-main-results}
-In this article, We develop a new type of TC shown in \Cref{Surface-programmable-thermodynamic computer}(a), which features a crystalline structure based on a universal elementary cellular automata, makes it easier to be constructed in real life.
+In this article, We develop a new type of TC shown in \Cref{Surface-programmable-thermodynamic computer}(a), which features a crystalline structure based on a universal elementary cellular automaton, makes it easier to be constructed in real life.
 
@@
     % Text Node
-    \draw (492.43,150.41) node [anchor=north west][inner sep=0.75pt]   [align=left] {{\tiny {\fontfamily{ptm}\selectfont p}}};
-    % Text Node
-    \draw (479.75,168.95) node [anchor=north west][inner sep=0.75pt]   [align=left] {{\fontfamily{ptm}\selectfont {\tiny q}}};
-    % Text Node
-    \draw (492.83,188.12) node [anchor=north west][inner sep=0.75pt]   [align=left] {{\tiny {\fontfamily{ptm}\selectfont r}}};
-    % Text Node
-    \draw (525.34,167.95) node [anchor=north west][inner sep=0.75pt]   [align=left] {{\tiny {\fontfamily{ptm}\selectfont q'}}};
-    % Text Node
-    \draw (504.00,168.45) node [anchor=north west][inner sep=0.75pt]   [align=left] {{\tiny {\fontfamily{ptm}\selectfont A}}};
+    \draw (492.00,150.41) node [anchor=north west][inner sep=0.75pt]   [align=left] {{\tiny {$p$}}};
+    % Text Node
+    \draw (479.75,168.95) node [anchor=north west][inner sep=0.75pt]   [align=left] {{\tiny {$q$}}};
+    % Text Node
+    \draw (492.45,188.12) node [anchor=north west][inner sep=0.75pt]   [align=left] {{\tiny {$r$}}};
+    % Text Node
+    \draw (525.00,166.95) node [anchor=north west][inner sep=0.75pt]   [align=left] {{\tiny {$q'$}}};
+    % Text Node
+    \draw (504.00,168.45) node [anchor=north west][inner sep=0.75pt]   [align=left] {{\tiny {$A$}}};
 
@@
     \end{tikzpicture}
-    \caption{Surface programmable thermodynamic computer (TC) and rule110 automata gadget.
+    \caption{Surface programmable thermodynamic computer (TC) and rule110 automaton gadget.
 $\mathtt{(a)}$ Example of a surface programmable TC with a moving heat bath slowly doing ``calculation''.
-White circles are spins and black lines represent interaction between spins, while red rectangles represent cellular automata gadget.
+White circles are spins and black lines represent interaction between spins, while red rectangles represent cellular automaton gadget.
 $\mathtt{(b)}$ Example of a rule110 gadget.
-Here spins $p$, $q$, and $r$ represent the left, middle, and right states in the cellular automata, respectively, while $q^\prime$ represents the result computed by the cellular automata, and $A$ is an auxiliary spin.
+Here spins $p$, $q$, and $r$ represent the left, middle, and right states in the cellular automaton, respectively, while $q’$ represents the result computed by the cellular automaton, and $A$ is an auxiliary spin.
 We define a spin pointing up as representing logical 1 and pointing down as representing logical 0.
@@
 The entire computing process can be described by gradually moving the external heat bath, which creates a temperature gradient and, consequently, a heat zone, from the input layer to the output layer.
-By utilizing thermal fluctuations from the heat bath, the spins in different layers sequentially settle into low-energy states within the state space, effectively completing the iterative computation of the cellular automata.
+By utilizing thermal fluctuations from the heat bath, the spins in different layers sequentially settle into low-energy states within the state space, effectively completing the iterative computation of the cellular automaton.
 
@@
 
-\subsection{Elementary cellular automata}\label{elementary-cellular-automata}
-In cellular automata (CA), `space' is a regular lattice of `cells', each of which contains one of a small allowed set of integers.
-Only cells that are close together interact in one `time-step'-the time evolution is given by a rule that looks at the contents of a few neighbouring cells, and decides what should change.
-At each step, this local rule is applied everywhere simultaneously~\cite{}.
-Depending on different rules, some CAs can be more complex than others.
-The most interesting category is those proved to be universal~\cite{Berlekamp2004}, meaning that they can simulate any computer program.
-The best-known examples in two-dimensional include Conway's~\cite{Games1970} ``Game of Life'', Margolus's reversible cellular automata~\cite{Margolus1984} and its quantum version~\cite{Arrighi2012}.
-The simplest universal CA is a 1-dimensional cellular automata, namely, the rule 110 CA~\cite{Cook2009}.
-This CA is an elementary CA that defined on a one dimensional grid, each cell has two possible states (labeled by 0 and 1).
-The rule of an elementary CA to determine the state of the cell in next generation depends only on the current state of the cell and its two immediate neighbors.
-The number of possible elementary CA rules is the same as the number of 3-input Boolean functions, which is $2^{2^3} = 256$.
-The Boolean function for rule 110 is shown in the following table:
+\subsection{Elementary cellular automaton}\label{elementary-cellular-automaton}
+
+\jinguo{general CA, then the 1D CA.}
+\ym{I haven't made change in this section}
+
+An elementary cellular automaton is a 1-dimensional cellular
+automaton, where there are two possible states (labeled by 0 and 1). The rule to
+determine the state of the cell in next generation depends only on the
+current state of the cell and its two immediate neighbors.
+
+There are $8 = 2^3$ possible configurations for a cell and its two
+immediate neighbors. Different elementary cellular automaton are only
+different from their translation rules. There are only $2^8 = 256$
+different rules, so do the automatons.
+
+If we put each possible current configurations in order: 111, 110,
+\ldots, 001, 000, and put the resulting state under them. We then get an
+integer in its binary representations. Then this integer is taken to be
+the rule number of the automaton. For example, rule 110.
+
+Given that $110_d = 01101110_2$, so rule 110 is defined by the
+translation rule:
 
@@
 
-The name of the rule comes from the binary representation of the rule number, which is 110 in decimal.
-Let us denote the states of the three cells as $p$, $q$, and $r$, from left to right, respectively. The rule 110 can be expressed as the following Boolean function:
+In boolean form, it can be expressed as:
 \begin{equation}\label{eq:110rule}
@@
 \end{equation}
-where $q^\prime$ is the state of the center cell in the next generation.
+
+Rule 110 has been shown to be Turing Complete~\cite{Cook2009}, and thus capable of universal
+computation.
 
@@
 where, the variable $c$ is an ancilla spin.
-A cellular automata can be viewed as a translational invariant logic circuit, and thus can be encoded into the Ising model.
-The ground states of the Ising model encode the correspondence between the inputs and the outputs of the cellular automata.
+A cellular automaton can be viewed as a translational invariant logic circuit, and thus can be encoded into the Ising model.
+The ground states of the Ising model encode the correspondence between the inputs and the outputs of the cellular automaton.
 Directly synthesizing the logic circuit for the universal $110$ rule (\Cref{eq:110rule}) requires at least 3 ancilla spins, which is far from optimal.
-By converting the gadget finding problem to a linear programming problem~\cite{}, we propose a provable optimal method to encode any cellular automata rule into the Ising model, which is described in \Cref{sec:gadget-design}.
+By converting the gadget finding problem to a linear programming problem~\cite{}, we propose a provable optimal method to encode any cellular automaton rule into the Ising model, which is described in \Cref{sec:gadget-design}.
 The proposed gadget for the $110$ rule is shown in \Cref{Surface-programmable-thermodynamic computer}(b), which only requires 1 ancilla spin.
@@
 \end{equation}
-Since a copy gate\jinguo{do we really use copy gates?} can be simply described as two spins with an interaction $J_{u, v}=1$, and by applying the method of connecting logic gates~\cite{Aadit2022}, we can concatenate the rule 110 gadget with some copy gates, ultimately forming the TC shown in [Fig.
+Since a copy gate\jinguo{do we really use copy gates?} \ym{No need in practice, but indeed used in Fig.1a} can be simply described as two spins with an interaction $J_{u, v}=1$, and by applying the method of connecting logic gates~\cite{Aadit2022}, we can concatenate the rule 110 gadget with some copy gates, ultimately forming the TC shown in [Fig.
 \ref{Surface-programmable-thermodynamic computer}(a)].
-The gadget we constructed based on the Rule 110 cellular automata
+The gadget we constructed based on the Rule 110 cellular automaton
 naturally possesses Turing completeness. Therefore, this 2-dimensional TC is capable of universal computing.
 
+\subsection{Simulated Annealing}
+
+It is known that when the system and heat bath are at thermal equilibrium, 
+the probability of a spin configuration $|\mathbf{s}\rangle$ is given by the Boltzmann distribution:
+
+\begin{equation}
+    |\mathbf{s}\rangle = \frac{1}{Z}\exp\left(- \frac{E_{|\mathbf{s}\rangle}}{k_bT}\right)
+\end{equation}
+
+where $Z = \sum_{|\mathbf{s}\rangle} \exp\left(-\frac{E_{|\mathbf{s}\rangle}}{k_bT}\right)$ is the partition function, 
+$E_{|\mathbf{s}\rangle}$ is the energy of the each of $2^n$ spin configuration, labeled by $|\mathbf{s}\rangle = |s_1, s_2, \cdots, s_n\rangle$, $k_b$ is the Boltzmann constant, and $T$ is the temperature of the heat bath.
+In the following, we set $k_b = 1$.
+
+We employ the Metropolis-Hastings algorithm~\cite{metropolis1953equation} to characterize the thermodynamic process of the TC system as modulated by the heat bath.
+This algorithm perform a random walk in the state space of the TC, each step we try to flip a spin,
+and the probability of accepting a move from state $|\mathbf{s}\rangle$ to $|\mathbf{s}^\prime\rangle$ is given by:
+
+\begin{equation}
+    P_{\text{accept}} = \frac{1}{1+\exp\left(\frac{E_{|\mathbf{s}^\prime\rangle} - E_{|\mathbf{s}\rangle}}{T}\right)}
+\end{equation}
+
+This accepting probability follows from the glauber dynamics~\cite{glauber1963time}.
+It can be shown that this process is markovian and ergodic, and the system will eventually reach the thermal equilibrium.
+To determine the speed of the convergence, we should notice the spectral gap of the transition matrix of the Markov chain, which is defined as
+
+\begin{equation}
+    \Delta = 1 - \frac{\lambda_2}{\lambda_1}
+\end{equation}
+
+where $\lambda_1$ and $\lambda_2$ are the largest and second largest eigenvalues of the transition matrix, respectively.
+In order to sample from the distribution $\epsilon$ close to the equilibrilium distribution, the number of steps required is $O(\log_{1-\Delta} \epsilon)$.
+
 \subsection{Cooling computation with a moving heat bath}\label{cooling-computation-with-moving-heat-bath}
 
-The computational process of the cellular automata is divided into three steps: determining the state of each input cell, iteratively applying the transition rules to generate the next generation of cells, and identifying a certain generation of cells as the output.
+The computational process of the cellular automaton is divided into three steps: determining the state of each input cell, iteratively applying the transition rules to generate the next generation of cells, and identifying a certain generation of cells as the output.
 In fact, the width of the time axis in the Ising TC corresponds to the number of iterations.
@@
 
-Given that each ground state of the TC corresponds to a valid computational process of the cellular automata for a given input, the computational process of the TC is essentially reduced to finding the ground state of the TC with the spin configuration in the input layers fixed.
+Given that each ground state of the TC corresponds to a valid computational process of the cellular automaton for a given input, the computational process of the TC is essentially reduced to finding the ground state of the TC with the spin configuration in the input layers fixed.
 
@@
 
-\ym{This part should be rewrote in future..My words are so poor.}
-
 Let us initially treat the heat bath as ideal, assuming that the temperature within the interacting region of the system is uniform and that the temperature outside this region is zero.
@@
 In practice, temperature changes cannot occur instantaneously, and the temperature distribution within the heating zone may not be uniform.
-Thus, it is necessary to account for the effective width of the Heat Zone when the the heat bath are not ideal.
-
-Suppose the middle of the heat bath is at $middle(t)$, and the temperature at the region with a Time coordinate $x$ can be represent as $Temp(x) \propto \Lambda^{-|x - middle(t)|}$. Then
-
-\begin{equation}
-    e^{-\Delta E \Lambda^{cW}} \sim \epsilon \sim \frac{W}{T}
-\end{equation}
-
-Where $c$ is the empirical constant for effective width and can be determined during the experiment. The total annealing time should be
+Thus, we come up with a more realistic model for the block annealing process.
+
+Now suppose the heat bath only connects to a small rectangle region of the system,
+covers the region encompassing all time coordinates between $[middle(t)-\frac{\Delta_L}{2}, middle(t)+\frac{\Delta_L}{2}]$, where $\Delta_L$ is a small constant.
+The heat radiation is conducted to other regions, thereby inducing a temperature gradient,
+which can be modeled as $T(x) \propto \Lambda^{-|x - middle(t)|}$, where $T(x)$ is the temperature at the region with a time coordinate $x$, and $\Lambda$ is a constant.
+
+The block annealing process then can be reconstruct as slowly moving
+the middle of the heat bath from one end to the other. Defining $\Delta E_{max}$ to be the
+largest possible energy change when a spin is fliped.
+The effective heat zone should then be $[y-W, y]$, where position $y$ satisfying 
+$\exp(\frac{\Delta E_{max}}{T(y)}) = 0.1$ and $y<middle(t)$. Since the layers
+in fronts of the effective heat zone can only be fliped with a $\epsilon$ probability if the local energy would increase. 
+The effective width $W$ then should scale as $\exp(-\Delta E_{max} \Lambda^{cW}) \sim \epsilon \sim \frac{W}{T}$, where $c$ is the empirical constant for effective width and can be determined during the experiment.
+
+The total annealing time can be calculated as
 
@@
 Numerical result shows that computing complexity is linear to $n$. Thus a total time
-for the computation should scale as $nm\log^2(m)e^{(1-\lambda)^{-1}}$
-
-\subsubsection{Testing model through equilibrilium SA}\label{temperature-gradient-and-energy-gradient}
-
-We used simulated annealing to mimic the heating-annealing process.
-However, classical simulated annealing can only handle the situation
-where the temperature is space-invariant. Thus, a scheme change is needed.
-
-One can simply
-make the following modification to the transition probability in the
-markov process and return to the situation, called energy-gradient scheme, where the temperature is space-invariant.
-
-\begin{equation}
-e^{-\frac{\Delta E_k}{T\lambda^{ct+k}}} = e^{-\frac{\Delta E_k(\frac{1}{\lambda})^k}{T\lambda^{ct}}} = e^{-\frac{\Delta E_k \Lambda^k}{T(t)}}
-\end{equation}
-
-Where we denote $\Lambda = \frac{1}{\lambda}$ and the time complexity in $\Lambda$ form is apparently
-$T_{total} \sim \frac{m}{W}\log^2(\frac{m}{W})e^{(\Lambda-1)^{-1}}$
-
-\subsection{Algorithm beyond temperature
-gradient}\label{algorithm-beyond-temperature-gradient}
-
-Applying a huge energy gradient or temperature gradient to this material
-seems not a good idea when the system become larger.
-
-Inspired by the way clothes are ironed, we conceived an idea called wave-packet scheme, that slowly
-scanning a wave-shaped temperature curve from one end to the other. This
-method is widely used in studying the heating-recrystallization
-properties of real materials~\cite{Zhang2014}.
-
-\begin{figure}[h]
-\centering
-\includegraphics[width=\columnwidth]{../notes/images/zhang2014.png}
-\caption{Method to scan the wave packet}
-\end{figure}
-
-There are various specific choices for the wave packet, such as
-power-law, exponential, and others. In this context, we primarily focus
-on a exponential wave packet, which can be directly linked to the
-concept of energy gradient.
-
-A expoential wave packet with central position $middle(t)$, amplitude
-$A$ and base $\Lambda$, can be express as following.
-
-\[
-T(k,t) = A\Lambda^{|k-middle(t)|}
-\]
-
-So slowly moving the wave packet means slowly changing $middle(t)$
-
-Let's review the concept \textbf{active zone} defined earlier. When the
-temperature of the system is defined as
-$T_{tg}(k, t) = T\lambda^{ct-k}$, atoms in the active zone are those
-whose layer $k$ belongs to $k<ct - \frac{W}{2}$, where $W$ are
-given by
-$e^{-\frac{\Delta E_{max}}{\lambda^{\frac{W}{2}}}}\leq \epsilon$. For
-those $k<ct - \frac{W}{2}$, the probability that SA would flip an
-atom's state is no more than
-$e^{-\frac{\Delta E_{max}}{T\lambda^{ct}\lambda^{-ct + \frac{W}{2}}}}=e^{-\frac{\Delta E_{max}}{T\lambda^{\frac{W}{2}}}}\leq \epsilon^{\frac{1}{T}}$,
-which means these previous layer would stay ``frozen''. For those layer
-much deeper than $k = ct$, SA would just randomly flip them. These
-layer won't affect layers in active zone.
-
-Now turn our sight into the wave packet model, we can construct a
-similar concept \textbf{heat zone}. Layers in the heat zone are those
-$A\lambda^{|k-middle(t)|}\ge \epsilon\rightarrow middle(t) + \frac{\log(\epsilon)}{\log(\Lambda)}< k < middle(t) - \frac{\log(\epsilon)}{\log(\Lambda)}$.
-
-The layers that shallower than
-$middle(t) + \frac{\log(\epsilon)}{\log(\Lambda)}$ correspond to
-layers shallower than $ct-\frac{W}{2}$ in temperature gradient model,
-since they are both stay ``frozen''; layers between
-$middle(t) +\frac{\log(\epsilon)}{\log(\Lambda)}$ and $middle(t)$
-are effectively cooled down, which correspond to the \textbf{active
-zone}; layers deeper than $middle(t)$ are either randomly fliped or
-stay ``frozen'', but we don't care their state.
-
-Therefore, the wave packet model are just the same as the temperature
-gradient model, and is more likely to be realized physically.
-
-\subsubsection{Some details about non-equilibrium simulated
+for the computation should scale as $nm\log^{1 + \frac{1}{c\ln(\Lambda)}}(m)$
+
+\subsubsection{Testing model with non-equilibrium simulated
 annealing}\label{some-details-about-non-equilibrium-simulated-annealing}
@@
 The classical simulated annealing can only deal with the situation that
-the temperature is space-invariant. Although there are many ways to
+the temperature is space-invariant. However, we need to borden this concept
+due to the temperature gradient. Although there are many ways to
 simulated a real-world system with temperature gradient, such as
@@
 
-When we flip one atom's state, there would be some energy difference
+When we flip one spin, there would be some energy difference
 $\Delta E_{i}$ in field $i$ with temperature $T_i$. The
@@
 heat-equilibrium, the probability reverts to the classical HeatBath
-acceptance probability.
+acceptance probability. We also provided a more general proof by constructing another equivalent model in Appendix \ref{proof-of_non-equilibrium-SA}.
+
 \section{Numerical simulation}\label{sec:numerical-result}
@@
 
-Given that simulating a cellular automata with a deep computational layer on the Ising model requires a large number of spins, making large-scale numerical simulations impractical, we opted to introduce a similar but simpler energy model to observe the behavior on a larger scale.
+Given that simulating a cellular automaton with a deep computational layer on the Ising model requires a large number of spins, making large-scale numerical simulations impractical, we opted to introduce a similar but simpler energy model to observe the behavior on a larger scale.
 
@@
 where $n_{i, t} \in \{0, 1\}$ is the state of the cell at row $i$ and column $t$, the boundary is periodic in the space direction, i.e. $n_{0, t} = n_{S, t}$.
-Its ground state with energy $0$ encodes a $110$ cellular automata, where the direction of computation is from the left to right.
+Its ground state with energy $0$ encodes a $110$ cellular automaton, where the direction of computation is from the left to right.
 \subsection{Numerical result}
@@
 
+\section{Proof of the applicability of non-equilibrium SA}\label{proof-of_non-equilibrium-SA}
+
+Assume there is another model where the temperature at the region with 
+time coordinate $x$ at step $t$ is $T(x, t) = T_0\Lambda^{x - \eta t}$, where 
+$\eta$ is cooling constant and $T_0$ satisfies $\exp(\frac{\Delta E_{max}}{T_0})\approx 1$, 
+which means all the system stays in a relative high temperature initially. 
+We called this model as temperature gradient model.
+
+The cooling process starts at $t=0$ and ends at $t=t_{end}$, where $t_{end}$ satisfies
+$\exp(\frac{\Delta E_{max}}{T_0\Lambda^{T - \eta t_{end}}}) \gg 1$, representing there wouldn't be any heat
+fluctuations in the system. By noticing that we can define the effective heat zone
+similarly to the moving heat bath model and then evaluating the time complexity, one can show that these two model are
+equivalent.
+
+The temperature gradient model can then be easily transform to
+the energy gradient model in which equilibrilium SA can be applied by rescale local interacting and onsite energy.
+The markov process can be treated with uniform temperature while rescale the energy associated with spin with Time-coordinate $x$
+to be $E_{energy-gradient}(x) = E_{temp-gradient}(x)\Lambda^{-x}$. The acceptance probability is
+invariant under this transformation.
+
+\begin{equation}
+    \exp\left({\frac{\Delta E_x}{T\Lambda^{x-\eta t}}}\right) = \exp\left({\frac{\Delta E_x\Lambda^{-x}}{T\Lambda^{-\eta t}}}\right) = \exp\left({\frac{\Delta E_x \Lambda^{-x}}{T(t)}}\right)
+\end{equation}
+
 \section{The implmentation in Rydberg atoms array}\label{physical-model-rydberg-atoms-array}
@@
 
-We can encode the Rule 110 cellular automata into a Weighted Maximum
+We can encode the Rule 110 cellular automaton into a Weighted Maximum
 Independent Set Problem, with blue vertices assigned a weight of 1 and
@@
 \textbf{8} represent the states of the \textbf{middle}, \textbf{left},
-and \textbf{right} cells of the automata's \textbf{input},
+and \textbf{right} cells of the automaton's \textbf{input},
 respectively. If the input value of a cell is 1, then the corresponding
 vertex must be in the MWIS solution; otherwise, it is not. Vertex
-\textbf{12} corresponds to the automata's \textbf{output}. If the
-automata output is 1, then vertex 12 is in the MWIS solution;
+\textbf{12} corresponds to the automaton's \textbf{output}. If the
+automaton output is 1, then vertex 12 is in the MWIS solution;
 otherwise, it is not.
 
-In the automata diagram, the above gadget is equivalent to:
+In the automaton diagram, the above gadget is equivalent to:
 
@@
 weighted size of each MWIS solution is 7), each corresponding to one of
-the \textbf{8} possible outputs of the automata. We list them as
+the \textbf{8} possible outputs of the automaton. We list them as
 follows.
@@
 
-The above gadget depicts a two-layer cellular automata. The vertices in
+The above gadget depicts a two-layer cellular automaton. The vertices in
 blue, red, green and black have weights of 1, 2, 3 and 4, respectively.
-In the automata diagram, the above gadget is equivalent to:
+In the automaton diagram, the above gadget is equivalent to:
 
@@
 \centering
-\includegraphics[width=\columnwidth]{../notes/images/rule110_2-2_automata.png}
+\includegraphics[width=\columnwidth]{../notes/images/rule110_2-2_automaton.png}
 \caption{Alt text}

### 2024-09-04 paper/main.tex

@@
 \begin{abstract}
+    Thermodynamic computers are believed to be more energy efficient than conventional computers, however, a practical implementation of a thermodynamic computer is still challenging.
+In this paper, we propose a thermodynamics driven computer that enables use to perform computation by editing its surface.
+    The crystalline structure is based on a universal elementary CA, and is translational invariant in all spacial dimensions.
+The translational invariance not only makes the crystal easier to be constructed in nature, but also enables the study of the scaling behavior the thermalization process.
 \end{abstract}
@@
 Intrigued by the question of how to thermalize and lower the energy of an Ising machine, we propose a new type of TC that has a crystalline structure.
-The crystalline structure is based on a universal elementary cellular automaton, and is translational invariant in all spacial dimensions.
+The crystalline structure is based on a universal elementary CA, and is translational invariant in all spacial dimensions.
 The translational invariance not only makes the crystal easier to be constructed in nature, but also enables the study of the scaling behavior the thermalization process.
@@
 \section{Overview of the computation model}\label{sec:Overview-of-main-results}
-In this article, We develop a new type of TC shown in \Cref{Surface-programmable-thermodynamic computer}(a), which features a crystalline structure based on a universal elementary cellular automaton, makes it easier to be constructed in real life.
+In this article, We develop a new type of TC shown in \Cref{Surface-programmable-thermodynamic computer}(a), which features a crystalline structure based on a universal elementary CA, makes it easier to be constructed in real life.
 
@@
     \end{tikzpicture}
-    \caption{Surface programmable thermodynamic computer (TC) and rule110 automaton gadget.
+    \caption{Surface programmable thermodynamic computer (TC) and rule110 automata gadget.
 $\mathtt{(a)}$ Example of a surface programmable TC with a moving heat bath slowly doing ``calculation''.
-White circles are spins and black lines represent interaction between spins, while red rectangles represent cellular automaton gadget.
+White circles are spins and black lines represent interaction between spins, while red rectangles represent CA gadget.
 $\mathtt{(b)}$ Example of a rule110 gadget.
-Here spins $p$, $q$, and $r$ represent the left, middle, and right states in the cellular automaton, respectively, while $q’$ represents the result computed by the cellular automaton, and $A$ is an auxiliary spin.
+Here spins $p$, $q$, and $r$ represent the left, middle, and right states in the cellular automata, respectively, while $q^\prime$ represents the result computed by the cellular automata, and $A$ is an auxiliary spin.
 We define a spin pointing up as representing logical 1 and pointing down as representing logical 0.
@@
 The entire computing process can be described by gradually moving the external heat bath, which creates a temperature gradient and, consequently, a heat zone, from the input layer to the output layer.
-By utilizing thermal fluctuations from the heat bath, the spins in different layers sequentially settle into low-energy states within the state space, effectively completing the iterative computation of the cellular automaton.
+By utilizing thermal fluctuations from the heat bath, the spins in different layers sequentially settle into low-energy states within the state space, effectively completing the iterative computation of the CA.
 
@@
 
-\subsection{Elementary cellular automaton}\label{elementary-cellular-automaton}
-
-\jinguo{general CA, then the 1D CA.}
-\ym{I haven't made change in this section}
-
-An elementary cellular automaton is a 1-dimensional cellular
-automaton, where there are two possible states (labeled by 0 and 1). The rule to
-determine the state of the cell in next generation depends only on the
-current state of the cell and its two immediate neighbors.
-
-There are $8 = 2^3$ possible configurations for a cell and its two
-immediate neighbors. Different elementary cellular automaton are only
-different from their translation rules. There are only $2^8 = 256$
-different rules, so do the automatons.
-
-If we put each possible current configurations in order: 111, 110,
-\ldots, 001, 000, and put the resulting state under them. We then get an
-integer in its binary representations. Then this integer is taken to be
-the rule number of the automaton. For example, rule 110.
-
-Given that $110_d = 01101110_2$, so rule 110 is defined by the
-translation rule:
+\subsection{Elementary cellular automata}\label{elementary-cellular-automata}
+In cellular automata (CA), `space' is a regular lattice of `cells', each of which contains one of a small allowed set of integers.
+Only cells that are close together interact in one `time-step'-the time evolution is given by a rule that looks at the contents of a few neighbouring cells, and decides what should change.
+At each step, this local rule is applied everywhere simultaneously~\cite{}.
+Depending on different rules, some CAs can be more complex than others.
+The most interesting category is those proved to be universal~\cite{Berlekamp2004}, meaning that they can simulate any computer program.
+The best-known examples in two-dimensional include Conway's~\cite{Games1970} ``Game of Life'', Margolus's reversible CA~\cite{Margolus1984} and its quantum version~\cite{Arrighi2012}.
+The simplest universal CA is a 1-dimensional CA, namely, the rule 110 CA~\cite{Cook2009}.
+This CA is an elementary CA that defined on a one dimensional grid, each cell has two possible states (labeled by 0 and 1).
+The rule of an elementary CA to determine the state of the cell in next generation depends only on the current state of the cell and its two immediate neighbors.
+The number of possible elementary CA rules is the same as the number of 3-input Boolean functions, which is $2^{2^3} = 256$.
+The Boolean function for rule 110 is shown in the following table:
 
@@
 
-In boolean form, it can be expressed as:
+The name of the rule comes from the binary representation of the rule number, which is 110 in decimal.
+Let us denote the states of the three cells as $p$, $q$, and $r$, from left to right, respectively. The rule 110 can be expressed as the following Boolean function:
 \begin{equation}\label{eq:110rule}
@@
 \end{equation}
-
-Rule 110 has been shown to be Turing Complete~\cite{Cook2009}, and thus capable of universal
-computation.
+where $q^\prime$ is the state of the center cell in the next generation.
 
@@
 where, the variable $c$ is an ancilla spin.
-A cellular automaton can be viewed as a translational invariant logic circuit, and thus can be encoded into the Ising model.
-The ground states of the Ising model encode the correspondence between the inputs and the outputs of the cellular automaton.
+A CA can be viewed as a translational invariant logic circuit, and thus can be encoded into the Ising model.
+The ground states of the Ising model encode the correspondence between the inputs and the outputs of the CA.
 Directly synthesizing the logic circuit for the universal $110$ rule (\Cref{eq:110rule}) requires at least 3 ancilla spins, which is far from optimal.
-By converting the gadget finding problem to a linear programming problem~\cite{}, we propose a provable optimal method to encode any cellular automaton rule into the Ising model, which is described in \Cref{sec:gadget-design}.
+By converting the gadget finding problem to a linear programming problem~\cite{}, we propose a provable optimal method to encode any CA rule into the Ising model, which is described in \Cref{sec:gadget-design}.
 The proposed gadget for the $110$ rule is shown in \Cref{Surface-programmable-thermodynamic computer}(b), which only requires 1 ancilla spin.
@@
 \ref{Surface-programmable-thermodynamic computer}(a)].
-The gadget we constructed based on the Rule 110 cellular automaton
+The gadget we constructed based on the Rule 110 CA
 naturally possesses Turing completeness. Therefore, this 2-dimensional TC is capable of universal computing.
@@
 
-The computational process of the cellular automaton is divided into three steps: determining the state of each input cell, iteratively applying the transition rules to generate the next generation of cells, and identifying a certain generation of cells as the output.
+The computational process of the CA is divided into three steps: determining the state of each input cell, iteratively applying the transition rules to generate the next generation of cells, and identifying a certain generation of cells as the output.
 In fact, the width of the time axis in the Ising TC corresponds to the number of iterations.
@@
 
-Given that each ground state of the TC corresponds to a valid computational process of the cellular automaton for a given input, the computational process of the TC is essentially reduced to finding the ground state of the TC with the spin configuration in the input layers fixed.
+Given that each ground state of the TC corresponds to a valid computational process of the CA for a given input, the computational process of the TC is essentially reduced to finding the ground state of the TC with the spin configuration in the input layers fixed.
 
@@
 
-Given that simulating a cellular automaton with a deep computational layer on the Ising model requires a large number of spins, making large-scale numerical simulations impractical, we opted to introduce a similar but simpler energy model to observe the behavior on a larger scale.
+Given that simulating a CA with a deep computational layer on the Ising model requires a large number of spins, making large-scale numerical simulations impractical, we opted to introduce a similar but simpler energy model to observe the behavior on a larger scale.
 
@@
 where $n_{i, t} \in \{0, 1\}$ is the state of the cell at row $i$ and column $t$, the boundary is periodic in the space direction, i.e. $n_{0, t} = n_{S, t}$.
-Its ground state with energy $0$ encodes a $110$ cellular automaton, where the direction of computation is from the left to right.
+Its ground state with energy $0$ encodes a $110$ CA, where the direction of computation is from the left to right.
 \subsection{Numerical result}
@@
 
-We can encode the Rule 110 cellular automaton into a Weighted Maximum
+We can encode the Rule 110 CA into a Weighted Maximum
 Independent Set Problem, with blue vertices assigned a weight of 1 and
@@
 \textbf{8} represent the states of the \textbf{middle}, \textbf{left},
-and \textbf{right} cells of the automaton's \textbf{input},
+and \textbf{right} cells of the automata's \textbf{input},
 respectively. If the input value of a cell is 1, then the corresponding
 vertex must be in the MWIS solution; otherwise, it is not. Vertex
-\textbf{12} corresponds to the automaton's \textbf{output}. If the
-automaton output is 1, then vertex 12 is in the MWIS solution;
+\textbf{12} corresponds to the automata's \textbf{output}. If the
+automata output is 1, then vertex 12 is in the MWIS solution;
 otherwise, it is not.
 
-In the automaton diagram, the above gadget is equivalent to:
+In the automata diagram, the above gadget is equivalent to:
 
@@
 weighted size of each MWIS solution is 7), each corresponding to one of
-the \textbf{8} possible outputs of the automaton. We list them as
+the \textbf{8} possible outputs of the automata. We list them as
 follows.
@@
 
-The above gadget depicts a two-layer cellular automaton. The vertices in
+The above gadget depicts a two-layer CA. The vertices in
 blue, red, green and black have weights of 1, 2, 3 and 4, respectively.
-In the automaton diagram, the above gadget is equivalent to:
+In the automata diagram, the above gadget is equivalent to:
 
@@
 \centering
-\includegraphics[width=\columnwidth]{../notes/images/rule110_2-2_automaton.png}
+\includegraphics[width=\columnwidth]{../notes/images/rule110_2-2_automata.png}
 \caption{Alt text}

### 2024-09-04 paper/main.tex
update

@@
 
+\ym{I will move this figure to AppendixB to show the equivalent 
+between heat bath and energy gradient. Another plot would be put here that
+show the TL v.s. $m\ln^{1+\frac{1}{c\ln(\Lambda)}}m$}
 We conducted numerical experiments both for energy-gradient and wave-packet scheme, under the condition

### 2024-09-05 paper/main.tex
update

@@
 The translational invariance not only makes the crystal easier to be constructed in nature, but also enables the study of the scaling behavior the thermalization process.
+    Efficiency of the computation of the proposed thermodynamic computer is demonstrated by numerical results.
 \end{abstract}
@@
 
-\jinguo{Please cover the following topics:
-\begin{enumerate}
-    \item The method to thermalize, inspired from crystalization and heat zone.
-\end{enumerate}
-}
+\jinguo{}
 \ym{Need to add a brief summary about the state-of-the-art TCs. Following is some basic summaries of references
 \begin{enumerate}
-    \item The material was orderly grown by slowly moving the temperature gradient in-plane~\cite{Zhang2014}. Tested thermal gradient force for grain boundary migration~\cite{Bai2015}.
     \item Discussed the architecture of future thermodynamic computer and brought up an idea about the understanding of using TC to solve problems~\cite{hylton2021vision}.
@@
 \section{Overview of the computation model}\label{sec:Overview-of-main-results}
-In this article, We develop a new type of TC shown in \Cref{Surface-programmable-thermodynamic computer}(a), which features a crystalline structure based on a universal elementary CA, makes it easier to be constructed in real life.
+The TC we are proposing is shown in \Cref{Surface-programmable-thermodynamic computer}.
+It features a crystalline structure that encodes the time evolution of a universal CA that capable of performing universal computation.
+To encode a $D$-dimensional CA, we need a $D+1$-dimensional crystal. The extra dimension is used to encode the time-axis of the CA.
+For simplicity, we will focus on the 1D 110 rule elementary CA in the rest of this paper.
+The physical implementation of the TC is based on the Ising model, where we use the spin up and down to encode the state $1$ and $0$ of the cellular automata, respectively.
+The energy of the Ising model is designed to be minimized when the spins are in the state that satisfies the rule 110 cellular automata, which can be achieved by constructing the rule 110 gadget shown in the inset of \Cref{Surface-programmable-thermodynamic computer}.
 
@@
     % Text Node
-    \draw (220.87,45.67) node [anchor=north west][inner sep=3pt]   [align=left] {\large {$\displaystyle \mathtt{(a)}$}};
-    % Text Node
-    \draw (490.67,121.47) node [anchor=north west][inner sep=3pt]   [align=left] {\large {$\displaystyle \mathtt{(b)}$}};
+    %\draw (220.87,45.67) node [anchor=north west][inner sep=3pt]   [align=left] {\large {$\displaystyle \mathtt{(a)}$}};
+    % Text Node
+    %\draw (490.67,121.47) node [anchor=north west][inner sep=3pt]   [align=left] {\large {$\displaystyle \mathtt{(b)}$}};
     % Text Node
@@
     \end{tikzpicture}
-    \caption{Surface programmable thermodynamic computer (TC) and rule110 automata gadget.
-$\mathtt{(a)}$ Example of a surface programmable TC with a moving heat bath slowly doing ``calculation''.
-White circles are spins and black lines represent interaction between spins, while red rectangles represent CA gadget.
-$\mathtt{(b)}$ Example of a rule110 gadget.
-Here spins $p$, $q$, and $r$ represent the left, middle, and right states in the cellular automata, respectively, while $q^\prime$ represents the result computed by the cellular automata, and $A$ is an auxiliary spin.
-We define a spin pointing up as representing logical 1 and pointing down as representing logical 0.
-\jinguo{why capital A?
-q' not clear.}}
+    \caption{A surface programmable thermodynamic computer (TC) that implements the rule 110 elementary cellular automata. The vertical direction is the space axis,
+    while the horizontal direction is the time axis.
+    The computation is done by moving the heat zone (orange colored area) from the input surface (left) to the output surface (right) slowly with a constant speed $v$.
+    The TC has a translational invariant structure, and each unit cell (inset) is a $110$ rule cellular automata gadget that consists of 5 mutually correlated spins (white circles).
+    \jinguo{please add symbols for space, time and width}}
     \label{Surface-programmable-thermodynamic computer}
@@
 
-The physical implementation of the TC is based on spins, with computational information encoded in the orientation of the spins, represented by white circles, while the red box represents a logic circuit, composed of several spins.
-The horizontal axis represents the number of computational layers, with spins belonging to the same computational layer sharing the same horizontal coordinate, and vertical axis represents the number of spins in each layer.
-
-The input layer consists of the leftmost spin, while the output layer consists of the rightmost spin.
-The entire computing process can be described by gradually moving the external heat bath, which creates a temperature gradient and, consequently, a heat zone, from the input layer to the output layer.
+The inputs, including the data and the program are encoded in the initial configuration of the spins on the left surface. These spins are fixed during the computation.
+The entire computing process can be described by gradually moving an external heat bath with finite width from the input end to the output end.
+It creates a temperature gradient and, consequently, a heat zone of width $W$.
 By utilizing thermal fluctuations from the heat bath, the spins in different layers sequentially settle into low-energy states within the state space, effectively completing the iterative computation of the CA.
 
-Users can design the computing algorithm and obtain the desired output by setting the input configuration and then making slight movements to the external heat bath, requiring only approximately linear time (up to a $\log^2$ factor) with respect to the number of layers.
+%Users can design the computing algorithm and obtain the desired output by setting the input configuration and then making slight movements to the external heat bath, requiring only approximately linear time (up to a $\log^2$ factor) with respect to the number of layers.
 
@@
 
-\subsection{Mapping CA to Ising model}
+\subsection{CA embedded in an Ising model}
 
@@
 \end{equation}
-Since a copy gate\jinguo{do we really use copy gates?} \ym{No need in practice, but indeed used in Fig.1a} can be simply described as two spins with an interaction $J_{u, v}=1$, and by applying the method of connecting logic gates~\cite{Aadit2022}, we can concatenate the rule 110 gadget with some copy gates, ultimately forming the TC shown in [Fig.
-\ref{Surface-programmable-thermodynamic computer}(a)].
-The gadget we constructed based on the Rule 110 CA
-naturally possesses Turing completeness. Therefore, this 2-dimensional TC is capable of universal computing.
+%Since a copy gate\jinguo{do we really use copy gates?} \ym{No need in practice, but indeed used in Fig.1a} can be simply described as two spins with an interaction $J_{u, v}=1$, and by applying the method of connecting logic gates~\cite{Aadit2022}, we can concatenate the rule 110 gadget with some copy gates, ultimately forming
+By concatenating the rule 110 gadgets, we can construct a 2-dimensional TC that implements the rule 110 CA, as shown in \Cref{Surface-programmable-thermodynamic computer}.
+The gadget we constructed based on the Rule 110 CA naturally possesses Turing completeness. Therefore, this 2-dimensional TC is capable of universal computing.
 
@@
 
+\ym{
+    The material was orderly grown by slowly moving the temperature gradient in-plane~\cite{Zhang2014}. Tested thermal gradient force for grain boundary migration~\cite{Bai2015}.
+}
 We test the hypothesis: Cooling is easy if the process is from the
@@
     \includegraphics[width=\columnwidth,keepaspectratio]{../notes/images/numercial result.pdf}
-    \caption{Time v.s. Depth of the material}
+    \caption{Time v.s. Depth of the material\jinguo{show a comparison from right to left}\jinguo{I have already used D as the dimension}}
 \end{figure}
@@
 
+We conducted numerical experiments to verify this equivalence under the condition
+that $\Lambda = 1.3$ and $n=15$. The result is shown in [Fig. \ref{EGvsMHB}].
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=\columnwidth,keepaspectratio]{../notes/images/EGvsMHB.png}
+    \caption{Running time v.s Depth of the material}
+    \label{EGvsMHB}
+\end{figure}
+
 \section{The implmentation in Rydberg atoms array}\label{physical-model-rydberg-atoms-array}

### 2024-09-05 paper/main.tex
update

@@
 Directly synthesizing the logic circuit for the universal $110$ rule (\Cref{eq:110rule}) requires at least 3 ancilla spins, which is far from optimal.
-By converting the gadget finding problem to a linear programming problem~\cite{}, we propose a provable optimal method to encode any CA rule into the Ising model, which is described in \Cref{sec:gadget-design}.
+By converting the gadget finding problem to a linear programming problem~\cite{Kolman1995}, we propose a provable optimal method to encode any CA rule into the Ising model, which is described in \Cref{sec:gadget-design}.
 The proposed gadget for the $110$ rule is shown in \Cref{Surface-programmable-thermodynamic computer}(b), which only requires 1 ancilla spin.
@@
 
+With the proposed Ising model, we are interested in how efficiently we can drive the system to the ground state, which encodes the output of the CA.
+Since the natural cooling process is highly nontrivial to model, we consider a theoretical model for cooling, which is simulated annealing (SA)~\cite{Kirkpatrick1983}.
+\jinguo{random fluctuations may be linear in time considering the parallelism of the system.}
 It is known that when the system and heat bath are at thermal equilibrium, 
@@
 
+\jinguo{please do not use the ket bra notation}
 \begin{equation}

### 2024-09-05 paper/main.tex
update numerical result parts

--- 2024-09-04 paper/main.tex
@@
 \begin{equation}
+    \label{eq:total-annealing-time}
     t_{total} = \frac{T}{W}(\ln(\frac{T}{W}))^{1+ \frac{1}{c\ln(\Lambda)}}
@@
 \begin{equation}
+    \label{eq:non-equilibrium-SA}
 P = \frac{1}{1 + e^{\sum_i \frac{\Delta E_i}{T_i}}}
@@
 
-Let us define a model Hamiltonian on a 2D lattice of size $S \times T$ as
+Denote $S$ to be the length of the material along the ``Space'' axis, $T$
+to be the length of the material along the ``Time'' axis. 
+Let us define a simpler but equivalent energy model on a 2D lattice of size $S \times T$, whose hamiltonian
+is given by
 \begin{equation}\label{eq:toy-hamiltonian}
@@
 \end{equation}
+
 where $n_{i, t} \in \{0, 1\}$ is the state of the cell at row $i$ and column $t$, the boundary is periodic in the space direction, i.e. $n_{0, t} = n_{S, t}$.
-Its ground state with energy $0$ encodes a $110$ CA, where the direction of computation is from the left to right.
+Its ground state with energy $0$ also encodes a $110$ CA, where the direction of computation is from the left to right.
 \subsection{Numerical result}
 
-\ym{I will move this figure to AppendixB to show the equivalent 
-between heat bath and energy gradient. Another plot would be put here that
-show the TL v.s. $m\ln^{1+\frac{1}{c\ln(\Lambda)}}m$}
-We conducted numerical experiments both for energy-gradient and wave-packet scheme, under the condition
-$\Lambda = 1.3, n = 15$ , and fitted each sweep time against
-$m \log^2(m)$. Where $m$ represents the number of the single layers,
-$n$ represents the width per single layer.
+Here we conducted numerical experiments to examine both the time complexity along the ``Space'' direction and the ``Time'' direction.
+We use binary search to determine the speed of the slowly moving heat bath at which
+the simulated annealing procedure would produce 
+a ground state configuration with $50\%$ probability. Denote this speed 
+as $v$, the simulated annealing procedure will then take $\frac{T}{v}$
+stages to complete the computation, each stage we try to flip a spin with 
+probability define in (\ref{eq:non-equilibrium-SA}). We name $\frac{T}{v}$ 
+as Sweep Time.
 
@@
     \centering
-    \includegraphics[width=\columnwidth,keepaspectratio]{../notes/images/numercial result.pdf}
-    \caption{Time v.s. Depth of the material}
+    \includegraphics[width=\columnwidth,keepaspectratio]{../notes/images/MainNumericalResult.png}
+    \caption{Numerical Result}
+    \label{fig:main-numerical-result}
 \end{figure}
 
-Another numerical experiment are conducted to determine the time complexity of the computation along the input memory direction.
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=\columnwidth,keepaspectratio]{../notes/images/toymodel_time_vs_width.png}
-    \caption{Time v.s. width of the material}
-\end{figure}
-
-This indeed informs that the time scale along the memory direction is linear.
+[Fig. \ref{fig:main-numerical-result}(a)] shows the relationship between
+$\ln(\ln(T))$ and $\ln(\frac{\text{Sweep Time}}{T})$ shoule be linear, which implies 
+the time complexity along the ``Time'' direction should scale as $T\ln(T)^{f(\Lambda)}$. 
+We then fit the slopes of each line and $\frac{1}{\ln(\Lambda)}$ and find the 
+empirical constant $c$ in (\ref{eq:total-annealing-time}) to be $3$. [Fig. \ref{fig:main-numerical-result}(b)] shows 
+the the relationship between Sweep Time and $S$ should be linear. Combining these two results, 
+we can conclude that the time complexity should scales as $TS\log(T)^{1+\frac{1}{3\ln(\Lambda)}}$, 
+which is consistent with our theoretical prediction in (\ref{eq:total-annealing-time}).
+% \begin{figure}[h]
+%     \centering
+%     \begin{minipage}[b]{0.485\columnwidth}
+%         \centering
+%         \includegraphics[width=\columnwidth,keepaspectratio]{../notes/images/TimeComplexityalongTaxis.png}
+%         \caption{Time v.s. Depth of the material}
+%         \label{fig:image1}
+%     \end{minipage}
+%     \hspace{0.001\columnwidth} % 两张图片之间的水平间距
+%     \begin{minipage}[b]{0.485\columnwidth}
+%         \centering
+%         \includegraphics[width=\columnwidth,keepaspectratio]{../notes/images/toymodel_time_vs_width.png}
+%         \caption{Time v.s. width of the material}
+%         \label{fig:image2}
+%     \end{minipage}
+% \end{figure}
 

### 2024-09-05 paper/main.tex

--- 2024-09-05 paper/main.tex
@@
 \end{equation}
+
 where $n_{i, t} \in \{0, 1\}$ is the state of the cell at row $i$ and column $t$, the boundary is periodic in the space direction, i.e. $n_{0, t} = n_{S, t}$.
-Its ground state with energy $0$ encodes a $110$ CA, where the direction of computation is from the left to right.
+Its ground state with energy $0$ also encodes a $110$ CA, where the direction of computation is from the left to right.
 \subsection{Numerical result}
 
-\ym{I will move this figure to AppendixB to show the equivalent 
-between heat bath and energy gradient. Another plot would be put here that
-show the TL v.s. $m\ln^{1+\frac{1}{c\ln(\Lambda)}}m$}
-We conducted numerical experiments both for energy-gradient and wave-packet scheme, under the condition
-$\Lambda = 1.3, n = 15$ , and fitted each sweep time against
-$m \log^2(m)$. Where $m$ represents the number of the single layers,
-$n$ represents the width per single layer.
+\jinguo{show a comparison from right to left}\jinguo{I have already used D as the dimension}}
+\ym{Great, i will do this}
+Here we conducted numerical experiments to examine both the time complexity along the ``Space'' direction and the ``Time'' direction.
+We use binary search to determine the speed of the slowly moving heat bath at which
+the simulated annealing procedure would produce 
+a ground state configuration with $50\%$ probability. Denote this speed 
+as $v$, the simulated annealing procedure will then take $\frac{T}{v}$
+stages to complete the computation, each stage we try to flip a spin with 
+probability define in (\ref{eq:non-equilibrium-SA}). We name $\frac{T}{v}$ 
+as Sweep Time.
 
@@
     \centering
-    \includegraphics[width=\columnwidth,keepaspectratio]{../notes/images/numercial result.pdf}
-    \caption{Time v.s. Depth of the material\jinguo{show a comparison from right to left}\jinguo{I have already used D as the dimension}}
+    \includegraphics[width=\columnwidth,keepaspectratio]{../notes/images/MainNumericalResult.png}
+    \caption{Numerical Result}
+    \label{fig:main-numerical-result}
 \end{figure}
 
-Another numerical experiment are conducted to determine the time complexity of the computation along the input memory direction.
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=\columnwidth,keepaspectratio]{../notes/images/toymodel_time_vs_width.png}
-    \caption{Time v.s. width of the material}
-\end{figure}
-
-This indeed informs that the time scale along the memory direction is linear.
+[Fig. \ref{fig:main-numerical-result}(a)] shows the relationship between
+$\ln(\ln(T))$ and $\ln(\frac{\text{Sweep Time}}{T})$ shoule be linear, which implies 
+the time complexity along the ``Time'' direction should scale as $T\ln(T)^{f(\Lambda)}$. 
+We then fit the slopes of each line and $\frac{1}{\ln(\Lambda)}$ and find the 
+empirical constant $c$ in (\ref{eq:total-annealing-time}) to be $3$. [Fig. \ref{fig:main-numerical-result}(b)] shows 
+the the relationship between Sweep Time and $S$ should be linear. Combining these two results, 
+we can conclude that the time complexity should scales as $TS\log(T)^{1+\frac{1}{3\ln(\Lambda)}}$, 
+which is consistent with our theoretical prediction in (\ref{eq:total-annealing-time}).
+% \begin{figure}[h]
+%     \centering
+%     \begin{minipage}[b]{0.485\columnwidth}
+%         \centering
+%         \includegraphics[width=\columnwidth,keepaspectratio]{../notes/images/TimeComplexityalongTaxis.png}
+%         \caption{Time v.s. Depth of the material}
+%         \label{fig:image1}
+%     \end{minipage}
+%     \hspace{0.001\columnwidth} % 两张图片之间的水平间距
+%     \begin{minipage}[b]{0.485\columnwidth}
+%         \centering
+%         \includegraphics[width=\columnwidth,keepaspectratio]{../notes/images/toymodel_time_vs_width.png}
+%         \caption{Time v.s. width of the material}
+%         \label{fig:image2}
+%     \end{minipage}
+% \end{figure}
 

### 2024-09-05 paper/main.tex
update
update depth label

@@
 It is known that when the system and heat bath are at thermal equilibrium, 
-the probability of a spin configuration $|\mathbf{s}\rangle$ is given by the Boltzmann distribution:
+the probability of a spin configuration $\mathbf{s}$ is given by the Boltzmann distribution:
 
@@
 \begin{equation}
-    |\mathbf{s}\rangle = \frac{1}{Z}\exp\left(- \frac{E_{|\mathbf{s}\rangle}}{k_bT}\right)
-\end{equation}
-
-where $Z = \sum_{|\mathbf{s}\rangle} \exp\left(-\frac{E_{|\mathbf{s}\rangle}}{k_bT}\right)$ is the partition function, 
-$E_{|\mathbf{s}\rangle}$ is the energy of the each of $2^n$ spin configuration, labeled by $|\mathbf{s}\rangle = |s_1, s_2, \cdots, s_n\rangle$, $k_b$ is the Boltzmann constant, and $T$ is the temperature of the heat bath.
+    \mathbf{s} = \frac{1}{Z}\exp\left(- \frac{E_{\mathbf{s}}}{k_bT}\right)
+\end{equation}
+
+where $Z = \sum_{\mathbf{s}} \exp\left(-\frac{E_{\mathbf{s}}}{k_bT}\right)$ is the partition function, 
+$E_{\mathbf{s}}$ is the energy of the each of $2^n$ spin configuration, labeled by $\mathbf{s} = (s_1, s_2, \cdots, s_n)$, $k_b$ is the Boltzmann constant, and $T$ is the temperature of the heat bath.
 In the following, we set $k_b = 1$.
@@
 This algorithm perform a random walk in the state space of the TC, each step we try to flip a spin,
-and the probability of accepting a move from state $|\mathbf{s}\rangle$ to $|\mathbf{s}^\prime\rangle$ is given by:
-
-\begin{equation}
-    P_{\text{accept}} = \frac{1}{1+\exp\left(\frac{E_{|\mathbf{s}^\prime\rangle} - E_{|\mathbf{s}\rangle}}{T}\right)}
+and the probability of accepting a move from state $\mathbf{s}$ to $\mathbf{s}^\prime$ is given by:
+
+\begin{equation}
+    P_{\text{accept}} = \frac{1}{1+\exp\left(\frac{E_{\mathbf{s}^\prime} - E_{\mathbf{s}}}{T}\right)}
 \end{equation}
@@
 (2) Determine the number of layers $W$ that will interact with the external heat bath in each heating-annealing process.
-Group the layers in sets of $W$ from input to output, labeling them as groups $1, 2, \cdots, \frac{T}{W}$.
-The number of heating-annealing repetitions will then be $\frac{T}{W}$, where T is the total number of layers.
+Group the layers in sets of $W$ from input to output, labeling them as groups $1, 2, \cdots, \frac{D}{W}$.
+The number of heating-annealing repetitions will then be $\frac{D}{W}$, where D is the total number of layers.
 (3) Perform the heating-annealing process on each group sequentially.
@@
 Assume there is an annealing procedure that may prevent the layers in the Heat Zone from stabilizing in the local ground state, or equivalently, that an error occurs in the computation process with a probability $\epsilon$.
-Repeating this procedure $\frac{T}{W}$ times would result in a probability of $(1-\epsilon)^{\frac{T}{W}}$ to successfully find the proper global ground state.
-To maintain a constant success probability as $T \rightarrow +\infty$, the error probability $\epsilon$ should scale as $\frac{W}{T}$.
+Repeating this procedure $\frac{D}{W}$ times would result in a probability of $(1-\epsilon)^{\frac{D}{W}}$ to successfully find the proper global ground state.
+To maintain a constant success probability as $D \rightarrow +\infty$, the error probability $\epsilon$ should scale as $\frac{W}{D}$.
 
@@
 \begin{equation}
-    \left( \frac{\lambda_2}{\lambda_1} \right) ^ {t_{th}} = \epsilon \rightarrow t_{th} \sim \ln(\frac{T}{W})e^{W}
-\end{equation}
-
-And the total annealing time scale as $\frac{T}{W}\ln(\frac{T}{W})e^W$.
+    \left( \frac{\lambda_2}{\lambda_1} \right) ^ {t_{th}} = \epsilon \rightarrow t_{th} \sim \ln(\frac{D}{W})e^{W}
+\end{equation}
+
+And the total annealing time scale as $\frac{D}{W}\ln(\frac{D}{W})e^W$.
 
@@
 in fronts of the effective heat zone can only be fliped with a $\epsilon$ probability if the local energy would increase. 
-The effective width $W$ then should scale as $\exp(-\Delta E_{max} \Lambda^{cW}) \sim \epsilon \sim \frac{W}{T}$, where $c$ is the empirical constant for effective width and can be determined during the experiment.
+The effective width $W$ then should scale as $\exp(-\Delta E_{max} \Lambda^{cW}) \sim \epsilon \sim \frac{W}{D}$, where $c$ is the empirical constant for effective width and can be determined during the experiment.
 
@@
     \label{eq:total-annealing-time}
-    t_{total} = \frac{T}{W}(\ln(\frac{T}{W}))^{1+ \frac{1}{c\ln(\Lambda)}}
+    t_{total} = \frac{D}{W}(\ln(\frac{D}{W}))^{1+ \frac{1}{c\ln(\Lambda)}}
 \end{equation}
@@
 
-We fixed the number of layers and denote $n$ as the width of each layer in this material.
+We fixed the number of layers and denote $S$ as the width of each layer in this material.
 
 However, we fail to derive an explicitly expression for the time complexity in this direction. 
-Numerical result shows that computing complexity is linear to $n$. Thus a total time
-for the computation should scale as $nm\log^{1 + \frac{1}{c\ln(\Lambda)}}(m)$
+Numerical result shows that computing complexity is linear to $S$. Thus a total time
+for the computation should scale as $DS\log^{1 + \frac{1}{c\ln(\Lambda)}}(D)$
 
@@
 
-Denote $S$ to be the length of the material along the ``Space'' axis, $T$
+Denote $S$ to be the length of the material along the ``Space'' axis, $D$
 to be the length of the material along the ``Time'' axis. 
-Let us define a simpler but equivalent energy model on a 2D lattice of size $S \times T$, whose hamiltonian
+Let us define a simpler but equivalent energy model on a 2D lattice of size $S \times D$, whose hamiltonian
 is given by
 \begin{equation}\label{eq:toy-hamiltonian}
-H = \sum_{t=1}^{T-1}\sum_{i=1}^{S} (n_{i+1, t} \land \neg(n_{i, t} \land \neg n_{i-1, t})) \veebar n_{i,t+1},
+H = \sum_{t=1}^{D-1}\sum_{i=1}^{S} (n_{i+1, t} \land \neg(n_{i, t} \land \neg n_{i-1, t})) \veebar n_{i,t+1},
 \end{equation}
@@
 
-\jinguo{show a comparison from right to left}\jinguo{I have already used D as the dimension}}
+\jinguo{show a comparison from right to left}\jinguo{I have already used D as the dimension}
 \ym{Great, i will do this}
@@
 a ground state configuration with $50\%$ probability. Denote this speed 
-as $v$, the simulated annealing procedure will then take $\frac{T}{v}$
+as $v$, the simulated annealing procedure will then take $\frac{D}{v}$
 stages to complete the computation, each stage we try to flip a spin with 
-probability define in (\ref{eq:non-equilibrium-SA}). We name $\frac{T}{v}$ 
+probability define in (\ref{eq:non-equilibrium-SA}). We name $\frac{D}{v}$ 
 as Sweep Time.
@@
 [Fig. \ref{fig:main-numerical-result}(a)] shows the relationship between
-$\ln(\ln(T))$ and $\ln(\frac{\text{Sweep Time}}{T})$ shoule be linear, which implies 
-the time complexity along the ``Time'' direction should scale as $T\ln(T)^{f(\Lambda)}$. 
+$\ln(\ln(D))$ and $\ln(\frac{\text{Sweep Time}}{D})$ shoule be linear, which implies 
+the time complexity along the ``Time'' direction should scale as $D\ln(D)^{f(\Lambda)}$. 
 We then fit the slopes of each line and $\frac{1}{\ln(\Lambda)}$ and find the 
@@
 the the relationship between Sweep Time and $S$ should be linear. Combining these two results, 
-we can conclude that the time complexity should scales as $TS\log(T)^{1+\frac{1}{3\ln(\Lambda)}}$, 
+we can conclude that the time complexity should scales as $DS\log(D)^{1+\frac{1}{3\ln(\Lambda)}}$, 
 which is consistent with our theoretical prediction in (\ref{eq:total-annealing-time}).

### 2024-09-05 paper/main.tex
fixed some typo

@@
 A universal set logic gate gadgets are designed, by concatenating which any logic circuit can be constructed.
-For example the logic expression $z = \neg (x \land y)$ can be encoded into the Ising model by the following Hamiltonian:
+For example the logic expression $z = \neg (a \land b)$ can be encoded into the Ising model by the following Hamiltonian:
 \begin{equation}
@@
 By converting the gadget finding problem to a linear programming problem~\cite{Kolman1995}, we propose a provable optimal method to encode any CA rule into the Ising model, which is described in \Cref{sec:gadget-design}.
-The proposed gadget for the $110$ rule is shown in \Cref{Surface-programmable-thermodynamic computer}(b), which only requires 1 ancilla spin.
-The interaction energy and onsite energy of the rule 110 gadget are given below, where $p, q, r$ and inputs and $q'$ is the output in \Cref{Surface-programmable-thermodynamic computer}(b), respectively, while spin $A$ is the auxiliary spin.
+The proposed gadget for the $110$ rule is shown in \Cref{Surface-programmable-thermodynamic computer}, which only requires 1 ancilla spin.
+The interaction energy and onsite energy of the rule 110 gadget are given below, where $p, q, r$ and inputs and $q'$ is the output in \Cref{Surface-programmable-thermodynamic computer}, respectively, while spin $A$ is the auxiliary spin.
 \begin{equation}

### 2024-09-05 paper/main.tex
update

--- 2024-09-05 paper/main.tex
@@
 \begin{equation}
-    \label{eq:total-annealing-time}
     t_{total} = \frac{T}{W}(\ln(\frac{T}{W}))^{1+ \frac{1}{c\ln(\Lambda)}}
@@
 \begin{equation}
-    \label{eq:non-equilibrium-SA}
 P = \frac{1}{1 + e^{\sum_i \frac{\Delta E_i}{T_i}}}
@@
 
-Denote $S$ to be the length of the material along the ``Space'' axis, $T$
-to be the length of the material along the ``Time'' axis. 
-Let us define a simpler but equivalent energy model on a 2D lattice of size $S \times T$, whose hamiltonian
-is given by
+Let us define a model Hamiltonian on a 2D lattice of size $S \times T$ as
 \begin{equation}\label{eq:toy-hamiltonian}
@@
 \end{equation}
-
 where $n_{i, t} \in \{0, 1\}$ is the state of the cell at row $i$ and column $t$, the boundary is periodic in the space direction, i.e. $n_{0, t} = n_{S, t}$.
-Its ground state with energy $0$ also encodes a $110$ CA, where the direction of computation is from the left to right.
+Its ground state with energy $0$ encodes a $110$ CA, where the direction of computation is from the left to right.
 \subsection{Numerical result}
 
-\jinguo{show a comparison from right to left}\jinguo{I have already used D as the dimension}}
-\ym{Great, i will do this}
-Here we conducted numerical experiments to examine both the time complexity along the ``Space'' direction and the ``Time'' direction.
-We use binary search to determine the speed of the slowly moving heat bath at which
-the simulated annealing procedure would produce 
-a ground state configuration with $50\%$ probability. Denote this speed 
-as $v$, the simulated annealing procedure will then take $\frac{T}{v}$
-stages to complete the computation, each stage we try to flip a spin with 
-probability define in (\ref{eq:non-equilibrium-SA}). We name $\frac{T}{v}$ 
-as Sweep Time.
+\ym{I will move this figure to AppendixB to show the equivalent 
+between heat bath and energy gradient. Another plot would be put here that
+show the TL v.s. $m\ln^{1+\frac{1}{c\ln(\Lambda)}}m$}
+We conducted numerical experiments both for energy-gradient and wave-packet scheme, under the condition
+$\Lambda = 1.3, n = 15$ , and fitted each sweep time against
+$m \log^2(m)$. Where $m$ represents the number of the single layers,
+$n$ represents the width per single layer.
 
@@
     \centering
-    \includegraphics[width=\columnwidth,keepaspectratio]{../notes/images/MainNumericalResult.png}
-    \caption{Numerical Result}
-    \label{fig:main-numerical-result}
+    \includegraphics[width=\columnwidth,keepaspectratio]{../notes/images/numercial result.pdf}
+    \caption{Time v.s. Depth of the material\jinguo{show a comparison from right to left}\jinguo{I have already used D as the dimension}}
 \end{figure}
 
-[Fig. \ref{fig:main-numerical-result}(a)] shows the relationship between
-$\ln(\ln(T))$ and $\ln(\frac{\text{Sweep Time}}{T})$ shoule be linear, which implies 
-the time complexity along the ``Time'' direction should scale as $T\ln(T)^{f(\Lambda)}$. 
-We then fit the slopes of each line and $\frac{1}{\ln(\Lambda)}$ and find the 
-empirical constant $c$ in (\ref{eq:total-annealing-time}) to be $3$. [Fig. \ref{fig:main-numerical-result}(b)] shows 
-the the relationship between Sweep Time and $S$ should be linear. Combining these two results, 
-we can conclude that the time complexity should scales as $TS\log(T)^{1+\frac{1}{3\ln(\Lambda)}}$, 
-which is consistent with our theoretical prediction in (\ref{eq:total-annealing-time}).
-% \begin{figure}[h]
-%     \centering
-%     \begin{minipage}[b]{0.485\columnwidth}
-%         \centering
-%         \includegraphics[width=\columnwidth,keepaspectratio]{../notes/images/TimeComplexityalongTaxis.png}
-%         \caption{Time v.s. Depth of the material}
-%         \label{fig:image1}
-%     \end{minipage}
-%     \hspace{0.001\columnwidth} % 两张图片之间的水平间距
-%     \begin{minipage}[b]{0.485\columnwidth}
-%         \centering
-%         \includegraphics[width=\columnwidth,keepaspectratio]{../notes/images/toymodel_time_vs_width.png}
-%         \caption{Time v.s. width of the material}
-%         \label{fig:image2}
-%     \end{minipage}
-% \end{figure}
+Another numerical experiment is conducted to determine the time complexity of the computation along the input memory direction.
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=\columnwidth,keepaspectratio]{../notes/images/toymodel_time_vs_width.png}
+    \caption{Time v.s. width of the material}
+\end{figure}
+
+This indeed informs that the time scale along the memory direction is linear.
 
@@
 \begin{acknowledgments}
-    We thank Lei Wang, Madelyn Cain and XXX for helpful discussions on the simulation methods.
+    %We thank Lei Wang, Madelyn Cain and XXX for helpful discussions on the simulation methods.
 \end{acknowledgments}

### 2024-09-05 paper/main.tex

--- 2024-09-05 paper/main.tex
@@
 It features a crystalline structure that encodes the time evolution of a universal CA that capable of performing universal computation.
-To encode a $D$-dimensional CA, we need a $D+1$-dimensional crystal. The extra dimension is used to encode the time-axis of the CA.
-For simplicity, we will focus on the 1D 110 rule elementary CA in the rest of this paper.
+To encode a $d$-dimensional CA, we need a $d+1$-dimensional crystal. The extra dimension is used to encode the time-axis of the CA.
+For simplicity, we will focus on the one dimensional 110 rule elementary CA in the rest of this paper.
 The physical implementation of the TC is based on the Ising model, where we use the spin up and down to encode the state $1$ and $0$ of the cellular automata, respectively.

### 2024-09-05 paper/main.tex
update

@@
 Instead of performing the computation deterministically, TCs are stochastic and are driven by thermodynamics.
-Physical implementations of TCs include DNA machines~\cite{tanaka2005design}, memristors~\cite{yang2013memristive, wang2017memristors, kumar2017chaotic, wang2018fully}, and Ising machines~\cite{gu2012encoding, lucas2014ising, mohseni2022ising, fabre2014optical}.
+Physical implementations of TCs include DNA machines~\cite{tanaka2005design} and Ising machines~\cite{gu2012encoding, lucas2014ising, mohseni2022ising, fabre2014optical}.
+% memristors~\cite{yang2013memristive, wang2017memristors, kumar2017chaotic, wang2018fully},
 
@@
 The former is known as the Brownian machine, which evolves the system toward the direction of the entropy increase, while the latter are energy based, which evolves the system toward the direction of the energy decrease.
-\jinguo{What category are the memristors?} \ym{Memristors are energy based, which evolves the system toward the direction of the energy decrease.}
 
@@
 
+\ym{
+    The material was orderly grown by slowly moving the temperature gradient in-plane~\cite{Zhang2014}. Tested thermal gradient force for grain boundary migration~\cite{Bai2015}.
+}
+We test the hypothesis: Cooling is easy if the process is from the
+deterministic direction, hard if the process is from the
+non-deterministic direction.
+
+\begin{hyp}
+Let $\mathcal{P}$ be a circuit SAT problem, and $\mathcal{E}$ be an energy modeling encoding of $\mathcal{P}$ (locally).
+There exists a subset of $\mathcal{E}$ that exhibits the overlap gap property~\cite{Gamarnik2021}.
+\end{hyp}
+\jinguo{Leave this issue to Maddie}
+The overlap gap property is a property for describing the algorithmic intractability in random structures, which is based on the topological disconnectivity property of the set of pair-wise distances of near optimal solutions.
+If the energy landscape of a optimization problem exhibits the overlap gap property, then it can not be solved by any local algorithms in polynomial time, including the simulated annealing method used in this work.
+The intuition comes from the energy model encoding of the identity circuit.
+Given a circuit with $n$ bits, the ground state degeneracy of the corresponding energy model is at least $2^n$.
+The energy model can be vertically stacked $n$ copy gadgets.
+Let the circuit depth be $d \sim 2^{\gamma \sqrt{n}}$ for some constant $\gamma > 0$.
+The Hamming distance between two degenerate ground states for different input signals is at least $d$, which is exponential to $n$.
+Let us define the size of the problem as $d\times n$, then this distance is clearly linear to the problem size.
+We left the rigorous proof of this hypothesis to mathematicians.
+
 \subsection{Cooling computation with a moving heat bath}\label{cooling-computation-with-moving-heat-bath}
@@
 % However, solving the ground state from the non-deterministic direction is at least as hard as solving the circuit satisfiability problem, which is NP-complete~\cite{Moore2011}.
-
-\subsection{Computing by cooling}\label{local-cooling}
-
-\ym{
-    The material was orderly grown by slowly moving the temperature gradient in-plane~\cite{Zhang2014}. Tested thermal gradient force for grain boundary migration~\cite{Bai2015}.
-}
-We test the hypothesis: Cooling is easy if the process is from the
-deterministic direction, hard if the process is from the
-non-deterministic direction.
-
-\begin{hyp}
-Let $\mathcal{P}$ be a circuit SAT problem, and $\mathcal{E}$ be an energy modeling encoding of $\mathcal{P}$ (locally).
-There exists a subset of $\mathcal{E}$ that exhibits the overlap gap property~\cite{Gamarnik2021}.
-\end{hyp}
-The overlap gap property is a property for describing the algorithmic intractability in random structures, which is based on the topological disconnectivity property of the set of pair-wise distances of near optimal solutions.
-If the energy landscape of a optimization problem exhibits the overlap gap property, then it can not be solved by any local algorithms in polynomial time, including the simulated annealing method used in this work.
-The intuition comes from the energy model encoding of the identity circuit.
-Given a circuit with $n$ bits, the ground state degeneracy of the corresponding energy model is at least $2^n$.
-The energy model can be vertically stacked $n$ copy gadgets.
-Let the circuit depth be $d \sim 2^{\gamma \sqrt{n}}$ for some constant $\gamma > 0$.
-The Hamming distance between two degenerate ground states for different input signals is at least $d$, which is exponential to $n$.
-Let us define the size of the problem as $d\times n$, then this distance is clearly linear to the problem size.
-We left the rigorous proof of this hypothesis to mathematicians.
 
@@
 
-There is no solution with 4-atoms spin-glass that can satisfy the
-constraints. The minimum number of atoms required to satisfy the
+We set the $S_{\text{min}}$ to be the eight degenerate ground states of the spin-glass model to implement the $110$ rule.
+This is overly strict, as we do not consider the case that the ground states for different input signals to have degeneracy.
+The minimum number of atoms required to satisfy the
 constraints is 5. We set the target states to

### 2024-09-05 paper/main.tex
fix notation issues

@@
 \newcommand{\net}[1]{{\textsc{#1}}}
+\newcommand{\vs}{{\mathbf{s}}}
+\newcommand{\vn}{{\mathbf{n}}}
 \newcommand{\argmin}{\mathop{\mathrm{argmin}}\limits}
@@
 Improving the energy efficiency of computation is a major challenge in the development of future computing systems.
-The thermodynamic computer (TC)~\cite{conte2019thermodynamic} is a new type of computer that uses thermodynamics to perform computation.
+The thermodynamic computer (TC)~\cite{conte2019thermodynamic, hylton2021vision} is a new type of computer that uses thermodynamics to perform computation.
 Instead of performing the computation deterministically, TCs are stochastic and are driven by thermodynamics.
@@
 \begin{equation}
-H = \sum_{i < j} J_{ij}s_us_v + \sum_{i=1}^{n}h_i s_i
+E(\vs) = \sum_{i < j} J_{ij}s_us_v + \sum_{i=1}^{n}h_i s_i
 \end{equation}
@@
     \begin{split}
-        H_{c = a \land b} &= s_a s_b -2 s_a s_c -2 s_bs_c + s_a + s_b -2 s_c\\
-        H_{z = \neg c} &= s_c s_z\\
-        H_{z = \neg (a \land b)} &= H_{z = \neg c} + H_{c = a \land b}
+        E_{c = a \land b} &= s_a s_b -2 s_a s_c -2 s_bs_c + s_a + s_b -2 s_c\\
+        E_{z = \neg c} &= s_c s_z\\
+        E_{z = \neg (a \land b)} &= E_{z = \neg c} + E_{c = a \land b}
     \end{split}
@@
 the probability of a spin configuration $\mathbf{s}$ is given by the Boltzmann distribution:
-
-\jinguo{please do not use the ket bra notation}
-\begin{equation}
-    \mathbf{s} = \frac{1}{Z}\exp\left(- \frac{E_{\mathbf{s}}}{k_bT}\right)
-\end{equation}
-
-where $Z = \sum_{\mathbf{s}} \exp\left(-\frac{E_{\mathbf{s}}}{k_bT}\right)$ is the partition function, 
-$E_{\mathbf{s}}$ is the energy of the each of $2^n$ spin configuration, labeled by $\mathbf{s} = (s_1, s_2, \cdots, s_n)$, $k_b$ is the Boltzmann constant, and $T$ is the temperature of the heat bath.
+\begin{equation}
+    p(\mathbf{s}) = \frac{1}{Z}\exp\left(- \frac{E({\mathbf{s}})}{k_bT}\right),
+\end{equation}
+where $Z = \sum_{\mathbf{s}} \exp\left(-\frac{E({\mathbf{s}})}{k_bT}\right)$ is the partition function, 
+$E({\mathbf{s}})$ is the energy of the each of $2^n$ spin configuration, labeled by $\mathbf{s} = (s_1, s_2, \cdots, s_n)$, $k_b$ is the Boltzmann constant, and $T$ is the temperature of the heat bath.
 In the following, we set $k_b = 1$.
@@
 and the probability of accepting a move from state $\mathbf{s}$ to $\mathbf{s}^\prime$ is given by:
-
-\begin{equation}
-    P_{\text{accept}} = \frac{1}{1+\exp\left(\frac{E_{\mathbf{s}^\prime} - E_{\mathbf{s}}}{T}\right)}
-\end{equation}
-
-This accepting probability follows from the glauber dynamics~\cite{glauber1963time}.
-It can be shown that this process is markovian and ergodic, and the system will eventually reach the thermal equilibrium.
+\begin{equation}
+    P_{\text{accept}} = \frac{1}{1+\exp\left(\frac{E({\mathbf{s}^\prime}) - E({\mathbf{s}})}{T}\right)}.
+\end{equation}
+This accepting probability follows from the Glauber dynamics~\cite{glauber1963time}.
+It can be shown that this process is Markovian and ergodic, and the system will eventually reach the thermal equilibrium.
 To determine the speed of the convergence, we should notice the spectral gap of the transition matrix of the Markov chain, which is defined as
@@
 \begin{equation}\label{eq:toy-hamiltonian}
-H = \sum_{t=1}^{D-1}\sum_{i=1}^{S} (n_{i+1, t} \land \neg(n_{i, t} \land \neg n_{i-1, t})) \veebar n_{i,t+1},
+E(\vn) = \sum_{t=1}^{D-1}\sum_{i=1}^{S} (n_{i+1, t} \land \neg(n_{i, t} \land \neg n_{i-1, t})) \veebar n_{i,t+1},
 \end{equation}
@@
 
-\section{The implmentation in Rydberg atoms array}\label{physical-model-rydberg-atoms-array}
+\section{The implementation in Rydberg atoms array}\label{physical-model-rydberg-atoms-array}
 Let us consider a Rydberg atoms array with a two dimensional embedding. The coordinate of the atom $v$ is denoted as $\mathbf{r}_v$.

### 2024-09-05 paper/main.tex
update

@@
 
+\jinguo{
+    Need to introduce the heat zone.
+}
+
 The computational process of the CA is divided into three steps: determining the state of each input cell, iteratively applying the transition rules to generate the next generation of cells, and identifying a certain generation of cells as the output.
@@
 
-\section{The implementation in Rydberg atoms array}\label{physical-model-rydberg-atoms-array}
-Let us consider a Rydberg atoms array with a two dimensional embedding. The coordinate of the atom $v$ is denoted as $\mathbf{r}_v$.
-The Rydberg Hamiltonian~\cite{Nguyen2023} is defined as
-
-\begin{equation}
-    H_{\text{Ryd}} = \sum_v \dfrac{\Omega_v}{2} \sigma^x_v -\sum_v \Delta_v n_v + \sum_{v < w}  V_{\text{Ryd}}(|\overrightarrow{\mathbf{r}_v} -\overrightarrow{\mathbf{r}_w}|)n_v n_w,
-\end{equation}
-where $\Omega_v$ is the Rabi frequency, $\Delta_v$ is the detuning,
-$n_v = \dfrac{1}{2}(1 - \sigma^z_v)$ is the number operator, and
-$V_{\text{Ryd}}(|\overrightarrow{\mathbf{r}_v} - \overrightarrow{\mathbf{r}_w}|) = C_6/|\overrightarrow{\mathbf{r}_v} - \overrightarrow{\mathbf{r}_w}|^6$
-is the Rydberg interaction potential.
-
-In the following, we will show the classical part of the Rydberg Hamiltonian encodes an independent set problem on a unit disk graph.
-In graph theory, an independent set is a set of vertices in a graph, no two of which are adjacent.
-Here, we restrict the graph to be a two dimensional unit disk graph $G=(V, E)$, a geometric graph with two dimensional embedding, such that two vertices $u, v \in V$ are connected if and only if they are within the unit radius, i.e.
-$|\mathbf r_u - \mathbf r_v| < r_B$.
-This reflects the blockade phenomenon in Rydberg atoms arrays, where two atoms within blockade radius $r_B$ can not excite to the Rydberg state simultaneously due to the strong Rydberg interaction potential.
-Let us idealize the energy model by treating the blockade interaction between two atoms as infinity if two atoms are within blockade radius, zero otherwise.
-Then the energy model becomes
-\begin{equation}
-H_{\text{MWIS}} = -\sum_{v \in V}\Delta_v n_v + \sum_{(u, v) \in E} \infty n_u n_v.
-\end{equation}
-The ground state of which encodes the maximum weight independent set (MWIS) problem, and $\Delta_v$ is the weight associated with vertex $v \in V$.
-Whenever we have a atom in the Rydberg state in the ground state of $H_{\text{WMIS}}$, we add the vertex associated with that atom to the maximum independent set.
-
-\subsection{Gadget finding}
-Given a target logic gate, the goal is to find a graph $G = (V, E)$ and weights associated with vertices $\{\Delta_v \mid v\in V\}$ such that the WMIS problem of this graph encodes this gate.
-
-Let $\mathcal{M}$ be the set of all maximal independent sets of $G$, where a maximal independent set is an independent set that is not a subset of any other independent set.
-Each $\mathbf n \in \mathcal{M}$ is associated with an energy $H_{\text{WMIS}}(\mathbf n) = -\sum_v \Delta_v n_v$.
-We denote the target states with minimum energy as $\mathcal{M}_{\text{min}} \subseteq \mathcal{M}$.
-We can express the linear programming problem as
-
-\begin{equation}
-    \begin{split}
-        &\min_{\boldsymbol{\Delta} \in \mathbb{R}^{|V|}} 0\\
-        &\sum_i n_i' \Delta_i < \sum_i n_i \Delta_i, \forall \mathbf n \in \mathcal{M}_{\text{min}}, \mathbf n' \in \mathcal{M} \setminus \mathcal{M}_{\text{min}}\\
-        &\sum_i n_i \Delta_i = \sum_i n_i' \Delta_i, \forall \mathbf n, \mathbf n' \in \mathcal{M}_{\text{min}}
-    \end{split}
-\end{equation}
-
-Note that the constraints are all linear. The less constraints and equality constraints can be easily transformed into inequality constraints by adding ancilla variables.
-The possible choice of $S_{\text{min}}$ grows exponentially as the number of ancilla vertices increases, which limits the capability of this method.
-\jinguo{We focus on the general graphs first.}
-
-In the following, we restrict the graph to be two dimensional grid graphs, the unit distance can be arbitrary. A graph configuration can be denoted as a boolean mask $M\in \{0, 1\}^{m\times n}$.
-\jinguo{Then the unit disk graphs.}
-
-\subsubsection{Energy based universal computation with Rydberg atoms
-array}\label{energy-based-universal-computation-with-rydberg-atoms-array}
-
-\textbf{Statement 3}: The classical Rydberg Hamiltonian is universal for classical computation.
-
-The NOR gate can be implemented using the Rydberg Hamiltonian (subfigure
-c below). The NOR gate is a universal gate for classical computation.
-\includegraphics[width=\columnwidth]{../notes/images/gadgets.png}
-
-The conjunction of gates can be implemented by ``gluing'' the Rydberg
-atoms together (subfigure d below). The weights are added together.
-
-For more logic gates, please check the GitHub repository
-\href{https://github.com/QuEraComputing/UnitDiskMapping.jl/blob/main/test/logicgates.jl}{UnitDiskMapping.jl}.
-
-\subsubsection{Cooling the Rydberg Hamiltonian}\label{cooling-the-rydberg-hamiltonian}
-
-\textbf{Statement 4}: The Rydberg Hamiltonian, if cooled successfully
-with some vertices fixed to certain configuration, can be used to solve
-the circuit satisfiability problem, which is NP-complete~\cite{Moore2011}.
-
-$P \neq NP$: Cooling is generally hard, especially when from the
-non-deterministic direction.
-
-\subsubsection{The Rule 110 Gadget}\label{the-rule-110-gadget}
-
-We can encode the Rule 110 CA into a Weighted Maximum
-Independent Set Problem, with blue vertices assigned a weight of 1 and
-red vertices assigned a weight of 2, as follows.
-
-\includegraphics[width=0.6\columnwidth]{../notes/images/image.png}
-
-This graph can be embedded into a grid graph, where two vertices are
-connected if and only if their Euclidean distance is no more than $2$.
-
-\includegraphics[width=0.7\columnwidth]{../notes/images/image-1.png}
-
-The correspondence between the Maximum Weighted Independent Set (MWIS)
-Solution and Rule 110 is as follows:
-
-The states of vertex \textbf{1}, vertex \textbf{3}, and vertex
-\textbf{8} represent the states of the \textbf{middle}, \textbf{left},
-and \textbf{right} cells of the automata's \textbf{input},
-respectively. If the input value of a cell is 1, then the corresponding
-vertex must be in the MWIS solution; otherwise, it is not. Vertex
-\textbf{12} corresponds to the automata's \textbf{output}. If the
-automata output is 1, then vertex 12 is in the MWIS solution;
-otherwise, it is not.
-
-In the automata diagram, the above gadget is equivalent to:
-
-\begin{figure}
-\centering
-\includegraphics[width=\columnwidth]{../notes/images/rule110.png}
-\caption{Alt text}
-\end{figure}
-
-There are exactly \textbf{8} different MWIS solutions in this graph (the
-weighted size of each MWIS solution is 7), each corresponding to one of
-the \textbf{8} possible outputs of the automata. We list them as
-follows.
-\includegraphics[width=\columnwidth]{../notes/images/gadget110.png}
-
-Utilizing copy gadget and cross gadget~\cite{Nguyen2023}, we construct a \textbf{Surface Programmable Material} with open boundary conditions as follows.
-
-\begin{figure}
-\centering
-\includesvg[width=\columnwidth]{../notes/images/rule110transvarient.svg}
-\caption{Alt text}
-\end{figure}
-
-The above gadget depicts a two-layer CA. The vertices in
-blue, red, green and black have weights of 1, 2, 3 and 4, respectively.
-In the automata diagram, the above gadget is equivalent to:
-
-\begin{figure}
-\centering
-\includegraphics[width=\columnwidth]{../notes/images/rule110_2-2_automata.png}
-\caption{Alt text}
-\end{figure}
-
 \subsection{Speed and work}\label{speed-and-work}

### 2024-09-05 rydberg/main.tex
update

% !TEX program = xelatex
\documentclass[twocolumn,superscriptaddress,english,showpacs,longbibliography]{revtex4-2}
\usepackage[colorlinks=true,urlcolor=blue,citecolor=blue,linkcolor=blue]{hyperref}

\usepackage{svg}
\usepackage{amsmath}
\usepackage{graphicx}% Include figure files
\usepackage{textcomp}
\usepackage{bm}% bold math
\usepackage{color}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{graphicx}
\usepackage{color}
\usepackage{mathrsfs}
\usepackage{float}
\usepackage{indentfirst}
\usepackage{txfonts}
\usepackage{algorithm}  
\usepackage{algpseudocode}  
\usepackage{balance}
\usepackage{flushend}
\usepackage{cleveref}
\usepackage{blkarray}
\usepackage{tikz}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}  % Use Input in the format of Algorithm  
\renewcommand{\algorithmicensure}{\textbf{Output:}} % Use Output in the format of Algorithm  
\newtheorem{hyp}{Hypothesis}

\newcommand{\jinguo}[1]{[{\color{red}{JGL: #1}}]}
\newcommand{\ym}[1]{[{\color{blue}{YM: #1}}]}
\newcommand{\s}{\mathbf {s}}
\newcommand{\net}[1]{{\textsc{#1}}}
\newcommand{\vs}{{\mathbf{s}}}
\newcommand{\vn}{{\mathbf{n}}}
\newcommand{\argmin}{\mathop{\mathrm{argmin}}\limits}
\newcommand{\Eq}[1]{Eq.~(\ref{#1})}
\newcommand{\Fig}[1]{Fig.~\ref{#1}}

\begin{document}

\title{Crystal as a thermodynamic computer}

\author{Authors}
\email{xxx@xxx.com}
\affiliation{
    XXX
}

\begin{abstract}
\end{abstract}

\maketitle

\section{The implementation in Rydberg atoms array}\label{physical-model-rydberg-atoms-array}
Let us consider a Rydberg atoms array with a two dimensional embedding. The coordinate of the atom $v$ is denoted as $\mathbf{r}_v$.
The Rydberg Hamiltonian~\cite{Nguyen2023} is defined as
\begin{equation}
    H_{\text{Ryd}} = \sum_v \dfrac{\Omega_v}{2} \sigma^x_v -\sum_v \Delta_v n_v + \sum_{v < w}  V_{\text{Ryd}}(|\overrightarrow{\mathbf{r}_v} -\overrightarrow{\mathbf{r}_w}|)n_v n_w,
\end{equation}
where $\Omega_v$ is the Rabi frequency, $\Delta_v$ is the detuning,
$n_v = \dfrac{1}{2}(1 - \sigma^z_v)$ is the number operator, and
$V_{\text{Ryd}}(|\overrightarrow{\mathbf{r}_v} - \overrightarrow{\mathbf{r}_w}|) = C_6/|\overrightarrow{\mathbf{r}_v} - \overrightarrow{\mathbf{r}_w}|^6$
is the Rydberg interaction potential.

In the following, we will show the classical part of the Rydberg Hamiltonian encodes an independent set problem~\cite{Moore2011} on a unit disk graph.
In graph theory, an independent set is a set of vertices in a graph, no two of which are adjacent.
Here, we restrict the graph to be a two dimensional unit disk graph $G=(V, E)$, a geometric graph with two dimensional embedding, such that two vertices $u, v \in V$ are connected if and only if they are within the unit radius, i.e. $|\mathbf r_u - \mathbf r_v| < r_B$. This reflects the blockade phenomenon in Rydberg atoms arrays, where two atoms within blockade radius $r_B$ can not excite to the Rydberg state simultaneously due to the strong Rydberg interaction potential. Let us idealize the energy model by treating the blockade interaction between two atoms as infinity if two atoms are within blockade radius, zero otherwise. Then the energy model becomes
\begin{equation}
H_{\text{MWIS}} = -\sum_{v \in V}\Delta_v n_v + \sum_{(u, v) \in E} \infty n_u n_v.
\end{equation}
The ground state of which encodes the maximum weight independent set (MWIS) problem, and $\Delta_v$ is the weight associated with vertex $v \in V$. Whenever we have a atom in the Rydberg state in the ground state of $H_{\text{WMIS}}$, we add the vertex associated with that atom to the maximum independent set.

\section{Gadget finding}
Given a target logic gate, the goal is to find a graph $G = (V, E)$ and weights associated with vertices $\{\Delta_v \mid v\in V\}$ such that the WMIS problem of this graph encodes this gate.

Let $\mathcal{M}$ be the set of all maximal independent sets of $G$, where a maximal independent set is an independent set that is not a subset of any other independent set.
Each $\mathbf n \in \mathcal{M}$ is associated with an energy $H_{\text{WMIS}}(\mathbf n) = -\sum_v \Delta_v n_v$. We denote the target states with minimum energy as $\mathcal{M}_{\text{min}} \subseteq \mathcal{M}$. We can express the linear programming problem as
\begin{equation}\label{eq:lp}
    \begin{split}
        &\min_{\boldsymbol{\Delta} \in \mathbb{R}^{|V|}} 0\\
        &\sum_i n_i' \Delta_i < \sum_i n_i \Delta_i, \forall \mathbf n \in \mathcal{M}_{\text{min}}, \mathbf n' \in \mathcal{M} \setminus \mathcal{M}_{\text{min}}\\
        &\sum_i n_i \Delta_i = \sum_i n_i' \Delta_i, \forall \mathbf n, \mathbf n' \in \mathcal{M}_{\text{min}}
    \end{split}
\end{equation}
Note that the constraints are all linear. The less constraints and equality constraints can be easily transformed into inequality constraints by adding ancilla variables.
The possible choice of $S_{\text{min}}$ grows exponentially as the number of ancilla vertices increases, which limits the capability of this method.
\jinguo{We focus on the general graphs first.}

In the following, we restrict the graph to be two dimensional grid graphs, the unit distance can be arbitrary. A graph configuration can be denoted as a boolean mask $M\in \{0, 1\}^{m\times n}$.
\jinguo{Then the unit disk graphs.}

\subsection{Energy based universal computation with Rydberg atoms
array}\label{energy-based-universal-computation-with-rydberg-atoms-array}

The classical Rydberg Hamiltonian is universal for classical computation, since the NOR gate can be implemented using the Rydberg Hamiltonian (subfigure
c below). The NOR gate is a universal gate for classical computation.
\includegraphics[width=\columnwidth]{../notes/images/gadgets.png}

The conjunction of gates can be implemented by ``gluing'' the Rydberg
atoms together (subfigure d below). The weights are added together.

For more logic gates, please check the GitHub repository
\href{https://github.com/QuEraComputing/UnitDiskMapping.jl/blob/main/test/logicgates.jl}{UnitDiskMapping.jl}.

\subsection{The Rule 110 Gadget}\label{the-rule-110-gadget}

We can encode the Rule 110 CA into a Weighted Maximum
Independent Set Problem, with blue vertices assigned a weight of 1 and
red vertices assigned a weight of 2, as follows.

\includegraphics[width=0.6\columnwidth]{../notes/images/image.png}

This graph can be embedded into a grid graph, where two vertices are
connected if and only if their Euclidean distance is no more than $2$.

\includegraphics[width=0.7\columnwidth]{../notes/images/image-1.png}

The correspondence between the Maximum Weighted Independent Set (MWIS)
Solution and Rule 110 is as follows:

The states of vertex \textbf{1}, vertex \textbf{3}, and vertex
\textbf{8} represent the states of the \textbf{middle}, \textbf{left},
and \textbf{right} cells of the automata's \textbf{input},
respectively. If the input value of a cell is 1, then the corresponding
vertex must be in the MWIS solution; otherwise, it is not. Vertex
\textbf{12} corresponds to the automata's \textbf{output}. If the
automata output is 1, then vertex 12 is in the MWIS solution;
otherwise, it is not.

In the automata diagram, the above gadget is equivalent to:
There are exactly \textbf{8} different MWIS solutions in this graph (the
weighted size of each MWIS solution is 7), each corresponding to one of
the \textbf{8} possible outputs of the automata. We list them as
follows.
\includegraphics[width=\columnwidth]{../notes/images/gadget110.png}

Utilizing copy gadget and cross gadget~\cite{Nguyen2023}, we construct a \textbf{Surface Programmable Material} with open boundary conditions as follows.

\begin{figure}
\centering
\includesvg[width=\columnwidth]{../notes/images/rule110transvarient.svg}
\caption{Alt text}
\end{figure}

The above gadget depicts a two-layer CA. The vertices in
blue, red, green and black have weights of 1, 2, 3 and 4, respectively.
In the automata diagram, the above gadget is equivalent to:

\jinguo{Tasks:
\begin{enumerate}
    \item Implement the gadget design algorithm in \Cref{eq:lp}.
    \item Use the algorithm to search for all two-bit logic gates and CA rules.
    \item Generate all unit disk graphs with size < 15 (please check \href{https://github.com/GiggleLiu/SmallGraphs}{small graph zoo}).
    \item Use the algorithm to search for MWIS gadgets on unit disk graphs.
\end{enumerate}
}

\begin{acknowledgments}
    %We thank Lei Wang, Madelyn Cain and XXX for helpful discussions on the simulation methods.
\end{acknowledgments}

%\bibliographystyle{apsrev4-1}
\bibliography{refs.bib}

\appendix

\end{document}

### 2024-09-05 paper/main.tex
update

@@
 
-\subsection{Energy model}\label{a-2d-surface-programmable-material}
-
-Given that simulating a CA with a deep computational layer on the Ising model requires a large number of spins, making large-scale numerical simulations impractical, we opted to introduce a similar but simpler energy model to observe the behavior on a larger scale.
-
-Denote $S$ to be the length of the material along the ``Space'' axis, $D$
-to be the length of the material along the ``Time'' axis. 
-Let us define a simpler but equivalent energy model on a 2D lattice of size $S \times D$, whose hamiltonian
+Given that simulating a CA with a deep computational layer on the Ising model requires many spins, making large-scale numerical simulations impractical, we opted to introduce a similar but simpler energy model to observe the behavior on a larger scale.
+Let us define a simpler but ``equivalent'' energy model on a 2D lattice of size $S \times D$, whose hamiltonian
 is given by
@@
 \end{equation}
-
-where $n_{i, t} \in \{0, 1\}$ is the state of the cell at row $i$ and column $t$, the boundary is periodic in the space direction, i.e. $n_{0, t} = n_{S, t}$.
-Its ground state with energy $0$ also encodes a $110$ CA, where the direction of computation is from the left to right.
-\subsection{Numerical result}
+where $n_{i, t} \in \{0, 1\}$ is the state of the cell at row $i$ and column $t$, the lattice is periodic in the space direction, i.e. $n_{0, t} = n_{S, t}$.
+%$S$ to be the length of the material along the ``Space'' axis, $D$
+%to be the length of the material along the ``Time'' axis. 
+%Its ground state with energy $0$ also encodes a $110$ CA, where the direction of computation is from the left to right.
 
@@
 \ym{Great, i will do this}
-Here we conducted numerical experiments to examine both the time complexity along the ``Space'' direction and the ``Time'' direction.
-We use binary search to determine the speed of the slowly moving heat bath at which
-the simulated annealing procedure would produce 
-a ground state configuration with $50\%$ probability. Denote this speed 
-as $v$, the simulated annealing procedure will then take $\frac{D}{v}$
-stages to complete the computation, each stage we try to flip a spin with 
-probability define in (\ref{eq:non-equilibrium-SA}). We name $\frac{D}{v}$ 
-as Sweep Time.
+
+Here we conducted numerical experiments to examine how the cooling time scales with (i)
+the ``Space'' dimension $S$, (ii) the ``Time'' dimension $D$, (iii) the ``Width'' of the heat zone $W$, and (iv) the temperature gradient $\Lambda$.
+We use the number of SA sweeps as the metric to measure the cooling time, which could be determined with the binary search.
+We keep changing the heat bath moving speed $v$ (in unit of columns/sweep) until the system can reach a ground state configuration with $\sim 50\%$ probability.
+Let us denote this speed as $v_c$, then the cooling time can be denoted as $\frac{D}{v_c}$.
 
@@
     \includegraphics[width=\columnwidth,keepaspectratio]{../notes/images/MainNumericalResult.png}
-    \caption{Numerical Result}
+    \caption{Numerical Result\jinguo{images should use the pdf format, the font size should be larger.
+Is it possible to verify that the Ising model is similar to the toy model?
+What is $T$ in the xlabel?}}
     \label{fig:main-numerical-result}
@@
 
-[Fig. \ref{fig:main-numerical-result}(a)] shows the relationship between
+\jinguo{you need to explain the results... what can we learn from the results?}
+\jinguo{bad variable name: Sweep Time}
+\Cref{fig:main-numerical-result} (a) shows the relationship between
 $\ln(\ln(D))$ and $\ln(\frac{\text{Sweep Time}}{D})$ shoule be linear, which implies 

### 2024-09-10 paper/main.tex
modify main figure, rewrited partD, still some work need to do

@@
     % \node at (358.3, 306) [anchor=north] {$Time$};
-    \draw (358.3,320) node [anchor=north][inner sep=0.75pt]   [align=left] {${Time}$};
+    % \draw (358.3,320) node [anchor=north][inner sep=0.75pt]   [align=left] {${Time}$};
     % \node at (252, 175.7) [anchor=east] {$Space$};
-    \draw (215,175.7) node [anchor=west][inner sep=0.75pt]   [align=left] {${Space}$};
+    % \draw (215,175.7) node [anchor=west][inner sep=0.75pt]   [align=left] {${Space}$};
     %Rounded Rect [id:dp5816101232993451] 
@@
     % Text Node
-    %\draw (220.87,45.67) node [anchor=north west][inner sep=3pt]   [align=left] {\large {$\displaystyle \mathtt{(a)}$}};
-    % Text Node
-    %\draw (490.67,121.47) node [anchor=north west][inner sep=3pt]   [align=left] {\large {$\displaystyle \mathtt{(b)}$}};
-    % Text Node
     \draw (492.00,150.41) node [anchor=north west][inner sep=0.75pt]   [align=left] {{\tiny {$p$}}};
@@
     % Text Node
-    \draw (306.20,298.47) node [anchor=north west][inner sep=0.75pt]   [align=left] {$\displaystyle Width$};
+    \draw (317.20,298.47) node [anchor=north west][inner sep=0.75pt]   [align=left] {$W$};
+    % Text Node
+    \draw (448.3,323) node [anchor=north][inner sep=0.75pt]   [align=left] {${M}$};
+    \draw (448.3, 320) -- (448.3, 315);
+    \draw (406.8,323) node [anchor=north][inner sep=0.75pt]   [align=left] {${M-1}$};
+    \draw (408.3, 320) -- (408.3, 315);
+
+    \draw (375.3,327) node [anchor=north][inner sep=0.75pt]   [align=left] {${\cdots}$};
+
+    \draw (354.3,323) node [anchor=north][inner sep=0.75pt]   [align=left] {${3}$};
+    \draw (354.3, 320) -- (354.3, 315);
+    \draw (314.3,323) node [anchor=north][inner sep=0.75pt]   [align=left] {${2}$};
+    \draw (314.3, 320) -- (314.3, 315);
+    \draw (274.3,323) node [anchor=north][inner sep=0.75pt]   [align=left] {${1}$};
+    \draw (274.3, 320) -- (274.3, 315);
+
+    % \node at (252, 175.7) [anchor=east] {$Space$};
+    \draw (240,83.7) node [anchor=west][inner sep=0.75pt]   [align=left] {${N}$};
+    \draw (253,83.7) -- (258, 83.7);
+    \draw (220,113.7) node [anchor=west][inner sep=0.75pt]   [align=left] {${N-1}$};
+    \draw (253,113.7) -- (258, 113.7);
+    \draw (220,143.7) node [anchor=west][inner sep=0.75pt]   [align=left] {${N-2}$};
+    \draw (253,143.7) -- (258, 143.7);
+    \draw (220,173.7) node [anchor=west][inner sep=0.75pt]   [align=left] {${N-3}$};
+    \draw (253,173.7) -- (258, 173.7);
+
+    \draw (245,194.7) node [anchor=north][inner sep=0.75pt]   [align=left] {${\vdots}$};
+
+    \draw (240,243.7) node [anchor=west][inner sep=0.75pt]   [align=left] {${2}$};
+    \draw (253,243.7) -- (258, 243.7);
+    \draw (240,273.7) node [anchor=west][inner sep=0.75pt]   [align=left] {${1}$};
+    \draw (253,273.7) -- (258, 273.7);
 
@@
     The TC has a translational invariant structure, and each unit cell (inset) is a $110$ rule cellular automata gadget that consists of 5 mutually correlated spins (white circles).
-    \jinguo{please add symbols for space, time and width}}
+    % \jinguo{please add symbols for space, time and width}
+    \ym{I add symbols. please check if i still need to put original captions here}
+    }
+
     \label{Surface-programmable-thermodynamic computer}
@@
 
-\subsection{Simulated Annealing}
+\subsection{Simulated Annealing}\label{simulated-annealing-algorithm}
 
@@
 
-\subsection{Cooling computation with a moving heat bath}\label{cooling-computation-with-moving-heat-bath}
+\subsection{Cooling computation with an idealized heat bath}\label{cooling-computation-with-moving-heat-bath}
 
@@
 
-The computational process of the CA is divided into three steps: determining the state of each input cell, iteratively applying the transition rules to generate the next generation of cells, and identifying a certain generation of cells as the output.
-In fact, the width of the time axis in the Ising TC corresponds to the number of iterations.
-Hence, the smallest layer of spins on the time axis should be the input layer, and the largest layer of spins should be the output layer.
-
-Given that each ground state of the TC corresponds to a valid computational process of the CA for a given input, the computational process of the TC is essentially reduced to finding the ground state of the TC with the spin configuration in the input layers fixed.
-
-We focus here on the thermodynamics-driven approach to finding ground states, specifically the heating-annealing method.
-This involves gradually increasing and then decreasing the temperature of the heat bath with which the TC interacts.
-The TC may employ heat fluctuations to explore a state space in the first stage and stabilize on ground state during the second stage as long as the annealing stage is long enough.
-However, it is convinced that this stage can last for exponential time for some hard spin-glass problems.
-
-Due to the structure of the TC, we can allow only a portion of the system, rather than the entire system, to interact with the heat bath, while ignoring the interaction energy between the boundary spins and the exterior.
-After completing the heating-annealing procedure on one part of the system, we move the heat bath to another part and repeat the same process.
-This approach effectively finds a local ground state for each part of the system, which is reasonable when the global ground state can be divided into multiple local components.
-
-More specifically, the computation, progressing from the input layer to the output layer, involves the following steps: (1) Initialize the input layer configuration by adjusting the onsite energy for each spin.
-(2) Determine the number of layers $W$ that will interact with the external heat bath in each heating-annealing process.
-Group the layers in sets of $W$ from input to output, labeling them as groups $1, 2, \cdots, \frac{D}{W}$.
-The number of heating-annealing repetitions will then be $\frac{D}{W}$, where D is the total number of layers.
-(3) Perform the heating-annealing process on each group sequentially.
-
+The computational process of the TC is equivalent to finding the ground state of the TC with the spin configuration in the left surface being fixed.
+
+We focus here on the thermodynamics-driven approach to finding ground states, 
+specifically the simulated annealing method. This can be seen as the TC interacting with a heat bath, 
+as shown in \ref{simulated-annealing-algorithm}, by gradually decreasing the temperature
+of the heat bath the TC can be driven to the ground state if the temperature is decreased slowly enough.
+However, the cooling process can last for exponential time for some hard spin-glass problems.
+
+We modify the classical simulated annealing (SA) algorithm by introducing a heat zone of width  W , which represents the region of the system that interacts with the heat bath.
+To find the ground state of the system, we devided the system into $\lceil\frac{T}{W}\rceil$ parts
+where part $i$ consists of the spins in the region $[iW, (i+1)W]$.
 However, solving the ground state from the non-deterministic direction is at least as hard as solving the circuit satisfiability problem, which is NP-complete~\cite{Moore2011}.

### 2024-09-10 paper/main.tex
update

@@
     \ym{I add symbols. please check if i still need to put original captions here}
+    \jinguo{please make the circles and texts in the inset larger}
     }
@@
 which is consistent with our theoretical prediction in (\ref{eq:total-annealing-time}).
+
+\jinguo{I hope we can also present some results for the random fluctuation model.
+We just need some quantitative result about how the computing time scales with the depth.
+}
+
 % \begin{figure}[h]

### 2024-09-11 paper/main.tex
update. 2 experiments still need to be conducted

@@
 
-\ym{
-    The material was orderly grown by slowly moving the temperature gradient in-plane~\cite{Zhang2014}. Tested thermal gradient force for grain boundary migration~\cite{Bai2015}.
-}
+In the following article, denote one sweep as the process of trying to flip each spin at its local temperature.
+
+% \ym{
+%     The material was orderly grown by slowly moving the temperature gradient in-plane~\cite{Zhang2014}. Tested thermal gradient force for grain boundary migration~\cite{Bai2015}.
+% }
 We test the hypothesis: Cooling is easy if the process is from the
@@
 }
+\ym{
+    I tried. Please check if it is clear and if i still need to cut some details off.
+}
 
@@
 We focus here on the thermodynamics-driven approach to finding ground states, 
-specifically the simulated annealing method. This can be seen as the TC interacting with a heat bath, 
-as shown in \ref{simulated-annealing-algorithm}, by gradually decreasing the temperature
+specifically the simulated annealing (SA) method. Traditional SA method can be seen as the whole system interacting with a heat bath, by gradually decreasing the temperature
 of the heat bath the TC can be driven to the ground state if the temperature is decreased slowly enough.
@@
 
-We modify the classical simulated annealing (SA) algorithm by introducing a heat zone of width  W , which represents the region of the system that interacts with the heat bath.
-To find the ground state of the system, we devided the system into $\lceil\frac{T}{W}\rceil$ parts
-where part $i$ consists of the spins in the region $[iW, (i+1)W]$.
-However, solving the ground state from the non-deterministic direction is at least as hard as solving the circuit satisfiability problem, which is NP-complete~\cite{Moore2011}.
-
-% \subsection{Cooling computation with direction}\label{sec:direction}
-
-% Definitions: * \emph{in-surface/out-suface}: The surface of a surface
-% programmable material that associated with the input/output of the logic
-% circuit.
-
-% The process of heating and annealing the entire material does not have computational capability, as the system lacks logical directionality.
-
-% Logical directionality needs to be introduced through an orderly annealing method. 
-% Similar to the localized heating-annealing approach that catalyzes the growth of ordered crystals, we introduced a temperature gradient annealing scheme.
-
-% More specifically, the computation, with computing direction from in-surface to out-surface, contains the following steps: (1). Initialize the in-surface configuration. By removing
-% some atoms on the in-surface. (2). Connect the in-surface/out-surface to
-% external heat sources at temperature $T_1 < T_2$, respectively. We
-% also require that the energy gap between the ground state and the first
-% excited state of the Hamiltonian to be $\Delta E< T_1$. (3). Lower the
-% temperature of the heat sources ``slowly'' to cool the system to the
-% ground state of the Hamiltonian. The temperature of the heat sources at
-% time $t$ is $T_{1/2}(t) = T_{1/2}(0)\lambda^{-c t}$, where
-% $T_{1/2}(0)$ is the initial temperature of the heat sources, and
-% $\alpha$ is a constant.
-
-% The computing direction could be reversed by swaping the temperature of the heat sources connected in-surface and out-surface.
+We introduce a heat zone of width $W$, which represents the region of the system that interacts with the heat bath, as shown in \Cref{Surface-programmable-thermodynamic computer}.
+Let layer $i$ be defined as the set of spins with x-coordinate $i$.
+The system is devided into $\lceil\frac{M}{W}\rceil$ parts,
+where part $j$ consists of layers in the range $[jW, (j+1)W-1]$.
+The system can then be cooled by sequentially cooling each parts with an idealized heat bath, 
+which maintains a space-invariant temperature within the heat zone while keeping other regions at zero temperature.
+To drive the system toward the ground state, the cooling order should proceed from left to right
+, corresponding to the computation direction of the cellular automata.
+
+Assume the annealing procedure in each part has an error probability $\epsilon$ that prevents at least one layer
+from reaching the local ground state. 
+Repeating the procedure $\frac{M}{W}$ times results in a success probability of $(1 - \epsilon)^{\frac{M}{W}}$ for finding the global ground state. 
+To keep this probability constant as $M \to \infty$, the error probability $\epsilon$ should scale as $\frac{W}{M}$.
+
+Now we turn to determining the sweep time $t_{th}$ required to achieve an error probability $\epsilon$ in each part. 
+Let $\lambda_1$ and $\lambda_2$ be the largest and second largest eigenvalues of the Markov transition matrix, respectively. 
+The relationship between $\frac{\lambda_2}{\lambda_1}$ and $W$ can be expressed as
+\begin{equation}
+    \label{eq:spectral-gap}
+    1 - \frac{\lambda_2}{\lambda_1} \sim e^{-W}
+\end{equation}
+
+Consequently, a relationship exists between $t_{th}$ and $\epsilon$, which is given by:
+
+\begin{equation}
+    \left( \frac{\lambda_2}{\lambda_1} \right) ^ {t_{th}} = \epsilon \rightarrow t_{th} \sim \ln(\frac{M}{W})e^{W}
+\end{equation}
+
+And the total sweep time scale as $\frac{M}{W}\ln(\frac{M}{W})e^W$.
+
 % However, solving the ground state from the non-deterministic direction is at least as hard as solving the circuit satisfiability problem, which is NP-complete~\cite{Moore2011}.
 
-In our gadget, cooling from deterministic direction is from input to
-output, non-deterministic direction is from output to input. The latter
-one must be non-deterministic because this gadget is Turing-Complete.
-
-The goal is to drive the the \textbf{state} to the one with lowest energy as fast as possible, while some bits set to be 1 or 0 in the \textbf{state}.
-
-\subsubsection{Estimation of the computing time along computation direction}\label{estimation-of-the-computing-time}
-
-Let us initially treat the heat bath as ideal, assuming that the temperature within the interacting region of the system is uniform and that the temperature outside this region is zero.
-We refer to the interacting region as the ``Heat Zone''.
-
-Assume there is an annealing procedure that may prevent the layers in the Heat Zone from stabilizing in the local ground state, or equivalently, that an error occurs in the computation process with a probability $\epsilon$.
-Repeating this procedure $\frac{D}{W}$ times would result in a probability of $(1-\epsilon)^{\frac{D}{W}}$ to successfully find the proper global ground state.
-To maintain a constant success probability as $D \rightarrow +\infty$, the error probability $\epsilon$ should scale as $\frac{W}{D}$.
-
-Now we turn to determining the annealing time $t_{th}$ required to achieve an error probability $\epsilon$ in each Heat Zone.
-Let $\lambda_1$ and $\lambda_2$ be the largest and second largest eigenvalues of the Markov transition matrix, respectively.
-The relationship between $\frac{\lambda_2}{\lambda_1}$ and $W$ can be expressed as $1 - \frac{\lambda_2}{\lambda_1} \sim e^{-W}$.
-Consequently, a relationship exists between $t_{th}$ and $\epsilon$, which is given by:
-
-\begin{equation}
-    \left( \frac{\lambda_2}{\lambda_1} \right) ^ {t_{th}} = \epsilon \rightarrow t_{th} \sim \ln(\frac{D}{W})e^{W}
-\end{equation}
-
-And the total annealing time scale as $\frac{D}{W}\ln(\frac{D}{W})e^W$.
+% In our gadget, cooling from deterministic direction is from input to
+% output, non-deterministic direction is from output to input. The latter
+% one must be non-deterministic because this gadget is Turing-Complete.
+
+% The goal is to drive the the \textbf{state} to the one with lowest energy as fast as possible, while some bits set to be 1 or 0 in the \textbf{state}.
+
+\subsection{Cooling computation with a realistic heat bath}\label{estimation-of-the-computing-time}
 
@@
 
-Now suppose the heat bath only connects to a small rectangle region of the system,
-covers the region encompassing all time coordinates between $[middle(t)-\frac{\Delta_L}{2}, middle(t)+\frac{\Delta_L}{2}]$, where $\Delta_L$ is a small constant.
-The heat radiation is conducted to other regions, thereby inducing a temperature gradient,
-which can be modeled as $T(x) \propto \Lambda^{-|x - middle(t)|}$, where $T(x)$ is the temperature at the region with a time coordinate $x$, and $\Lambda$ is a constant.
-
-The block annealing process then can be reconstruct as slowly moving
-the middle of the heat bath from one end to the other. Defining $\Delta E_{max}$ to be the
+Now suppose the heat bath only connects to a small rectangle region of the system, creating a temperature gradient through heat flux,
+The temperature $T(x, t)$  at a position with x-coordinate  $x$  and time  $t$  can be modeled as  $T(x, t) \propto \Lambda^{-|x - L(t)|}$ , 
+where $\Lambda$ is a heat flux constant and $L(t)$ denotes the center of the heat bath at time $t$.
+
+The block annealing process then can be reconstruct as moving
+the heat bath from the left surface to the right surface at speed $v$. Defining $\Delta E_{max}$ to be the
 largest possible energy change when a spin is fliped.
-The effective heat zone should then be $[y-W, y]$, where position $y$ satisfying 
-$\exp(\frac{\Delta E_{max}}{T(y)}) = 0.1$ and $y<middle(t)$. Since the layers
+The effective heat zone with width $W'$ should then be $[y-W', y]$, where position $y$ satisfying 
+$\exp(\frac{\Delta E_{max}}{T(y)}) = 0.1$ and $y<L(t)$. Since the layers
 in fronts of the effective heat zone can only be fliped with a $\epsilon$ probability if the local energy would increase. 
-The effective width $W$ then should scale as $\exp(-\Delta E_{max} \Lambda^{cW}) \sim \epsilon \sim \frac{W}{D}$, where $c$ is the empirical constant for effective width and can be determined during the experiment.
-
-The total annealing time can be calculated as
+The effective width $W'$ then should scale as $\exp(-\Delta E_{max} \Lambda^{cW'}) \sim \epsilon \sim \frac{W'}{M}$, where $c$ is an empirical constant for effective width and can be determined during the experiment.
+\ym{I am not sure about how to give a concrete definition of the effective width $W'$.}
+
+The total sweep time with a fixed inputs size $N$ can be calculated as
 
@@
     \label{eq:total-annealing-time}
-    t_{total} = \frac{D}{W}(\ln(\frac{D}{W}))^{1+ \frac{1}{c\ln(\Lambda)}}
-\end{equation}
-
-\subsubsection{Estimation of the computing time along input memory direction}\label{Estimation-of-the-computing-time-along-input-memory-direction}
-
-We fixed the number of layers and denote $S$ as the width of each layer in this material.
-
-However, we fail to derive an explicitly expression for the time complexity in this direction. 
-Numerical result shows that computing complexity is linear to $S$. Thus a total time
-for the computation should scale as $DS\log^{1 + \frac{1}{c\ln(\Lambda)}}(D)$
+    t_{total} \propto \frac{M}{W'}(\ln(\frac{M}{W'}))^{1+ \frac{1}{c\ln(\Lambda)}}
+\end{equation}
+
+To determine the relationship between the total annealing time and the input size $N$, we should
+further discuss the relationship between the spectral gap given in  \Cref{eq:spectral-gap} and inputs size $N$.
+However, we failed to find a direct relationship.
+Numerical result shows that computing complexity is linear to $N$. Thus a total sweep time
+for the computation should scale as $NM\log^{1 + \frac{1}{c\ln(\Lambda)}}(M)$.
+\ym{Please help me to think about how to evaluate the time complexity while $N$ increases.} 
+The moving speed $v$ can be then calculated as
+
+\begin{equation}
+    \label{eq:moving-speed}
+    v \propto \frac{t_{total}}{M} = N\log^{1 + \frac{1}{c\ln(\Lambda)}}(M)
+\end{equation}
 
@@
 heat-equilibrium, the probability reverts to the classical HeatBath
-acceptance probability. We also provided a more general proof by constructing another equivalent model in Appendix \ref{proof-of_non-equilibrium-SA}.
+acceptance probability. We also provided a more general proof by constructing another equivalent model in \Cref{proof-of_non-equilibrium-SA}.
 
@@
 Given that simulating a CA with a deep computational layer on the Ising model requires many spins, making large-scale numerical simulations impractical, we opted to introduce a similar but simpler energy model to observe the behavior on a larger scale.
-Let us define a simpler but ``equivalent'' energy model on a 2D lattice of size $S \times D$, whose hamiltonian
+Let us define a simpler but ``equivalent'' energy model on a 2D lattice of size $N \times M$, whose hamiltonian
 is given by
 \begin{equation}\label{eq:toy-hamiltonian}
-E(\vn) = \sum_{t=1}^{D-1}\sum_{i=1}^{S} (n_{i+1, t} \land \neg(n_{i, t} \land \neg n_{i-1, t})) \veebar n_{i,t+1},
-\end{equation}
-where $n_{i, t} \in \{0, 1\}$ is the state of the cell at row $i$ and column $t$, the lattice is periodic in the space direction, i.e. $n_{0, t} = n_{S, t}$.
+E(\vn) = \sum_{j=1}^{M-1}\sum_{i=1}^{N} (n_{i+1, j} \land \neg(n_{i, j} \land \neg n_{i-1, j})) \veebar n_{i,j+1},
+\end{equation}
+where $n_{i, j} \in \{0, 1\}$ is the state of the cell at row $i$ and column $j$, the lattice is periodic in the space direction, i.e. $n_{0, t} = n_{N, j}$.
 %$S$ to be the length of the material along the ``Space'' axis, $D$
@@
 
-\jinguo{show a comparison from right to left}\jinguo{I have already used D as the dimension}
-\ym{Great, i will do this}
-
-Here we conducted numerical experiments to examine how the cooling time scales with (i)
-the ``Space'' dimension $S$, (ii) the ``Time'' dimension $D$, (iii) the ``Width'' of the heat zone $W$, and (iv) the temperature gradient $\Lambda$.
+\jinguo{show a comparison from right to left}
+\ym{I will do this in the next version.}
+
+Here we conducted numerical experiments to examine how the cooling time $T_{c}$ scales with (i)
+the ``Space'' dimension $N$, (ii) the ``Time'' dimension $M$, (iii) the ``Width'' of the heat zone $W$, and (iv) the temperature gradient $\Lambda$.
 We use the number of SA sweeps as the metric to measure the cooling time, which could be determined with the binary search.
 We keep changing the heat bath moving speed $v$ (in unit of columns/sweep) until the system can reach a ground state configuration with $\sim 50\%$ probability.
-Let us denote this speed as $v_c$, then the cooling time can be denoted as $\frac{D}{v_c}$.
-
-\begin{figure}[h]
+
+\begin{figure}[]
     \centering
-    \includegraphics[width=\columnwidth,keepaspectratio]{../notes/images/MainNumericalResult.png}
-    \caption{Numerical Result\jinguo{images should use the pdf format, the font size should be larger.
-Is it possible to verify that the Ising model is similar to the toy model?
-What is $T$ in the xlabel?}}
+    \includegraphics[width=\columnwidth,keepaspectratio]{../notes/images/main_result.pdf}
+    \caption{Numerical Result
+    \jinguo{images should use the pdf format, the font size should be larger. Is it possible to verify that the Ising model is similar to the toy model? What is $T$ in the xlabel?}
+    \ym{I changed the labels. Maybe i need to conduct another numerical experiment
+    to verify the similarity between the Ising model and the toy model.}
+    }
     \label{fig:main-numerical-result}
@@
 \jinguo{bad variable name: Sweep Time}
-\Cref{fig:main-numerical-result} (a) shows the relationship between
-$\ln(\ln(D))$ and $\ln(\frac{\text{Sweep Time}}{D})$ shoule be linear, which implies 
-the time complexity along the ``Time'' direction should scale as $D\ln(D)^{f(\Lambda)}$. 
+\Cref{fig:main-numerical-result}(a) shows the relationship between
+$\ln(\ln(M))$ and $\ln(v)$ shoule be linear, which implies 
+the time complexity $T_c$ along the ``Time'' direction should scale as $M\ln(M)^{f(\Lambda)}$. 
 We then fit the slopes of each line and $\frac{1}{\ln(\Lambda)}$ and find the 
-empirical constant $c$ in (\ref{eq:total-annealing-time}) to be $3$. [Fig. \ref{fig:main-numerical-result}(b)] shows 
-the the relationship between Sweep Time and $S$ should be linear. Combining these two results, 
-we can conclude that the time complexity should scales as $DS\log(D)^{1+\frac{1}{3\ln(\Lambda)}}$, 
-which is consistent with our theoretical prediction in (\ref{eq:total-annealing-time}).
+empirical constant $c$ in \Cref{eq:total-annealing-time} to be $3$. \Cref{fig:main-numerical-result}(b) shows 
+the the relationship between $T_c$ and $M$ should be linear. Combining these two results, 
+we can conclude that the time complexity should scales as $NM\log(M)^{1+\frac{1}{3\ln(\Lambda)}}$, 
+which is consistent with our theoretical prediction in \Cref{eq:total-annealing-time}.
 
@@
 }
+\ym{This experiment can be conducted together with the verification of the similarity between the Ising model and the toy model.}
 
@@
 
-To examine whether this model could achieve a better performance when
-using adiabatic methods, we need to generalize this energy function to
-some good hamiltonian. There has already been work on mapping
-combinatorial optimization problems to a spin-glass model (known as the
-Ising Machine) and leveraging the properties of digital devices that
-simulate this Ising Machine to find an appropriate ground state, which
-encodes computational information~\cite{Aadit2022,Bybee2023}.
+% To examine whether this model could achieve a better performance when
+% using adiabatic methods, we need to generalize this energy function to
+% some good hamiltonian. There has already been work on mapping
+% combinatorial optimization problems to a spin-glass model (known as the
+% Ising Machine) and leveraging the properties of digital devices that
+% simulate this Ising Machine to find an appropriate ground state, which
+% encodes computational information~\cite{Aadit2022,Bybee2023}.
 
@@
 We conducted numerical experiments to verify this equivalence under the condition
-that $\Lambda = 1.3$ and $n=15$. The result is shown in [Fig. \ref{EGvsMHB}].
+that $\Lambda = 1.3$ and $n=15$. The result is shown in \Cref{EGvsMHB}.
 \begin{figure}[h]
     \centering
-    \includegraphics[width=\columnwidth,keepaspectratio]{../notes/images/EGvsMHB.png}
+    \includegraphics[width=\columnwidth,keepaspectratio]{../notes/images/EGvsMHB.pdf}
     \caption{Running time v.s Depth of the material}

### 2024-09-12 paper/main.tex
updat

@@
 
-\begin{equation}
+\begin{equation}\label{eq:ising}
 E(\vs) = \sum_{i < j} J_{ij}s_us_v + \sum_{i=1}^{n}h_i s_i
@@
 
-\subsection{Simulated Annealing}\label{simulated-annealing-algorithm}
+To set the inputs, we raise or lower the energy of spins on the left surface.
+To set a spin to $s_i=-1/1$, we raise/lower the external field $h_i$ by $\Delta_{in}>0$.
+By setting all the spins on the left surface, the ground state of the TC has no degeneracy, and the output is encoded in the spins on the right surface.
+One can also set the outputs by raising or lowering the energy of spins on the right surface. Due to the lack of reversibility, the ground state may still have degeneracy.
+Each ground states corresponds to a solution to the encoded circuit satisfaction problem if the target circuit is satisfiable.
+We denote the computation from the left to the right as the \emph{deterministic computation}, and the computation from the right to the left as the \emph{non-deterministic computation}.
+
+\subsection{Compute by annealing}\label{simulated-annealing-algorithm}
 
 With the proposed Ising model, we are interested in how efficiently we can drive the system to the ground state, which encodes the output of the CA.
-Since the natural cooling process is highly nontrivial to model, we consider a theoretical model for cooling, which is simulated annealing (SA)~\cite{Kirkpatrick1983}.
-\jinguo{random fluctuations may be linear in time considering the parallelism of the system.}
-It is known that when the system and heat bath are at thermal equilibrium, 
-the probability of a spin configuration $\mathbf{s}$ is given by the Boltzmann distribution:
-\begin{equation}
-    p(\mathbf{s}) = \frac{1}{Z}\exp\left(- \frac{E({\mathbf{s}})}{k_bT}\right),
-\end{equation}
-where $Z = \sum_{\mathbf{s}} \exp\left(-\frac{E({\mathbf{s}})}{k_bT}\right)$ is the partition function, 
-$E({\mathbf{s}})$ is the energy of the each of $2^n$ spin configuration, labeled by $\mathbf{s} = (s_1, s_2, \cdots, s_n)$, $k_b$ is the Boltzmann constant, and $T$ is the temperature of the heat bath.
-In the following, we set $k_b = 1$.
-
-We employ the Metropolis-Hastings algorithm~\cite{metropolis1953equation} to characterize the thermodynamic process of the TC system as modulated by the heat bath.
-This algorithm perform a random walk in the state space of the TC, each step we try to flip a spin,
-and the probability of accepting a move from state $\mathbf{s}$ to $\mathbf{s}^\prime$ is given by:
-\begin{equation}
-    P_{\text{accept}} = \frac{1}{1+\exp\left(\frac{E({\mathbf{s}^\prime}) - E({\mathbf{s}})}{T}\right)}.
-\end{equation}
-This accepting probability follows from the Glauber dynamics~\cite{glauber1963time}.
-It can be shown that this process is Markovian and ergodic, and the system will eventually reach the thermal equilibrium.
-To determine the speed of the convergence, we should notice the spectral gap of the transition matrix of the Markov chain, which is defined as
-
-\begin{equation}
-    \Delta = 1 - \frac{\lambda_2}{\lambda_1}
-\end{equation}
-
-where $\lambda_1$ and $\lambda_2$ are the largest and second largest eigenvalues of the transition matrix, respectively.
-In order to sample from the distribution $\epsilon$ close to the equilibrilium distribution, the number of steps required is $O(\log_{1-\Delta} \epsilon)$.
-
-In the following article, denote one sweep as the process of trying to flip each spin at its local temperature.
+In contrast with a traditional computation model, cooling an energy model does not have a specific direction.
+It can be done from the input to the output, from the output to the input or neither.
+Intuitively, cooling the deterministic computation is much easier than cooling the non-deterministic computation.
+Since the latter encodes the circuit satisfaction problem, which is NP-hard, while the former is a simple linear-time computation.
+However, this is not always the case.
+Global cooling by gradually lowering the temperature (or annealing), as in the Ising machine~\cite{fabre2014optical}, may still hard for a deterministic computation, no matter how large the input detuning $\Delta_{in}$ is.
+
+%In the following article, denote one sweep as the process of trying to flip each spin at its local temperature.
 
@@
 % }
-We test the hypothesis: Cooling is easy if the process is from the
-deterministic direction, hard if the process is from the
-non-deterministic direction.
-
+%We test the hypothesis: Cooling is easy if the process is from the
+%deterministic direction, hard if the process is from the
+%non-deterministic direction.
 \begin{hyp}
@@
 \end{hyp}
-\jinguo{Leave this issue to Maddie}
+\jinguo{Confirm with Maddie}
 The overlap gap property is a property for describing the algorithmic intractability in random structures, which is based on the topological disconnectivity property of the set of pair-wise distances of near optimal solutions.
@@
 We left the rigorous proof of this hypothesis to mathematicians.
+
+\subsubsection{Simulated annealing algorithm}
+Since the natural cooling process is highly nontrivial to model, we consider a theoretical model for cooling, which is the simulated annealing (SA)~\cite{Kirkpatrick1983}.
+When the energy model in \Cref{eq:ising} thermalizes at temperature $T$, the spin configuration $\vs = (s_1, s_2, \cdots, s_n)$ follows the Boltzmann distribution:
+\begin{equation}
+    p(\vs) = \frac{1}{Z}\exp\left(- \frac{E({\vs})}{k_bT}\right),
+\end{equation}
+where $Z = \sum_{\vs} \exp\left(-\frac{E({\vs})}{k_bT}\right)$ is the partition function, 
+$E({\vs})$ is the energy of the spin configuration $\vs$, and $k_b$ is the Boltzmann constant, which is set $k_b = 1$ in this work.
+%We employ the Metropolis-Hastings algorithm~\cite{metropolis1953equation} to characterize the thermodynamic process of the TC system as modulated by the heat bath.
+SA is a Monte Carlo method~\cite{metropolis1953equation} that simulates the thermal annealing process.
+It performs a random walk in the state space of the TC, each step we try to flip a spin according to some unbiased prior distribution,
+and the probability of accepting a move from state $\vs$ to $\vs^\prime$ is given by:
+\begin{equation}
+    P_{\vs^\prime\leftarrow \vs} = \frac{1}{1+\exp\left(\frac{E({\vs^\prime}) - E({\vs})}{T}\right)}.
+\end{equation}
+This accepting probability follows from the Glauber dynamics~\cite{glauber1963time}.
+It can be shown that this process is Markovian and ergodic, and the system will eventually reach the thermal equilibrium.
+The speed of the convergence is determined by the spectral gap of the transition matrix of the Markov chain, which is defined as
+\begin{equation}
+    \Delta = 1 - \frac{\lambda_2}{\lambda_1},
+\end{equation}
+where $\lambda_1$ and $\lambda_2$ are the largest and second-largest eigenvalues of the transition matrix, respectively.
+In order to sample from the distribution $\epsilon$ close to the equilibrium distribution, the number of steps required is $O(\log_{1-\Delta} \epsilon)$, i.e.
+the distribution quality improves exponentially with the number of sampling steps.
 

### 2024-09-12 paper/main.tex
updat

@@
 Global cooling by gradually lowering the temperature (or annealing), as in the Ising machine~\cite{fabre2014optical}, may still hard for a deterministic computation, no matter how large the input detuning $\Delta_{in}$ is.
+It can be rigorous proved that the cooling process is hard if the energy landscape of the optimization problem exhibits the overlap gap property~\cite{Gamarnik2021}.
+If a problem has the overlap gap property, then it can not be solved by any local algorithms in time polynomial to the system size, including both the physical annealing and the simulated annealing method used in this work.
 
@@
 
-\subsubsection{Simulated annealing algorithm}
-Since the natural cooling process is highly nontrivial to model, we consider a theoretical model for cooling, which is the simulated annealing (SA)~\cite{Kirkpatrick1983}.
-When the energy model in \Cref{eq:ising} thermalizes at temperature $T$, the spin configuration $\vs = (s_1, s_2, \cdots, s_n)$ follows the Boltzmann distribution:
-\begin{equation}
-    p(\vs) = \frac{1}{Z}\exp\left(- \frac{E({\vs})}{k_bT}\right),
-\end{equation}
-where $Z = \sum_{\vs} \exp\left(-\frac{E({\vs})}{k_bT}\right)$ is the partition function, 
-$E({\vs})$ is the energy of the spin configuration $\vs$, and $k_b$ is the Boltzmann constant, which is set $k_b = 1$ in this work.
-%We employ the Metropolis-Hastings algorithm~\cite{metropolis1953equation} to characterize the thermodynamic process of the TC system as modulated by the heat bath.
-SA is a Monte Carlo method~\cite{metropolis1953equation} that simulates the thermal annealing process.
-It performs a random walk in the state space of the TC, each step we try to flip a spin according to some unbiased prior distribution,
-and the probability of accepting a move from state $\vs$ to $\vs^\prime$ is given by:
-\begin{equation}
-    P_{\vs^\prime\leftarrow \vs} = \frac{1}{1+\exp\left(\frac{E({\vs^\prime}) - E({\vs})}{T}\right)}.
-\end{equation}
-This accepting probability follows from the Glauber dynamics~\cite{glauber1963time}.
-It can be shown that this process is Markovian and ergodic, and the system will eventually reach the thermal equilibrium.
-The speed of the convergence is determined by the spectral gap of the transition matrix of the Markov chain, which is defined as
-\begin{equation}
-    \Delta = 1 - \frac{\lambda_2}{\lambda_1},
-\end{equation}
-where $\lambda_1$ and $\lambda_2$ are the largest and second-largest eigenvalues of the transition matrix, respectively.
-In order to sample from the distribution $\epsilon$ close to the equilibrium distribution, the number of steps required is $O(\log_{1-\Delta} \epsilon)$, i.e.
-the distribution quality improves exponentially with the number of sampling steps.
-
-\subsection{Cooling computation with an idealized heat bath}\label{cooling-computation-with-moving-heat-bath}
+Since there is no standard approach to model the physical annealing process, we consider a theoretical model for cooling, which is the simulated annealing (SA)~\cite{Kirkpatrick1983} algorithm that detailed in \Cref{app:sa}.
+
+\subsection{Dynamic annealing}\label{cooling-computation-with-moving-heat-bath}
+\jinguo{Please shorten this section!}
 
@@
 
-The computational process of the TC is equivalent to finding the ground state of the TC with the spin configuration in the left surface being fixed.
-
-We focus here on the thermodynamics-driven approach to finding ground states, 
-specifically the simulated annealing (SA) method. Traditional SA method can be seen as the whole system interacting with a heat bath, by gradually decreasing the temperature
-of the heat bath the TC can be driven to the ground state if the temperature is decreased slowly enough.
-However, the cooling process can last for exponential time for some hard spin-glass problems.
-
-We introduce a heat zone of width $W$, which represents the region of the system that interacts with the heat bath, as shown in \Cref{Surface-programmable-thermodynamic computer}.
+To overcome the overlap gap property, we propose to cool the system piece by piece, by introducing a heat zone with width $W$.
+It represents the region of the system that interacts with the heat bath, as shown in \Cref{Surface-programmable-thermodynamic computer}.
 Let layer $i$ be defined as the set of spins with x-coordinate $i$.
@@
 Let $\lambda_1$ and $\lambda_2$ be the largest and second largest eigenvalues of the Markov transition matrix, respectively. 
-The relationship between $\frac{\lambda_2}{\lambda_1}$ and $W$ can be expressed as
+We assume the relationship between $\frac{\lambda_2}{\lambda_1}$ and $W$ can be expressed as
 \begin{equation}
     \label{eq:spectral-gap}
-    1 - \frac{\lambda_2}{\lambda_1} \sim e^{-W}
-\end{equation}
-
-Consequently, a relationship exists between $t_{th}$ and $\epsilon$, which is given by:
-
+    1 - \frac{\lambda_2}{\lambda_1} \sim e^{-W}.
+\end{equation}
+Consequently, $t_{th}$ is related to $\epsilon$ by:
 \begin{equation}
-    \left( \frac{\lambda_2}{\lambda_1} \right) ^ {t_{th}} = \epsilon \rightarrow t_{th} \sim \ln(\frac{M}{W})e^{W}
-\end{equation}
-
-And the total sweep time scale as $\frac{M}{W}\ln(\frac{M}{W})e^W$.
+    \left( \frac{\lambda_2}{\lambda_1} \right) ^ {t_{th}} = \epsilon \rightarrow t_{th} \sim \ln(\frac{M}{W})e^{W},
+\end{equation}
+and the total sweep times scale as $\frac{M}{W}\ln(\frac{M}{W})e^W$.
 
@@
 
-\subsection{Cooling computation with a realistic heat bath}\label{estimation-of-the-computing-time}
+\subsubsection{A more realistic heat bath}\label{estimation-of-the-computing-time}
 
@@
 
-\subsubsection{Testing model with non-equilibrium simulated
-annealing}\label{some-details-about-non-equilibrium-simulated-annealing}
+\subsubsection{Testing model with non-equilibrium simulated annealing}\label{some-details-about-non-equilibrium-simulated-annealing}\jinguo{Suggested subtitle: Simulating temperature gradient}
 
@@
 temperature~\cite{Zollner2014}.
-Therefore, based on HeatBath acceptance rule, we made a slight modification to the classical SA model.
+Therefore, based on HeatBath acceptance rule, we made a slight modification to the classical SA model.\jinguo{??? shouldn't it be Glauber dynamics?}
 
@@
 
+\section{Simulated annealing algorithm}\label{app:sa}
+When the energy model in \Cref{eq:ising} thermalizes at temperature $T$, the spin configuration $\vs = (s_1, s_2, \cdots, s_n)$ follows the Boltzmann distribution:
+\begin{equation}
+    p(\vs) = \frac{1}{Z}\exp\left(- \frac{E({\vs})}{k_bT}\right),
+\end{equation}
+where $Z = \sum_{\vs} \exp\left(-\frac{E({\vs})}{k_bT}\right)$ is the partition function, 
+$E({\vs})$ is the energy of the spin configuration $\vs$, and $k_b$ is the Boltzmann constant, which is set $k_b = 1$ in this work.
+
+%We employ the Metropolis-Hastings algorithm~\cite{metropolis1953equation} to characterize the thermodynamic process of the TC system as modulated by the heat bath.
+SA is a Monte Carlo method~\cite{metropolis1953equation} that simulates the thermal annealing process.
+It performs a random walk in the state space of the TC, each step we try to flip a spin according to some unbiased prior distribution,
+and the probability of accepting a move from state $\vs$ to $\vs^\prime$ is given by:
+\begin{equation}
+    P_{\vs^\prime\leftarrow \vs} = \frac{1}{1+\exp\left(\frac{E({\vs^\prime}) - E({\vs})}{T}\right)}.
+\end{equation}
+This accepting probability follows from the Glauber dynamics~\cite{glauber1963time}.
+It can be shown that this process is Markovian and ergodic, and the system will eventually reach the thermal equilibrium.
+The speed of the convergence is determined by the spectral gap of the transition matrix of the Markov chain, which is defined as
+\begin{equation}
+    \Delta = 1 - \frac{\lambda_2}{\lambda_1},
+\end{equation}
+where $\lambda_1$ and $\lambda_2$ are the largest and second-largest eigenvalues of the transition matrix, respectively.
+In order to sample from the distribution $\epsilon$ close to the equilibrium distribution, the number of steps required is $O(\log_{1-\Delta} \epsilon)$, i.e.
+the distribution quality improves exponentially with the number of sampling steps.
+
 \section{Proof of the applicability of non-equilibrium SA}\label{proof-of_non-equilibrium-SA}

### 2024-09-14 paper/main.tex
shorten section D, added main result

@@
 
-\jinguo{
-    Need to introduce the heat zone.
-}
-\ym{
-    I tried. Please check if it is clear and if i still need to cut some details off.
-}
-
-To overcome the overlap gap property, we propose to cool the system piece by piece, by introducing a heat zone with width $W$.
+To overcome the overlap gap property, we propose to do block annealing, by introducing a heat zone with width $W$.
 It represents the region of the system that interacts with the heat bath, as shown in \Cref{Surface-programmable-thermodynamic computer}.
 Let layer $i$ be defined as the set of spins with x-coordinate $i$.
-The system is devided into $\lceil\frac{M}{W}\rceil$ parts,
-where part $j$ consists of layers in the range $[jW, (j+1)W-1]$.
-The system can then be cooled by sequentially cooling each parts with an idealized heat bath, 
-which maintains a space-invariant temperature within the heat zone while keeping other regions at zero temperature.
-To drive the system toward the ground state, the cooling order should proceed from left to right
-, corresponding to the computation direction of the cellular automata.
-
-Assume the annealing procedure in each part has an error probability $\epsilon$ that prevents at least one layer
-from reaching the local ground state. 
-Repeating the procedure $\frac{M}{W}$ times results in a success probability of $(1 - \epsilon)^{\frac{M}{W}}$ for finding the global ground state. 
+The system is devided into $\lceil\frac{M}{W}\rceil$ blocks,
+where block $j$ consists of layers in the range $[(j-1)W+1, jW]$.
+The system can then be cooled by sequentially cooling the blocks from left to right with an heat bath, where the temperature of the heat bath is gradually decreased.
+We treat it as an ideal bath as it maintains a space-invariant temperature within the heat zone while keeping other regions at zero temperature.
+
+Assume the SA procedure in each block has an error probability $\epsilon$.
+Repeating the procedure in $\frac{M}{W}$ blocks results in a success probability of $(1 - \epsilon)^{\frac{M}{W}}$ for finding the global ground state. 
 To keep this probability constant as $M \to \infty$, the error probability $\epsilon$ should scale as $\frac{W}{M}$.
 
-Now we turn to determining the sweep time $t_{th}$ required to achieve an error probability $\epsilon$ in each part. 
+Now we turn to determining the sweep time $t_{th}$ required to achieve $\epsilon$ error in each procedure. 
 Let $\lambda_1$ and $\lambda_2$ be the largest and second largest eigenvalues of the Markov transition matrix, respectively. 
@@
 
-In practice, temperature changes cannot occur instantaneously, and the temperature distribution within the heating zone may not be uniform.
-Thus, we come up with a more realistic model for the block annealing process.
-
-Now suppose the heat bath only connects to a small rectangle region of the system, creating a temperature gradient through heat flux,
+In practice, the heat bath and heat flux should establish a temperature gradient in the system.
+% Suppose the heat bath only connects to a small rectangle region of the system.
 The temperature $T(x, t)$  at a position with x-coordinate  $x$  and time  $t$  can be modeled as  $T(x, t) \propto \Lambda^{-|x - L(t)|}$ , 
@@
 largest possible energy change when a spin is fliped.
-The effective heat zone with width $W'$ should then be $[y-W', y]$, where position $y$ satisfying 
-$\exp(\frac{\Delta E_{max}}{T(y)}) = 0.1$ and $y<L(t)$. Since the layers
-in fronts of the effective heat zone can only be fliped with a $\epsilon$ probability if the local energy would increase. 
-The effective width $W'$ then should scale as $\exp(-\Delta E_{max} \Lambda^{cW'}) \sim \epsilon \sim \frac{W'}{M}$, where $c$ is an empirical constant for effective width and can be determined during the experiment.
+The effective heat zone with width $W'(\Lambda)$ should then be $[y-W'(\Lambda), y]$, where position $y$ satisfying 
+$\exp(\frac{\Delta E_{max}}{T(y)}) = 0.1$ and $y<L(t)$. 
+% Since the layers in fronts of the effective heat zone can only be fliped with a $\epsilon$ probability if the local energy would increase. 
+The effective width $W'$ then should scale as $\exp(-\Delta E_{max} \Lambda^{cW'(\Lambda)}) \sim \epsilon$, where $c$ is an empirical constant and can be determined during the experiment. 
 \ym{I am not sure about how to give a concrete definition of the effective width $W'$.}
 
-The total sweep time with a fixed inputs size $N$ can be calculated as
+The total sweep time with a fixed inputs size $N$ can then be calculated as
 
@@
     \label{eq:total-annealing-time}
-    t_{total} \propto \frac{M}{W'}(\ln(\frac{M}{W'}))^{1+ \frac{1}{c\ln(\Lambda)}}
+    t_{total} \propto \frac{M}{W'(\Lambda)}(\ln(\frac{M}{W'(\Lambda)}))^{1+ \frac{1}{c\ln(\Lambda)}}
 \end{equation}
@@
 
-\subsubsection{Testing model with non-equilibrium simulated annealing}\label{some-details-about-non-equilibrium-simulated-annealing}\jinguo{Suggested subtitle: Simulating temperature gradient}
-
-The classical simulated annealing can only deal with the situation that
-the temperature is space-invariant. However, we need to borden this concept
-due to the temperature gradient. Although there are many ways to
-simulated a real-world system with temperature gradient, such as
-Molecular Dynamics \cite{Bai2015, Deng2006}, but
-these methods mainly depend on dynamically adjusting the atomic
-velocities to achieve a temperature gradient, which can't be directly
-used in our model.
-
-There are also Monte Carlo-based methods to simulate a moving
-temperature wave packet that facilitates material growth~\cite{Godfrey1995, Tan2017}.
-However, these methods fail to establish a direct connection between the simulated temperature and experimental
-temperature~\cite{Zollner2014}.
-Therefore, based on HeatBath acceptance rule, we made a slight modification to the classical SA model.\jinguo{??? shouldn't it be Glauber dynamics?}
-
-When we flip one spin, there would be some energy difference
-$\Delta E_{i}$ in field $i$ with temperature $T_i$. The
-probability to accept this flip would be
-
-\begin{equation}
-    \label{eq:non-equilibrium-SA}
-P = \frac{1}{1 + e^{\sum_i \frac{\Delta E_i}{T_i}}}
-\end{equation}
-
-It is easily to observe that when the system returns to
-heat-equilibrium, the probability reverts to the classical HeatBath
-acceptance probability. We also provided a more general proof by constructing another equivalent model in \Cref{proof-of_non-equilibrium-SA}.
-
 \section{Numerical simulation}\label{sec:numerical-result}
 
+\subsection{Model and Method}
 Given that simulating a CA with a deep computational layer on the Ising model requires many spins, making large-scale numerical simulations impractical, we opted to introduce a similar but simpler energy model to observe the behavior on a larger scale.
@@
 
+When one spin is flipped in the SA, there would be some energy difference
+$\Delta E_{i}$ in field $i$ with temperature $T_i$. 
+We choose the probability to accept this flip to be
+
+\begin{equation}
+    \label{eq:non-equilibrium-SA}
+P = \frac{1}{1 + e^{\sum_i \frac{\Delta E_i}{T_i}}}
+\end{equation}
+
+It is easily to observe that when the system returns to
+heat-equilibrium, the probability reverts to the Glauber dynamics.
+We also provided a more general proof by constructing another equivalent model in \Cref{proof-of_non-equilibrium-SA}.
+
+\subsection{Numerical Result}
 \jinguo{show a comparison from right to left}
-\ym{I will do this in the next version.}
 
@@
 the ``Space'' dimension $N$, (ii) the ``Time'' dimension $M$, (iii) the ``Width'' of the heat zone $W$, and (iv) the temperature gradient $\Lambda$.
+\ym{I have not conducted experiments for (iii) and (iv).}
 We use the number of SA sweeps as the metric to measure the cooling time, which could be determined with the binary search.
@@
 
-\begin{figure}[]
+\begin{figure*}[]
     \centering
-    \includegraphics[width=\columnwidth,keepaspectratio]{../notes/images/main_result.pdf}
-    \caption{Numerical Result
+    \vspace*{-\topskip}
+    \includegraphics[width=\textwidth,keepaspectratio]{../notes/images/main_result.pdf}
+    \caption{Numerical Result.
     \jinguo{images should use the pdf format, the font size should be larger. Is it possible to verify that the Ising model is similar to the toy model? What is $T$ in the xlabel?}
-    \ym{I changed the labels. Maybe i need to conduct another numerical experiment
-    to verify the similarity between the Ising model and the toy model.}
+    \ym{If a comparison between Ising model and toy model is a must, plese inform me.}
     }
     \label{fig:main-numerical-result}
-\end{figure}
-
-\jinguo{you need to explain the results... what can we learn from the results?}
-\jinguo{bad variable name: Sweep Time}
+\end{figure*}
+
+% \jinguo{you need to explain the results... what can we learn from the results?}
 \Cref{fig:main-numerical-result}(a) shows the relationship between
@@
 We then fit the slopes of each line and $\frac{1}{\ln(\Lambda)}$ and find the 
-empirical constant $c$ in \Cref{eq:total-annealing-time} to be $3$. \Cref{fig:main-numerical-result}(b) shows 
-the the relationship between $T_c$ and $M$ should be linear. Combining these two results, 
+empirical constant $c$ in \Cref{eq:total-annealing-time} to be $3$.
+
+\Cref{fig:main-numerical-result}(b) shows 
+the the relationship between $T_c$ and $N$ should be linear. Combining these two results, 
 we can conclude that the time complexity should scales as $NM\log(M)^{1+\frac{1}{3\ln(\Lambda)}}$, 
 which is consistent with our theoretical prediction in \Cref{eq:total-annealing-time}.
+
+\Cref{fig:main-numerical-result}(c) compares the time complexity with different annealing
+methods. It costs exponential time to cool the system with the global annealing method no matter
+we set the system to perform a deterministic or non-deterministic computation. Using the blocking
+annealing method to perform a non-deterministic computation is still hard, too.
 
@@
 
+The classical simulated annealing can only deal with the situation that
+the temperature is space-invariant. However, we need to borden this concept
+due to the temperature gradient. Although there are many ways to
+simulated a real-world system with temperature gradient, such as
+Molecular Dynamics \cite{Bai2015, Deng2006}, but
+these methods mainly depend on dynamically adjusting the atomic
+velocities to achieve a temperature gradient, which can't be directly
+used in our model.
+
+There are also Monte Carlo-based methods to simulate a moving
+temperature wave packet that facilitates material growth~\cite{Godfrey1995, Tan2017}.
+However, these methods fail to establish a direct connection between the simulated temperature and experimental
+temperature~\cite{Zollner2014}.
+Therefore, based on HeatBath acceptance rule, we made a slight modification to the classical SA model.\jinguo{??? shouldn't it be Glauber dynamics?}
+
 Assume there is another model where the temperature at the region with 

### 2024-09-14 paper/main.tex
update

@@
 
-To overcome the overlap gap property, we propose to do block annealing, by introducing a heat zone with width $W$.
-It represents the region of the system that interacts with the heat bath, as shown in \Cref{Surface-programmable-thermodynamic computer}.
-Let layer $i$ be defined as the set of spins with x-coordinate $i$.
-The system is devided into $\lceil\frac{M}{W}\rceil$ blocks,
-where block $j$ consists of layers in the range $[(j-1)W+1, jW]$.
-The system can then be cooled by sequentially cooling the blocks from left to right with an heat bath, where the temperature of the heat bath is gradually decreased.
-We treat it as an ideal bath as it maintains a space-invariant temperature within the heat zone while keeping other regions at zero temperature.
+To overcome the overlap gap property, we propose to do block-wise annealing.
+As shown in \Cref{Surface-programmable-thermodynamic computer}, we divide the lattice into $\frac{M}{W}$ blocks along the time dimension, each having width $W$.
+%by introducing a heat zone with width $W$.
+%It represents the region of the system that interacts with the heat bath, as shown in \Cref{Surface-programmable-thermodynamic computer}.
+%Let layer $i$ be defined as the set of spins with x-coordinate $i$.
+These blocks are initialized to a low enough temperature, so that the spins freeze into a random local minimum.
+Then we anneal these blocks sequentially from left to right by heating up a block to a temperature higher than the energy scale and then cooling it down.
+%We treat it as an ideal bath as it maintains a space-invariant temperature within the heat zone while keeping other regions at zero temperature.
+Given a slow enough cooling rate, the spins in the block will settle into the global ground state.
+The cooling rate determines the true computing speed of this model.
+It must scale with the number of computational steps $M$, otherwise, the probability of success will exponentially decrease with the number of blocks.
+How cooling rate should scale with $M$ becomes a key question in this work.
 
@@
 Repeating the procedure in $\frac{M}{W}$ blocks results in a success probability of $(1 - \epsilon)^{\frac{M}{W}}$ for finding the global ground state. 
-To keep this probability constant as $M \to \infty$, the error probability $\epsilon$ should scale as $\frac{W}{M}$.
-
-Now we turn to determining the sweep time $t_{th}$ required to achieve $\epsilon$ error in each procedure. 
-Let $\lambda_1$ and $\lambda_2$ be the largest and second largest eigenvalues of the Markov transition matrix, respectively. 
-We assume the relationship between $\frac{\lambda_2}{\lambda_1}$ and $W$ can be expressed as
+To fix the success probability for arbitrary $M$, we must have $\epsilon \sim \frac{W}{M}$.
+The annealing time $t_{th}$ required to achieve a certain error in each block is determined by the spectral gap $\Delta$ of the Markov transition matrix of the SA update on the block.
+%Since the largest eigenvalue of a transition matrix is 1, the spectral gap is $\Delta = 1 - \lambda_2$, where $\lambda_2$ is the second-largest eigenvalue.
+The scaling behavior of $\Delta$ and block size $W$ can be complicated, in the worst case, it can be exponential, i.e.,
 \begin{equation}
     \label{eq:spectral-gap}
-    1 - \frac{\lambda_2}{\lambda_1} \sim e^{-W}.
-\end{equation}
-Consequently, $t_{th}$ is related to $\epsilon$ by:
-\begin{equation}
-    \left( \frac{\lambda_2}{\lambda_1} \right) ^ {t_{th}} = \epsilon \rightarrow t_{th} \sim \ln(\frac{M}{W})e^{W},
-\end{equation}
-and the total sweep times scale as $\frac{M}{W}\ln(\frac{M}{W})e^W$.
+    \Delta \sim e^{-W}.
+\end{equation}
+Consequently, $t_{th}$ is related to $\epsilon$ by $\left( 1-\Delta \right) ^ {t_{th}} = \epsilon$, which gives $t_{th} \sim \ln(\frac{M}{W})e^{W}$, and the total sweep times scale as $\frac{M}{W}\ln(\frac{M}{W})e^W$.
 
@@
 
-In practice, the heat bath and heat flux should establish a temperature gradient in the system.
+%In practice, the heat bath and heat flux should establish a temperature gradient in the system.
 % Suppose the heat bath only connects to a small rectangle region of the system.
-The temperature $T(x, t)$  at a position with x-coordinate  $x$  and time  $t$  can be modeled as  $T(x, t) \propto \Lambda^{-|x - L(t)|}$ , 
-where $\Lambda$ is a heat flux constant and $L(t)$ denotes the center of the heat bath at time $t$.
-
-The block annealing process then can be reconstruct as moving
-the heat bath from the left surface to the right surface at speed $v$. Defining $\Delta E_{max}$ to be the
-largest possible energy change when a spin is fliped.
-The effective heat zone with width $W'(\Lambda)$ should then be $[y-W'(\Lambda), y]$, where position $y$ satisfying 
-$\exp(\frac{\Delta E_{max}}{T(y)}) = 0.1$ and $y<L(t)$. 
+Instead of block-wise annealing, we propose to move the heat bath from the left surface to the right surface at a constant speed $v$.
+At time $t$, the temperature distribution $T$ is given by $T_{\rm max}\Lambda^{-|x - vt|}$, where $x$ is the computational step, $T_{\rm max}$ is the maximum temperature and $\Lambda > 1$ is a constant that determines the width of the heat zone.
+%The temperature $T(x, t)$  at a position with x-coordinate  $x$  and time  $t$  can be modeled as  $T(x, t) \propto \Lambda^{-|x - L(t)|}$ , 
+%where $\Lambda$ is a heat flux constant and $L(t)$ denotes the center of the heat bath at time $t$.
+
+We can define an effective heat zone with width $W'$ as the width of the raising edge of the temperature distribution, where the spins can be cooled actively.
+%Defining $\Delta E_{max}$ to be the largest possible energy change when a spin is fliped.
+%The effective heat zone with width $W'(\Lambda)$ should then be $[y-W'(\Lambda), y]$, where position $y$ satisfying 
+%$\exp(\frac{\Delta E_{max}}{T(y)}) = 0.1$ and $y<L(t)$. 
 % Since the layers in fronts of the effective heat zone can only be fliped with a $\epsilon$ probability if the local energy would increase. 
-The effective width $W'$ then should scale as $\exp(-\Delta E_{max} \Lambda^{cW'(\Lambda)}) \sim \epsilon$, where $c$ is an empirical constant and can be determined during the experiment. 
-\ym{I am not sure about how to give a concrete definition of the effective width $W'$.}
+The spins outside the effective heat zone are either frozen (too cold) or flip randomly (too hot).
+As a spin flips with a probability $\sim e^{-\Delta E/T}$, the cold edge of the heat zone can be defined as the position where the probability of flipping is $\epsilon$.
+We have $W'$ scales with the required error probability $\epsilon$ as:
+\begin{equation}
+    e^{-\frac{\Delta E}{T_{\rm max}}\Lambda^{cW'}} \sim \epsilon
+\end{equation}
+where $c$ is an empirical constant and can be determined during the experiment. 
+\ym{I am not sure about how to give a concrete definition of the effective width $W'$.}\jinguo{How about this?}
 
@@
     \label{eq:total-annealing-time}
-    t_{total} \propto \frac{M}{W'(\Lambda)}(\ln(\frac{M}{W'(\Lambda)}))^{1+ \frac{1}{c\ln(\Lambda)}}
+    t_{total} \propto \frac{M}{W'}(\ln(\frac{M}{W'}))^{1+ \frac{1}{c\ln(\Lambda)}}
 \end{equation}
@@
 for the computation should scale as $NM\log^{1 + \frac{1}{c\ln(\Lambda)}}(M)$.
-\ym{Please help me to think about how to evaluate the time complexity while $N$ increases.} 
+\ym{Please help me to think about how to evaluate the time complexity while $N$ increases.}\jinguo{Leave it to Maddie}
 The moving speed $v$ can be then calculated as

### 2024-09-14 paper/main.tex
update

@@
 \end{equation}
-Consequently, $t_{th}$ is related to $\epsilon$ by $\left( 1-\Delta \right) ^ {t_{th}} = \epsilon$, which gives $t_{th} \sim \ln(\frac{M}{W})e^{W}$, and the total sweep times scale as $\frac{M}{W}\ln(\frac{M}{W})e^W$.
+Consequently, $t_{th}$ is related to $\epsilon$ by $\left( 1-\Delta \right) ^ {t_{th}} = \epsilon$, which gives $t_{th} \sim \ln\left(\frac{M}{W}\right)e^{W}$, and the total sweep times scale as:
+\begin{equation}\label{eq:totaltime}
+t_{\rm total} \sim \frac{M}{W}\ln\left(\frac{M}{W}\right)e^W.
+\end{equation}
 
@@
 \ym{I am not sure about how to give a concrete definition of the effective width $W'$.}\jinguo{How about this?}
-
-The total sweep time with a fixed inputs size $N$ can then be calculated as
-
+We have $\log(\Lambda) cW' \sim \log(\frac{T_{\rm max}}{\Delta E}\log(\frac{1}{\epsilon}))$.
+
+Combining with \Cref{eq:totaltime}, the total annealing time can be estimated as
 \begin{equation}
     \label{eq:total-annealing-time}
-    t_{total} \propto \frac{M}{W'}(\ln(\frac{M}{W'}))^{1+ \frac{1}{c\ln(\Lambda)}}
+    t_{\rm total} \sim \frac{M}{W'}\left(\ln\left(\frac{M}{W'}\right)\right)^{1+ \frac{1}{c\ln(\Lambda)}}
 \end{equation}
@@
     \ym{If a comparison between Ising model and toy model is a must, plese inform me.}
+    \jinguo{(1) We should make the lines in (c) fit better with the data points.
+(2) Please complete the caption.
+You need to at least explain the short notations: GA, HB.
+(3) Please use log-scale axes for (a) and (c), instead of taking log directly on the data points.
+$\ln(\ln(M))$ is difficult to interpret.}
     }

### 2024-09-16 paper/main.tex
update main figure, add description for eqa (8).

@@
     % \jinguo{please add symbols for space, time and width}
-    \ym{I add symbols. please check if i still need to put original captions here}
+    % \ym{I add symbols. please check if i still need to put original captions here}
     \jinguo{please make the circles and texts in the inset larger}
@@
 where $c$ is an empirical constant and can be determined during the experiment. 
-\ym{I am not sure about how to give a concrete definition of the effective width $W'$.}\jinguo{How about this?}
-We have $\log(\Lambda) cW' \sim \log(\frac{T_{\rm max}}{\Delta E}\log(\frac{1}{\epsilon}))$.
-
-Combining with \Cref{eq:totaltime}, the total annealing time can be estimated as
+\jinguo{How about this?}
+\ym{But I still don't think the constant $c$ is reasonable in this version. Anyway it is a better 
+description for $W'$.}
+
+We can further derive $e^{W'}$ as function of $\Lambda$:
+\begin{equation}
+    e^{\ln(\Lambda)cW'}\sim \ln(\frac{1}{\epsilon})\rightarrow e^{W'}\sim \ln(\frac{1}{\epsilon})^{\frac{1}{c\ln(\Lambda)}}
+\end{equation}
+
+Combining with \Cref{eq:totaltime} and $\epsilon \sim \frac{W'}{M}$, the total annealing time can be estimated as
 \begin{equation}
@@
     \includegraphics[width=\textwidth,keepaspectratio]{../notes/images/main_result.pdf}
-    \caption{Numerical Result.
+    \caption{Numerical Result. (a) The moving speed $v$ of the heat bath is proportional
+    to $\ln(M)^{f(\Lambda)}$, where the power function $f(\Lambda)$ can be determined
+    by fitting the slope. (b) The total annealing time $T_c$ scales linearly with the
+    number of spins in single layer $N$. (c) The total annealing time $T_c$ with different annealing methods,
+    including heat bath (HB) moving forward, heat bath (HB) moving backward, Global annealing (GA) with input spins fixed and
+    Global annealing (GA) with output spins fixed. The latter three methods are all hard to cool the system.
     \jinguo{images should use the pdf format, the font size should be larger. Is it possible to verify that the Ising model is similar to the toy model? What is $T$ in the xlabel?}
@@
 (3) Please use log-scale axes for (a) and (c), instead of taking log directly on the data points.
-$\ln(\ln(M))$ is difficult to interpret.}
-    }
+$\ln(\ln(M))$ is difficult to interpret.}}
     \label{fig:main-numerical-result}
@@
 
-\section{Physical implementation on Ising machine}\label{spin-glass}
+% \section{Physical implementation on Ising machine}\label{spin-glass}
 

### 2024-09-16 paper/main.tex
enlarge the circles and texts in the inset picture of Fig.1

@@
 
-%Shape: Circle [id:dp3980815479811872] 
-\draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ] (491,154.1) ..
-controls (491,151.61) and (493.01,149.6) ..
-(495.5,149.6) ..
-controls (497.99,149.6) and (500,151.61) ..
-(500,154.1) ..
-controls (500,156.59) and (497.99,158.6) ..
-(495.5,158.6) ..
-controls (493.01,158.6) and (491,156.59) ..
-(491,154.1) -- cycle ;
-%Shape: Circle [id:dp8208493476316323] 
-\draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ] (491,191.1) ..
-controls (491,188.61) and (493.01,186.6) ..
-(495.5,186.6) ..
-controls (497.99,186.6) and (500,188.61) ..
-(500,191.1) ..
-controls (500,193.59) and (497.99,195.6) ..
-(495.5,195.6) ..
-controls (493.01,195.6) and (491,193.59) ..
-(491,191.1) -- cycle ;
+%Shape: Ellipse [id:dp3980815479811872] 
+\draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ] (493.14,156.7) ..
+controls (493.14,153.44) and (495.79,150.79) ..
+(499.05,150.79) ..
+controls (502.31,150.79) and (504.96,153.44) ..
+(504.96,156.7) ..
+controls (504.96,159.97) and (502.31,162.61) ..
+(499.05,162.61) ..
+controls (495.79,162.61) and (493.14,159.97) ..
+(493.14,156.7) -- cycle ;
+%Shape: Ellipse [id:dp8208493476316323] 
+\draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ] (493.14,205.29) ..
+controls (493.14,202.03) and (495.79,199.38) ..
+(499.05,199.38) ..
+controls (502.31,199.38) and (504.96,202.03) ..
+(504.96,205.29) ..
+controls (504.96,208.56) and (502.31,211.2) ..
+(499.05,211.2) ..
+controls (495.79,211.2) and (493.14,208.56) ..
+(493.14,205.29) -- cycle ;
 %Shape: Circle [id:dp3173494411067954] 
-\draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ] (478.67,172.6) ..
-controls (478.67,170.11) and (480.68,168.1) ..
-(483.17,168.1) ..
-controls (485.65,168.1) and (487.67,170.11) ..
-(487.67,172.6) ..
-controls (487.67,175.09) and (485.65,177.1) ..
-(483.17,177.1) ..
-controls (480.68,177.1) and (478.67,175.09) ..
-(478.67,172.6) -- cycle ;
-%Shape: Circle [id:dp967421569400009] 
-\draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ] (503.4,172.6) ..
-controls (503.4,170.11) and (505.41,168.1) ..
-(507.9,168.1) ..
-controls (510.39,168.1) and (512.4,170.11) ..
-(512.4,172.6) ..
-controls (512.4,175.09) and (510.39,177.1) ..
-(507.9,177.1) ..
-controls (505.41,177.1) and (503.4,175.09) ..
-(503.4,172.6) -- cycle ;
-%Shape: Circle [id:dp938870324276512] 
-\draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ] (524.7,172.5) ..
-controls (524.7,170.01) and (526.71,168) ..
-(529.2,168) ..
-controls (531.69,168) and (533.7,170.01) ..
-(533.7,172.5) ..
-controls (533.7,174.99) and (531.69,177) ..
-(529.2,177) ..
-controls (526.71,177) and (524.7,174.99) ..
-(524.7,172.5) -- cycle ;
+\draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ] (476.94,181) ..
+controls (476.94,177.74) and (479.59,175.09) ..
+(482.85,175.09) ..
+controls (486.12,175.09) and (488.76,177.74) ..
+(488.76,181) ..
+controls (488.76,184.26) and (486.12,186.91) ..
+(482.85,186.91) ..
+controls (479.59,186.91) and (476.94,184.26) ..
+(476.94,181) -- cycle ;
+%Shape: Ellipse [id:dp967421569400009] 
+\draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ] (509.42,181) ..
+controls (509.42,177.74) and (512.07,175.09) ..
+(515.33,175.09) ..
+controls (518.6,175.09) and (521.24,177.74) ..
+(521.24,181) ..
+controls (521.24,184.26) and (518.6,186.91) ..
+(515.33,186.91) ..
+controls (512.07,186.91) and (509.42,184.26) ..
+(509.42,181) -- cycle ;
+%Shape: Ellipse [id:dp938870324276512] 
+\draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ] (537.4,180.87) ..
+controls (537.4,177.6) and (540.04,174.96) ..
+(543.31,174.96) ..
+controls (546.57,174.96) and (549.22,177.6) ..
+(549.22,180.87) ..
+controls (549.22,184.13) and (546.57,186.78) ..
+(543.31,186.78) ..
+controls (540.04,186.78) and (537.4,184.13) ..
+(537.4,180.87) -- cycle ;
 %Rounded Rect [id:dp40904235215635065] 
-\draw  [fill={rgb, 255:red, 235; green, 83; blue, 112 }  ,fill opacity=1 ] (475.6,155.04) ..
-controls (475.6,148.59) and (480.83,143.36) ..
-(487.28,143.36) -- (525.12,143.36) ..
-controls (531.57,143.36) and (536.8,148.59) ..
-(536.8,155.04) -- (536.8,190.08) ..
-controls (536.8,196.53) and (531.57,201.76) ..
-(525.12,201.76) -- (487.28,201.76) ..
-controls (480.83,201.76) and (475.6,196.53) ..
-(475.6,190.08) -- cycle ;
+\draw  [fill={rgb, 255:red, 235; green, 83; blue, 112 }  ,fill opacity=1 ] (472.92,157.94) ..
+controls (472.92,149.47) and (479.78,142.6) ..
+(488.26,142.6) -- (537.95,142.6) ..
+controls (546.42,142.6) and (553.29,149.47) ..
+(553.29,157.94) -- (553.29,203.95) ..
+controls (553.29,212.43) and (546.42,219.29) ..
+(537.95,219.29) -- (488.26,219.29) ..
+controls (479.78,219.29) and (472.92,212.43) ..
+(472.92,203.95) -- cycle ;
 %Straight Lines [id:da6938220604961829] 
-\draw    (491,154.1) -- (469.8,154.1) ;
+\draw    (493.14,156.7) -- (465.3,156.7) ;
 %Straight Lines [id:da05667244881651223] 
-\draw    (478.67,172.47) -- (469.8,172.5) ;
+\draw    (476.94,180.82) -- (465.3,180.87) ;
 %Straight Lines [id:da7336130308225484] 
-\draw    (491,191.1) -- (469.8,191.1) ;
+\draw    (493.14,205.29) -- (465.3,205.29) ;
 %Straight Lines [id:da9632416883191204] 
-\draw    (483.17,172.6) -- (495.5,154.1) ;
+\draw    (482.85,181) -- (499.05,156.7) ;
 %Straight Lines [id:da8062551247029028] 
-\draw    (483.17,172.6) -- (495.5,191.1) ;
+\draw    (482.85,181) -- (499.05,205.29) ;
 %Straight Lines [id:da6815111207533529] 
-\draw    (495.5,154.1) -- (507.9,172.6) ;
+\draw    (499.05,156.7) -- (515.33,181) ;
 %Straight Lines [id:da2583696463055196] 
-\draw    (495.5,191.1) -- (507.9,172.6) ;
+\draw    (499.05,205.29) -- (515.33,181) ;
 %Straight Lines [id:da5112788448231447] 
-\draw    (483.17,172.6) -- (507.9,172.6) ;
+\draw    (482.85,181) -- (515.33,181) ;
 %Straight Lines [id:da21092112099851623] 
-\draw    (495.5,191.1) -- (495.5,154.1) ;
+\draw    (499.05,205.29) -- (499.05,178.37) -- (499.05,156.7) ;
 %Curve Lines [id:da6381556136782309] 
-\draw    (495.5,191.1) .. controls (509.12,191.04) and (521.92,189.04) .. (529.2,172.5) ;
+\draw    (499.05,205.29) .. controls (516.94,205.22) and (533.75,202.59) .. (543.31,180.87) ;
 %Curve Lines [id:da40382455887046964] 
-\draw    (495.5,154.1) .. controls (511.92,153.84) and (524.32,158.24) .. (529.2,172.5) ;
+\draw    (499.05,156.7) .. controls (520.61,156.36) and (536.9,162.14) .. (543.31,180.87) ;
 %Curve Lines [id:da518536427411914] 
-\draw    (529.2,172.5) .. controls (514.32,159.44) and (495.92,161.04) .. (483.17,172.6) ;
+\draw    (543.31,180.87) .. controls (523.77,163.72) and (499.6,165.82) .. (482.85,181) ;
 %Curve Lines [id:da5213323072929468] 
-\draw    (529.2,172.5) .. controls (523.52,180.64) and (511.92,179.84) .. (507.9,172.6) ;
+\draw    (543.31,180.87) .. controls (535.85,191.56) and (520.61,190.51) .. (515.33,181) ;
 %Straight Lines [id:da26081701800713075] 
-\draw    (533.7,172.5) -- (541.8,172.5) ;
-%Shape: Circle [id:dp28592847133985866] 
-\draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ] (478.67,172.6) ..
-controls (478.67,170.11) and (480.68,168.1) ..
-(483.17,168.1) ..
-controls (485.65,168.1) and (487.67,170.11) ..
-(487.67,172.6) ..
-controls (487.67,175.09) and (485.65,177.1) ..
-(483.17,177.1) ..
-controls (480.68,177.1) and (478.67,175.09) ..
-(478.67,172.6) -- cycle ;
-%Shape: Circle [id:dp7005363351052425] 
-\draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ] (491,154.1) ..
-controls (491,151.61) and (493.01,149.6) ..
-(495.5,149.6) ..
-controls (497.99,149.6) and (500,151.61) ..
-(500,154.1) ..
-controls (500,156.59) and (497.99,158.6) ..
-(495.5,158.6) ..
-controls (493.01,158.6) and (491,156.59) ..
-(491,154.1) -- cycle ;
-%Shape: Circle [id:dp5131516311175763] 
-\draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ] (491,191.1) ..
-controls (491,188.61) and (493.01,186.6) ..
-(495.5,186.6) ..
-controls (497.99,186.6) and (500,188.61) ..
-(500,191.1) ..
-controls (500,193.59) and (497.99,195.6) ..
-(495.5,195.6) ..
-controls (493.01,195.6) and (491,193.59) ..
-(491,191.1) -- cycle ;
-%Shape: Circle [id:dp38829310474408074] 
-\draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ] (503.4,172.6) ..
-controls (503.4,170.11) and (505.41,168.1) ..
-(507.9,168.1) ..
-controls (510.39,168.1) and (512.4,170.11) ..
-(512.4,172.6) ..
-controls (512.4,175.09) and (510.39,177.1) ..
-(507.9,177.1) ..
-controls (505.41,177.1) and (503.4,175.09) ..
-(503.4,172.6) -- cycle ;
-%Shape: Circle [id:dp6003377245628321] 
-\draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ] (524.7,172.5) ..
-controls (524.7,170.01) and (526.71,168) ..
-(529.2,168) ..
-controls (531.69,168) and (533.7,170.01) ..
-(533.7,172.5) ..
-controls (533.7,174.99) and (531.69,177) ..
-(529.2,177) ..
-controls (526.71,177) and (524.7,174.99) ..
-(524.7,172.5) -- cycle ;
+\draw    (549.22,180.87) -- (559.85,180.87) ;
+%Shape: Ellipse [id:dp28592847133985866] 
+\draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ] (476.94,181) ..
+controls (476.94,177.74) and (479.59,175.09) ..
+(482.85,175.09) ..
+controls (486.12,175.09) and (488.76,177.74) ..
+(488.76,181) ..
+controls (488.76,184.26) and (486.12,186.91) ..
+(482.85,186.91) ..
+controls (479.59,186.91) and (476.94,184.26) ..
+(476.94,181) -- cycle ;
+%Shape: Ellipse [id:dp7005363351052425] 
+\draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ] (493.14,156.7) ..
+controls (493.14,153.44) and (495.79,150.79) ..
+(499.05,150.79) ..
+controls (502.31,150.79) and (504.96,153.44) ..
+(504.96,156.7) ..
+controls (504.96,159.97) and (502.31,162.61) ..
+(499.05,162.61) ..
+controls (495.79,162.61) and (493.14,159.97) ..
+(493.14,156.7) -- cycle ;
+%Shape: Ellipse [id:dp5131516311175763] 
+\draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ] (493.14,205.29) ..
+controls (493.14,202.03) and (495.79,199.38) ..
+(499.05,199.38) ..
+controls (502.31,199.38) and (504.96,202.03) ..
+(504.96,205.29) ..
+controls (504.96,208.56) and (502.31,211.2) ..
+(499.05,211.2) ..
+controls (495.79,211.2) and (493.14,208.56) ..
+(493.14,205.29) -- cycle ;
+%Shape: Ellipse [id:dp38829310474408074] 
+\draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ] (509.42,181) ..
+controls (509.42,177.74) and (512.07,175.09) ..
+(515.33,175.09) ..
+controls (518.6,175.09) and (521.24,177.74) ..
+(521.24,181) ..
+controls (521.24,184.26) and (518.6,186.91) ..
+(515.33,186.91) ..
+controls (512.07,186.91) and (509.42,184.26) ..
+(509.42,181) -- cycle ;
+%Shape: Ellipse [id:dp6003377245628321] 
+\draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ] (537.4,180.87) ..
+controls (537.4,177.6) and (540.04,174.96) ..
+(543.31,174.96) ..
+controls (546.57,174.96) and (549.22,177.6) ..
+(549.22,180.87) ..
+controls (549.22,184.13) and (546.57,186.78) ..
+(543.31,186.78) ..
+controls (540.04,186.78) and (537.4,184.13) ..
+(537.4,180.87) -- cycle ;
+%Straight Lines [id:da025020526203919813] 
+\draw    (305.63,73.33) -- (329.63,73.33) ;
+\draw [shift={(331.63,73.33)}, rotate = 180] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) ..
+controls (6.95,-1.4) and (3.31,-0.3) ..
+(0,0) ..
+controls (3.31,0.3) and (6.95,1.4) ..
+(10.93,3.29)   ;
+%Shape: Brace [id:dp8023308836405996] 
+\draw   (283.2,286.4) ..
+controls (283.2,291.07) and (285.53,293.4) ..
+(290.2,293.4) -- (314.2,293.4) ..
+controls (320.87,293.4) and (324.2,295.73) ..
+(324.2,300.4) ..
+controls (324.2,295.73) and (327.53,293.4) ..
+(334.2,293.4)(331.2,293.4) -- (358.2,293.4) ..
+controls (362.87,293.4) and (365.2,291.07) ..
+(365.2,286.4) ;
 
@@
     % Text Node
-    \draw (492.00,150.41) node [anchor=north west][inner sep=0.75pt]   [align=left] {{\tiny {$p$}}};
+    \draw (494.80,152.01) node [anchor=north west][inner sep=0.75pt]   [align=left] {{\scriptsize {$p$}}};
     % Text Node
-    \draw (479.75,168.95) node [anchor=north west][inner sep=0.75pt]   [align=left] {{\tiny {$q$}}};
+    \draw (478.75,176.45) node [anchor=north west][inner sep=0.75pt]   [align=left] {{\scriptsize {$q$}}};
     % Text Node
-    \draw (492.45,188.12) node [anchor=north west][inner sep=0.75pt]   [align=left] {{\tiny {$r$}}};
+    \draw (495.60,201.80) node [anchor=north west][inner sep=0.75pt]   [align=left] {{\scriptsize {$r$}}};
     % Text Node
-    \draw (525.00,166.95) node [anchor=north west][inner sep=0.75pt]   [align=left] {{\tiny {$q'$}}};
+    \draw (539.00,174.95) node [anchor=north west][inner sep=0.75pt]   [align=left] {{\scriptsize {$q'$}}};
     % Text Node
-    \draw (504.00,168.45) node [anchor=north west][inner sep=0.75pt]   [align=left] {{\tiny {$A$}}};
+    \draw (510.60,175.95) node [anchor=north west][inner sep=0.75pt]   [align=left] {{\scriptsize {$A$}}};
 

### 2024-09-16 paper/main.tex
update

@@
     % Text Node
-    \draw (495.60,201.80) node [anchor=north west][inner sep=0.75pt]   [align=left] {{\scriptsize {$r$}}};
+    \draw (495.30,201.60) node [anchor=north west][inner sep=0.75pt]   [align=left] {{\footnotesize {$r$}}};
     % Text Node
@@
     \label{eq:spectral-gap}
-    \Delta \sim e^{-W}.
-\end{equation}
-Consequently, $t_{th}$ is related to $\epsilon$ by $\left( 1-\Delta \right) ^ {t_{th}} = \epsilon$, which gives $t_{th} \sim \ln\left(\frac{M}{W}\right)e^{W}$, and the total sweep times scale as:
+    \Delta \sim e^{-f(W)},
+\end{equation}
+where $f(W)$ is a polynomial of $W$.
+Consequently, $t_{th}$ is related to $\epsilon$ by $\left( 1-\Delta \right) ^ {t_{th}} = \epsilon$, which gives $t_{th} \sim \ln\left(\frac{M}{W}\right)e^{f(W)}$, and the total sweep times scale as:
 \begin{equation}\label{eq:totaltime}
-t_{\rm total} \sim \frac{M}{W}\ln\left(\frac{M}{W}\right)e^W.
+t_{\rm total} \sim \frac{M}{W}\ln\left(\frac{M}{W}\right)e^{f(W)}.
 \end{equation}
@@
 \begin{equation}
-    e^{-\frac{\Delta E}{T_{\rm max}}\Lambda^{cW'}} \sim \epsilon
-\end{equation}
-where $c$ is an empirical constant and can be determined during the experiment. 
-\jinguo{How about this?}
+    e^{-\frac{\Delta E}{T_{\rm max}}\Lambda^{W'}} \sim \epsilon
+\end{equation}
 \ym{But I still don't think the constant $c$ is reasonable in this version. Anyway it is a better 
 description for $W'$.}
-
-We can further derive $e^{W'}$ as function of $\Lambda$:
-\begin{equation}
-    e^{\ln(\Lambda)cW'}\sim \ln(\frac{1}{\epsilon})\rightarrow e^{W'}\sim \ln(\frac{1}{\epsilon})^{\frac{1}{c\ln(\Lambda)}}
-\end{equation}
-
-Combining with \Cref{eq:totaltime} and $\epsilon \sim \frac{W'}{M}$, the total annealing time can be estimated as
+\jinguo{I changed $c$ to $1/c$}
+
+We can further derive $e^{W'}$ as function of $\Lambda$ by taking the logarithm of both sides:
+\begin{equation}
+    e^{\ln(\Lambda)W'}\sim \ln(\epsilon^{-1})\rightarrow e^{W'}\sim \ln(\epsilon^{-1})^{\frac{1}{\ln(\Lambda)}}
+\end{equation}
+
+Let $f(x) = c x + b$, then $e^{f(W')} \sim \ln(\epsilon^{-1})^{\frac{c}{\ln(\Lambda)}}$.
+Combining with \Cref{eq:totaltime} and the requirement of $\epsilon \sim \frac{W'}{M}$, the total annealing time can be estimated as
 \begin{equation}
     \label{eq:total-annealing-time}
-    t_{\rm total} \sim \frac{M}{W'}\left(\ln\left(\frac{M}{W'}\right)\right)^{1+ \frac{1}{c\ln(\Lambda)}}
-\end{equation}
-
-To determine the relationship between the total annealing time and the input size $N$, we should
-further discuss the relationship between the spectral gap given in  \Cref{eq:spectral-gap} and inputs size $N$.
-However, we failed to find a direct relationship.
-Numerical result shows that computing complexity is linear to $N$. Thus a total sweep time
-for the computation should scale as $NM\log^{1 + \frac{1}{c\ln(\Lambda)}}(M)$.
+    t_{\rm total} \sim \frac{M}{W'}\ln\left(\frac{M}{W'}\right)^{1+ \frac{c}{\ln(\Lambda)}}
+\end{equation}
+The reason why we choose $f$ to be linear is due to the simplicity of the model, and it turns out to be a good approximation in the numerical simulation.
+%To determine the relationship between the total annealing time and the input size $N$, we should
+%further discuss the relationship between the spectral gap given in  \Cref{eq:spectral-gap} and inputs size $N$.
+%However, we failed to find a direct relationship.
+%Numerical result shows that computing complexity is linear to $N$.
+%Thus a total sweep time for the computation should scale as $NM\log^{1 + \frac{c}{\ln(\Lambda)}}(M)$.
 \ym{Please help me to think about how to evaluate the time complexity while $N$ increases.}\jinguo{Leave it to Maddie}
-The moving speed $v$ can be then calculated as
-
+The computing speed $v$ defined as operations per unit time, can be estimated as
 \begin{equation}
     \label{eq:moving-speed}
-    v \propto \frac{t_{total}}{M} = N\log^{1 + \frac{1}{c\ln(\Lambda)}}(M)
-\end{equation}
+    v = \frac{M}{t_{total}} \sim \ln(M)^{-(1 + \frac{c}{\ln(\Lambda)})}
+\end{equation}
+As the computational step $M$ increases, the computing speed $v$ decreases logarithmically.
 

### 2024-09-16 paper/main.tex
updte

@@
 %non-deterministic direction.
-\begin{hyp}
+\begin{hyp}\label{hyp:overlap-gap}
 Let $\mathcal{P}$ be a circuit SAT problem, and $\mathcal{E}$ be an energy modeling encoding of $\mathcal{P}$ (locally).
@@
 \subsection{Dynamic annealing}\label{cooling-computation-with-moving-heat-bath}
-\jinguo{Please shorten this section!}
-
+
+\subsubsection{Block-wise annealing}
 To overcome the overlap gap property, we propose to do block-wise annealing.
@@
 
-\subsubsection{A more realistic heat bath}\label{estimation-of-the-computing-time}
+\subsubsection{Annealing by a moving heat bath}\label{estimation-of-the-computing-time}
 
@@
 \section{Numerical simulation}\label{sec:numerical-result}
-
-\subsection{Model and Method}
-Given that simulating a CA with a deep computational layer on the Ising model requires many spins, making large-scale numerical simulations impractical, we opted to introduce a similar but simpler energy model to observe the behavior on a larger scale.
-Let us define a simpler but ``equivalent'' energy model on a 2D lattice of size $N \times M$, whose hamiltonian
-is given by
+%Given that simulating a CA with a deep computational layer on the Ising model requires many spins, making large-scale numerical simulations impractical, we opted to introduce a similar but simpler energy model to observe the behavior on a larger scale.
+Instead of studying the spin-glass model directly, we propose a toy energy model to enable large-scale numerical simulations.
+%on a 2D lattice of size $N \times M$.
+The energy model on a 2D lattice of size $N \times M$ is defined as:
 \begin{equation}\label{eq:toy-hamiltonian}
@@
 
-When one spin is flipped in the SA, there would be some energy difference
-$\Delta E_{i}$ in field $i$ with temperature $T_i$. 
-We choose the probability to accept this flip to be
-
+Modeling temperature gradient could be achieved by using the following non-equilibrium SA acceptance probability:
 \begin{equation}
     \label{eq:non-equilibrium-SA}
-P = \frac{1}{1 + e^{\sum_i \frac{\Delta E_i}{T_i}}}
-\end{equation}
-
-It is easily to observe that when the system returns to
-heat-equilibrium, the probability reverts to the Glauber dynamics.
-We also provided a more general proof by constructing another equivalent model in \Cref{proof-of_non-equilibrium-SA}.
+P = \frac{1}{1 + e^{\sum_i \Delta E_i/ T_i}},
+\end{equation}
+where $\Delta E_i$ is the energy change of the $i$-th term in the Hamiltonian and $T_i$ is the temperature of the $i$-th term.
+It is easily to verify that this acceptance probability returns to the Glauber dynamics when $T_i = T$ for all $i$.
+In \Cref{proof-of_non-equilibrium-SA}, we show this non-equilibrilium SA is equivalent to an equilibrilium SA with a layer dependent energy scale.
 
 \subsection{Numerical Result}
-\jinguo{show a comparison from right to left}
-
-Here we conducted numerical experiments to examine how the cooling time $T_{c}$ scales with (i)
+Here we conducted numerical experiments to examine how the cooling time $T_{c}$ ($N \times t_{\rm total}$) scales with (i)
 the ``Space'' dimension $N$, (ii) the ``Time'' dimension $M$, (iii) the ``Width'' of the heat zone $W$, and (iv) the temperature gradient $\Lambda$.
 \ym{I have not conducted experiments for (iii) and (iv).}
-We use the number of SA sweeps as the metric to measure the cooling time, which could be determined with the binary search.
-We keep changing the heat bath moving speed $v$ (in unit of columns/sweep) until the system can reach a ground state configuration with $\sim 50\%$ probability.
+If a SA run finds the ground state, we mark it as a success, otherwise, it is a failure.
+The success probability is directly related to the moving speed $v$ of the heat bath.
+The slower the heat bath moves, the higher the success probability.
+We use the number of SA sweeps to reach $50\%$ success probability as the metric to measure the cooling time, which could be obtained by tuning the speed $v$ through binary search.
 
@@
     \includegraphics[width=\textwidth,keepaspectratio]{../notes/images/main_result.pdf}
-    \caption{Numerical Result. (a) The moving speed $v$ of the heat bath is proportional
+    \caption{Simulated annealing results for the toy model in \Cref{eq:toy-hamiltonian}.
+    (a) The moving speed $v$ of the heat bath is proportional
     to $\ln(M)^{f(\Lambda)}$, where the power function $f(\Lambda)$ can be determined
     by fitting the slope. (b) The total annealing time $T_c$ scales linearly with the
-    number of spins in single layer $N$. (c) The total annealing time $T_c$ with different annealing methods,
+    number of spins in single layer $N$. (c) The total annealing time $T_c$ ($N \times t_{\rm total}$) with different annealing methods,
     including heat bath (HB) moving forward, heat bath (HB) moving backward, Global annealing (GA) with input spins fixed and
     Global annealing (GA) with output spins fixed. The latter three methods are all hard to cool the system.
-    \jinguo{images should use the pdf format, the font size should be larger. Is it possible to verify that the Ising model is similar to the toy model? What is $T$ in the xlabel?}
+    \jinguo{Is it possible to verify that the Ising model is similar to the toy model?}
     \ym{If a comparison between Ising model and toy model is a must, plese inform me.}
-    \jinguo{(1) We should make the lines in (c) fit better with the data points.
-(2) Please complete the caption.
-You need to at least explain the short notations: GA, HB.
-(3) Please use log-scale axes for (a) and (c), instead of taking log directly on the data points.
-$\ln(\ln(M))$ is difficult to interpret.}}
+    }
     \label{fig:main-numerical-result}
@@
 % \jinguo{you need to explain the results... what can we learn from the results?}
-\Cref{fig:main-numerical-result}(a) shows the relationship between
-$\ln(\ln(M))$ and $\ln(v)$ shoule be linear, which implies 
-the time complexity $T_c$ along the ``Time'' direction should scale as $M\ln(M)^{f(\Lambda)}$. 
-We then fit the slopes of each line and $\frac{1}{\ln(\Lambda)}$ and find the 
-empirical constant $c$ in \Cref{eq:total-annealing-time} to be $3$.
-
-\Cref{fig:main-numerical-result}(b) shows 
-the the relationship between $T_c$ and $N$ should be linear. Combining these two results, 
-we can conclude that the time complexity should scales as $NM\log(M)^{1+\frac{1}{3\ln(\Lambda)}}$, 
-which is consistent with our theoretical prediction in \Cref{eq:total-annealing-time}.
-
-\Cref{fig:main-numerical-result}(c) compares the time complexity with different annealing
-methods. It costs exponential time to cool the system with the global annealing method no matter
-we set the system to perform a deterministic or non-deterministic computation. Using the blocking
-annealing method to perform a non-deterministic computation is still hard, too.
+\Cref{fig:main-numerical-result} (a) shows a polynomial correlation between $\ln(M)$ and $v$. By fitting the curve, we can determine the constant $c$ in \Cref{eq:moving-speed}.
+An empirical value of $c \approx 1/3$ is obtained.
+\Cref{fig:main-numerical-result} (b) shows a linear relationship between $T_c$ and $N$.
+Since in a real TC, a layer is cooled in parallel, the true computing time $t_{\rm total} \sim T_c / N$, which cancels the linear scaling of $N$.
+We conclude that the real computing time does not scale with the computer memory size $N$.
+%we can conclude that the time complexity should scales as $NM\log(M)^{1+\frac{1}{3\ln(\Lambda)}}$, 
+%which is consistent with our theoretical prediction in \Cref{eq:total-annealing-time}.
+
+\Cref{fig:main-numerical-result}(c) compares different annealing methods for computing from the deterministic direction and the non-deterministic direction.
+The computing time scales exponentially with the number of layers $M$ for all non-deterministic methods, regardless of the direction of computation.
+It is consistent with the computational complexity of the circuit satisfiability problem.
+For the deterministic computation, the global annealing method also takes exponential time, which is consistent with our theoretical prediction in \Cref{hyp:overlap-gap}.
+The heat bath moving forward method is the most efficient, the computing time is almost perfectly linear to $M\ln(M)^{(1+\frac{c}{\ln(\Lambda)})}$.\jinguo{we need to add this plot back, how about using linear axis in figure (c)?}
 

### 2024-09-16 paper/main.tex
update

@@
 
-Energy based models are probability one of the most powerful models for computation.
-The Ising model is not only capable of universal computation~\cite{gu2012encoding}, and it can be used to formulate many NP problems~\cite{lucas2014ising,mohseni2022ising}.
-
-However, they are notoriously hard to thermalize, even with the help of quantum entanglement~\cite{boixo2013experimental, boixo2014evidence, Pichler2018, Ebadi2022, Nguyen2023}.
-There is no evidence yet that they can significantly outperform existing algorithms run on classical computers~\cite{}.
-Even when the encoded problem is an easy one, it is not guaranteed that the system can thermalize in polynomial time as we will show in the main text.
-
-Intrigued by the question of how to thermalize and lower the energy of an Ising machine, we propose a new type of TC that has a crystalline structure.
-The crystalline structure is based on a universal elementary CA, and is translational invariant in all spacial dimensions.
-The translational invariance not only makes the crystal easier to be constructed in nature, but also enables the study of the scaling behavior the thermalization process.
-In the rest of this paper, we first show that the crystalline structure can be programmed on its surfaces to perform universal computation \Cref{sec:Overview-of-main-results}.
-Then we use numerical results in \Cref{sec:numerical-result} to show that if we thermalize the crystal from the so-called ``deterministic direction'', the crystal can thermalize in time almost linear to the size of the crystal, i.e.
-efficient computation can be performed.
+In this work, we focus on the energy based models, which are one of the most powerful models for computation.
+For example, the Ising model can formulate any problems in NP~\cite{gu2012encoding, lucas2014ising,mohseni2022ising}.
+However, Ising models with random coupling are notoriously hard to thermalize, even with the help of quantum entanglement~\cite{boixo2013experimental, boixo2014evidence, Pichler2018, Ebadi2022, Nguyen2023}.
+%There is no evidence yet that they can significantly outperform existing algorithms run on classical computers~\cite{}.
+
+Can we utilize a natural energy based model for efficient computation?
+Intrigued by this question, we designed an energy based TC as a translational invariant Ising model with universal computation capability on its surface, and study how to efficiently thermalize the system to perform computation.
+Our TC implements a universal elementary CA, the translational invariance in both time and space dimension mimics a crystal in nature, which also eases the study of the scaling behaviors the thermalization process.
+
+In the rest of this paper, we first show the design of crystalline structure that can be programmed on its surfaces to perform universal computation in \Cref{sec:Overview-of-main-results}.
+The method we use to study the thermalization process is introduced in \Cref{sec:model-method}.
+Finally, we reported numerical simulation results in \Cref{sec:numerical-result}.
+We show that even when the encoded problem is a deterministic computation, the system is not guaranteed to thermalize in time polynomial to the size of the crystal.
+However, if we use the moving temperature gradient method, the system can thermalize in time almost linear to the size of the crystal, i.e. just like a normal computer.
 

### 2024-10-13 paper/main.tex
update
update one figure
Wrote down the problem, temporarily blocked part: Numerical simulation

@@
 We show that even when the encoded problem is a deterministic computation, the system is not guaranteed to thermalize in time polynomial to the size of the crystal.
-However, if we use the moving temperature gradient method, the system can thermalize in time almost linear to the size of the crystal, i.e. just like a normal computer.
+However, if we use the moving temperature gradient method, the system can thermalize in time almost linear to the size of the crystal, i.e. as efficient as a normal computer.
 
@@
 %Straight Lines [id:da025020526203919813] 
-\draw    (305.63,73.33) -- (329.63,73.33) ;
-\draw [shift={(331.63,73.33)}, rotate = 180] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) ..
+% \draw    (305.63,73.33) -- (329.63,73.33) ;
+% \draw [shift={(331.63,73.33)}, rotate = 180] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) ..
 controls (6.95,-1.4) and (3.31,-0.3) ..
@@
 %Shape: Brace [id:dp8023308836405996] 
-\draw   (283.2,286.4) ..
+% \draw   (283.2,286.4) ..
 controls (283.2,291.07) and (285.53,293.4) ..
@@
     % \ym{I add symbols. please check if i still need to put original captions here}
-    \jinguo{please make the circles and texts in the inset larger}
+    % \jinguo{please make the circles and texts in the inset larger}
     }
@@
 \end{equation}
-\ym{But I still don't think the constant $c$ is reasonable in this version. Anyway it is a better 
-description for $W'$.}
-\jinguo{I changed $c$ to $1/c$}
+% \ym{But I still don't think the constant $c$ is reasonable in this version. Anyway it is a better 
+% description for $W'$.}
+% \jinguo{I changed $c$ to $1/c$}
 
@@
 %Thus a total sweep time for the computation should scale as $NM\log^{1 + \frac{c}{\ln(\Lambda)}}(M)$.
-\ym{Please help me to think about how to evaluate the time complexity while $N$ increases.}\jinguo{Leave it to Maddie}
+% \ym{Please help me to think about how to evaluate the time complexity while $N$ increases.}\jinguo{Leave it to Maddie}
 The computing speed $v$ defined as operations per unit time, can be estimated as
@@
 
+\subsubsection{Question about the above theory}
+
+\ym{Please check this part}
+
+We expect the error rate would decrease exponentially with the annealing time while $N, M$ is fixed, i.e. 
+\begin{equation}
+    \ln(\frac{1}{\epsilon}) \propto t_{\rm total}
+\end{equation}
+
+However, we found that the error rate is only inversely proportional to the annealing time, i.e,
+$\frac{1}{\epsilon} \propto t_{\rm total}$.
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=\columnwidth,keepaspectratio]{../notes/images/eps_vs_t.pdf}
+    \caption{(a): The error rate $\epsilon$ scales inversely with the total annealing time $t_{\rm total}$, which is different from the expected exponential scaling.
+    (b): The log plot implies that $\ln(v)$ is linear to $\ln(M)$, which then implies $v \propto (\frac{1}{M})^{b}$, where $b$
+    is the slope of the line.}
+    \label{questionplot}
+\end{figure}
+
+\Cref{questionplot}(b) shows that the moving speed $v$ is at least proportional to $\frac{1}{M}$,
+ which means we need at least $O(M^2)$ time to achieve a fixed error rate. This is correspond to the relationship
+ between $\epsilon$ and $t_{\rm total}$ when $N, M$ is fixed.
+
+The main problem is that $\epsilon$ does not obey the hypothesis that it decreases exponentially with the annealing time.
+We come up with this hypothesis based on the intuition that the sampling procedure is a Markov chain, 
+the proportion of the non-steady-state distribution should decrease exponentially with the number of samples.
+
+\ym{I think this hypothesis make sense, but how to check whether the code is correct or not?
+I set a minimum temperature of $10^{-5}$ in simulation. Should this be the reason?}
+
+This problem has nothing to do with the temperature distribution model. Same relationship between
+$v$ and $M$ also exist when we choose to anneal this system with a gaussian type temperature distribution.
+
+\iffalse
 \section{Numerical simulation}\label{sec:numerical-result}
@@
 % \end{figure}
+
+\fi
 
